### 2018-06-06 SJIS/esample.tex
Copied SWoPP template into the directory.

\documentclass[JIP]{ipsj}

\usepackage{graphicx}
\usepackage{latexsym}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{22}% vol22=2014
\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
\setcounter{page}{1}

\received{2014}{3}{4}
%\rereceived{2011}{10}{1}   % optional
%\rerereceived{2011}{10}{31} % optional
\accepted{2014}{8}{1}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\begin{document}

\title{How to Prepare Your Papers for the JIP\\
(ipsj.cls version 1.7)}

\affiliate{IPSJ}{Information Processing Society of Japan, 
Chiyoda, Tokyo 101--0062, Japan}
\affiliate{JU}{Johoshori University, Chiyoda, Tokyo 101--0062, Japan}
\paffiliate{PJU}{Johoshori University}

\author{Taro Joho}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
\author{Hanako Shori}{JU}[shori.hanako@johosyori-u.ac.jp]
\author{Jiro Gakkai}{IPSJ}

\begin{abstract}
This document is a guide for preparing drafts to be submitted to the
Journal of Information Processing (JIP) and for the final camera-ready
manuscripts of papers to appear in the JIP that use \LaTeX and special
style files.  Since this document itself is produced with these style
files, it will help you to refer to its source file, which is
distributed with these style files.
\end{abstract}

\begin{keyword}
Journal of Information Processing, \LaTeX, style files, ``Dos and
 Don'ts'' list
\end{keyword}

\maketitle

%1
\section{Introduction}

The Information Processing Society of Japan (IPSJ) publishes Journal of
Information Processing (JIP) as its flagship international journal.
Thus far, the JIP adopted the landscape A4 format for publishing papers,
but it has changed this format to the portrait A4 format because of many
requests from authors.  Corresponding to this format change, the JIP
accepts the portrait A4 format for submitting papers.

Following with this change, we, the Editorial Board of the JIP, prepared
a new style file for \LaTeX\@.  In this manuscript, we first describe
the usage of the style file.  The basic strategy of the new style file
is to require no special knowledge of command usage that does not use
standard \LaTeX commands.  Authors of a paper can use standard \LaTeX
commands to keep within the formatting restrictions of the paper, such
as setting space pitches and margins.  The guideline of the paper format
will be described in Section~\ref{body}.  Since this manuscript itself
also is written with the style file, we hope it will help with writing a
paper.

The Editorial Board of the JIP has also prepared a ``Dos and Don'ts''
list of matters an author should consider while writing a paper.  We
have added the list to the latter portion of this manuscript.  Please
use the list as a checklist for preparing to submit a paper.

%2
\section{Flow from Submission to Publishing}
%2.1
\subsection{Preparation}

The JIP author's kit including the \LaTeX style files can be downloaded
from the following URL:
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/style.html|
\end{quote}
The kit includes the following files:
\begin{enumerate}
\item \|ipsj.cls|: style file for ipsj journals
\item \|ipsjpref.sty|: style for the foreword
\item \|jsample.tex|: source for the Japanese version of this guide
\item \|esample.tex|: source of this guide
\item \|ipsjsort-e.bst|: bibtex style (sorted)
\item \|ipsjunsrt-e.bst|: bibtex style (unsorted)
\item \|bibsample.bib|: sample of bibliographic data (Japanese)
\item \|ebibsample.bib|: sample of bibliographic data (English)

\item \|ipsjtech.sty|: style file for technical report
\item \ \|tech-jsample.tex|: source for the Japanese version of technical report
\item \ \|tech-esample.tex|: source for the English version of technical report
\end{enumerate}

Since the kit has variants corresponding to multiple platforms,
including UNIX workstations, Windows (DOS), and Macintosh machines, an
appropriate variant can be selected and unpacked on the target
platform.

Since {\LaTeXe} is required as an execution environment, please install
it.

Regarding manuscripts written with Microsoft Word, a corresponding
company will convert them into \LaTeX\@.  This means that the Microsoft
Word format is used just a reference.

\footnotetext{The real author is the Editorial Board of JIP.}

%2.2
\subsection{Draft Submission}

First, generate a PDF file from your \LaTeX source and style file under
your {\LaTeXe} environment and check that the generated PDF file can be
read with the Adobe PDF reader.  After that, register your email address
into the Paper Review Management System (PRMS) through the following
URL:
\begin{quote}
 \small
 \|https://www.ipsj.or.jp/prms/author_pre_submit.do|
\end{quote}

\noindent
The system will return an email including another URL for submitting
your paper. The manual for submission via the PRMS is available at the
following URL: 
\begin{quote}
 \small
 \|http://www.ipsj.or.jp/jip/submit/manual/|\\
 \|e_manual.html|
\end{quote}

The JIP adopts \textit{single blind review}, 
where you will not know reviewers names.

%2.3
\subsection{Final Version}

After you receive the notification of acceptance, revise your paper in
accordance with the comments from the referees.
The layout of
figures and tables should be fixed. After that, \textit{check your paper
again and again to completely remove description errors}.

Send \textit{both the {\LaTeX} file package and the hard copy} to the
IPSJ\@. The standard contents of the file package are .tex and .bbl. If
you include PostScript files and/or special style files, add them into
the package. Note that \textit{you must not split your source into
multiple .tex files} because it is hard for printers to access multiple
files when they modify your source. Also, carefully make sure that the
package contains all necessary files, especially special style files.

Details on the file transfer, including its destination and packaging
method, will be provided to you by the IPSJ secretariat.

%2.4
\subsection{Proofreading, Typesetting, and Publishing}

The IPSJ may change terms in your paper as per its standard, and the
printing house may modify your source to make it fit the standard
printing style.  Even if they make no changes, the result printed at the
printing house may be different from what you printed because of
differences in the {\LaTeX} execution environment.  Therefore, the
galley proofs of your paper will be sent to you so that you can check if
those modifications and/or differences are acceptable.  If not, correct
errors with red ink.  Note that \textit{this proofreading is not for
correcting your errors}, which should have been corrected before sending
the final version.

Your paper will be typeset after errors you notify us about (if any) are
corrected and will be published as part of the JIP.

%3
\section{Guide for Formatting a Paper}

The JIP, as opposed to conference proceedings, has a traditional and
\textit{stiff} style.  This makes the style files also \textit{stiff}
and strongly restricts customizability, which is one of the most useful
features of {\LaTeX}.  For example, you must not change \textit{style
parameters}, such as \verb+\texheight+.  It is not easy to show which
customizations are allowed, but the rule ``Don't tamper with it unless
you are confident'' should suffice.

Note that if you do something you should not, \textit{you may not have
error messages but simply unattractive results}.

The source file must use the following format.  Underlined parts can be
omitted from draft versions.

%4
\section{Configuration of Paper}
\label{body}

The source file must use the following format.  Underlined parts can be
omitted from draft versions.  Note that a few additional commands, shown
in A.1 of the Appendix, are available for a paper included in the
Transactions.

\vskip\baselineskip

\noindent
\|\documentclass[JIP]{ipsj}|\\
\quad Specify other option styles if necessary.\\
\quad Specify auxiliary styles with \|\usepackage|.\\
\\
\Underline{\|\setcounter{|{\bf volume}\|}{<volume>}|}\\
\Underline{\|\setcounter{|{\bf number}\|}{<number>}|}\\
\Underline{\|\setcounter{|{\bf page}\|}{<first-page>}|}\\
\Underline{\|\|{\bf received}\|{<year>}{<month>}{<day>}|}\\
\Underline{\|\|{\bf accepted}\|{<year>}{<month>}{<day>}|}\\
\quad Define your own macros if necessary.\\\\
\quad If you cannot use the \|txfonts| package, please do not use the following command\\
\Underline{\|\usepackage[varg]{txfonts}|}\\
\Underline{\|\makeatletter|}\\
\Underline{\|\input{ot1txtt.fd}|}\\
\Underline{\|\makeatother|}\\\\
\|\begin{document}|\\[.5em]
\|\title{<title>}|\\[.5em]
\Underline{\|\affiliate{<affiliation-label>}{<affiliation>}|}\\\\
\quad Declare current affiliation with \|\paffilabel| if necessary.\\
\Underline{\|\paffiliate{<affiliation-label>}{<affiliation>}|}\\\\
\Underline{\|\author{1st-author}{affiliation-label}[E-mail]|}\\
\Underline{\|\author{2nd-author}{affiliation-label}|}\\\\
\|\begin{abstract}|\\
\quad\|<abstract>|\\
\|\end{abstract}|\\\\
\|\begin{keyword}|\\
\quad\|<keyword>|\\
\|\end{keyword}|\\\\
\|\maketitle|\\\\
\|\section{|heading-of-1st-section\|}|\\
\dots\dots\dots\dots\dots\\
\quad \|<main text>|\\
\dots\dots\dots\dots\dots\\\\
\quad Put acknowledgments here with the acknowledgment environment if any.\\
\|\begin{acknowledgment}|\\
\|\end{acknowledgment}|\\\\
\|\begin{thebibliography}{99}%9 or 99|\\
\|\bibitem{1}|\\
\|\bibitem{2}|\\
\|\end{thebibliography}|\\\\
\quad Put appendices here following \|\appendix| if any.\\
\|\appendix|\\
\|\section{|heading-of-1st-section\|}|\\\\
\Underline{\|\begin{biography}|}\\
\Underline{\|\profile{<1st-author>}{<biography-of-1st-author>}|}\\
\Underline{\|\profile{<2nd-author>}{<biography-of-2nd-author>}|}\\
\Underline{\|\end{biography}|}\\
\|\end{document}|

%4.1
\subsection{Option Style}

The following six styles are available as optional arguments of the
\|\documentclass|.  If the JIP option is not used, the program will use
the standard Japanese paper style as the default.

\begin{enumerate}
\item\|JIP|\footnote{English should be used for the English version of the Transactions.}
\quad For English documents
\item\|invited| \quad For invited papers
\item\|sigrecommended| \quad For recommended papers
\item\|technote| \quad For technical notes
\item\|preface| \quad For the preface of an issue
\end{enumerate}

Any combination of these options can be used.

If you specify auxiliary style files with the
\|\usepackage|, you must include them in the file package when you send
your final version to the IPSJ\@.

However, style files included in the {\LaTeXe} standard distribution
(e.g., graphicx) may be omitted.  Note that style files may be
incompatible with the style of the Journal Transaction.

%4.1.1
\subsubsection{Optional style exclusively for technical reports}

In addition to the options described above, 
an option intended exclusively for technical reports is available.
\begin{quote}
\|techrep|\quad technical report
\end{quote}

If \|\documentclass[techrep,JIP]{ipsj}| is used,
the technical-report style will be applied.

%4.2
\subsection{Title, Author Names, etc.}

Describe the title of your paper, author names and affiliations, and
abstract using the commands and environment shown in Section~\ref{body}.
Then, perform \verb+\maketitle+ to automatically put them at the
appropriate position.  In the draft version, the title and abstract are
automatically printed onto separate pages, while author names and
affiliations are not printed in order to make your paper anonymous.

%4.2.1
\subsubsection{Title}

The title specified with \verb+\title+ is made centered.  Even if the
title is too long to fit onto one line, \textit{an automatic line break
is not performed}.  If your title is long, insert \verb+\\+ into the
appropriate positions to break the lines.  A multiple line title is
first flushed left and then centered with respect to the widest line.

The title also appears in the header of odd numbered pages.  If your
title is too long, provide a shortened title for the header to
\verb+\title+ as its optional argument as follows.

%4.2.2
\subsubsection{Author Name and Affiliation}

When indicating the affiliation of each author with a label (first
citation) and starting from the first author, by using \|\affiliate|,
numbered footnotes will be generated that show the affiliations.  When
several authors are affiliated with the same organization, the
affiliation needs to be indicated only once.  For the author's current
affiliation, use \|\paffiliate| and provide the label and affiliated
organization as before.  If the affiliated organization arguments are
entered as current and a line break is inserted using \|\\|, the author
name will be automatically defined by \|\author|.  Immediately after the
author's name, enter the affiliation label and the author's e-mail
address.

Where there are several authors, repeating \|\author| will generate
additional authors in sequence (two authors, three authors, and so
forth).

To add current affiliations or multiple affiliations, delineate the
affiliate label using commas to include additional data.

%4.2.3
\subsubsection{Abstract}

The abstract of your paper should only be used in the \verb+abstract+
environment.

%4.2.4
\subsubsection{Keywords}

The keywords of your paper should be included as the content for the
 \verb+keyword+ environment.

%4.3
\subsection{Main part}

%4.3.1
\subsubsection{Sectioning}

{\LaTeX} standard commands such as \|\section| and \|\sub-| \|section|
are available for sectioning. The section heading of \|\section|
occupies two lines, while others are put into one line.

%4.3.2
\subsubsection{Fixed Baselines}

Each page of the JIP is formatted with the double-column style.  The
printing tradition of double-column requires that a line in the left
column and its neighbor in the right column have the same baseline.  To
meet this requirement, the style files carefully control the progression
of baselines when a vertical space is inserted for section titles and so
on.

%4.3.3
\subsubsection{Font Size}

You will see that various size fonts are used in the printed result of
your paper.  Since these fonts are automatically and carefully chosen by
the style files, you are free from the headache of selecting proper
fonts.  In fact, it is strongly recommended not to use
font-size-changing commands such as \verb+\large+ and \verb+\small+ in
the main text because they are quite harmful to retaining fixed
baselines.

%4.3.4
\subsubsection{Itemizing}

There is no special format for itemization. You can use the standard
\|enumerate|, \|itemize|, \|description| environment.

%4.3.5
\subsubsection{Footnotes}

The command \|\footnote| produces footnotes with reference marks such as
\footnote{An example of footnote 1.} and \footnote{An example of
footnote 2.}.  When there is more than one footnote within a single
page, please note that it is necessary to run \LaTeX\ twice to process
them correctly.  Moreover, it is sometimes preferable to separate a
footnote and its mark into different columns.  This can be achieved
using the \|\footnotemark| and \|\footnotetext| commands. The footnote
numbering produced by \LaTeX\ is continuous throughout the paper; it
does not restart on each new page.

%4.3.6
\subsubsection{Overfulls and Underfulls}

The final result must be free from any overfulls.  It is well known that
almost all overfulls can be avoided with a little effort when writing
sentences.  For example, avoiding long in-text formulas and \|\verb| is
very effective.  However, tricks using the \|flushleft| environment,
\|\\|, or \|\linebreak| are not recommended because they cause quite
unattractive results.

For underfulls, you will conveniently get the following warning message,
\begin{quote}\footnotesize*
\|Underfull| \|\hbox| \|(badness 10000)| \|detected|
\end{quote}
by inserting \|\\| at the end of a paragraph.  This message is also
output when you use \|\\| just before a list-like environment, just
before an \|\item|, and at the end of the environment. Such underfulls
cause unattractive empty lines and a flood of warnings that will hide
important error messages.

%4.4
\subsection{Formulas}\label{sec:ITEM}

%4.4.1
\subsubsection{In-text Formulas}

In-text formulas may be surrounded by any proper math-open\slash close
pair, i.e. \|$| and \|$|, \|\(| and \|\)|, or \|\begin| and \|\end| for
the \|math| environment. Note that tall materials in in-text formulas,
such as \smash{$\frac{a}{b}$} (\|\frac{a}{b}|), are unattractive and
will disarrange the baseline progression.

%4.4.2
\subsubsection{Displayed Formulas}

Displayed formulas {\em must not be surrounded by the pair
\|$$|}.  Instead, use the \|\[| and \|\]| pair or one of the environments
\|displaymath|, \|equation|, or \|eqnarray|.  These commands\slash
environments indent formulas (not centered) and keep fixed baselines as
follows.
\begin{equation}
\Delta_l = \sum_{i=l+1}^L\delta_{pi}.
\end{equation}

%4.4.3
\subsubsection{Eqnarray environment}

For a sequence of two or more related formulas (equations), use the
\|eqnarray| environment to line them up at equal (or unequal) signs
instead of \|\[| \ \|\]| or the \|equation| environment.

%4.4.4
\subsubsection{Special Fonts}

It is strongly recommended to use only standard {\LaTeX} math
fonts.  Otherwise, you must report that you are using special fonts.

\begin{figure}[tb]%1
\setbox0\vbox{\it
\hbox{\|\begin{figure}[tb]|}
\hbox{\quad \|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure}\|}}
\centerline{\fbox{\box0}}
\caption{Single column figure with caption\\
explicitly broken by $\backslash\backslash$}
\label{fig:single}
\end{figure}

\begin{figure}[tb]%2
\begin{minipage}[t]{0.5\columnwidth}
\footnotesize
\setbox0\vbox{
\hbox{\|\begin{minipage}[t]%|}
\hbox{\|  {0.5\columnwidth}|}
\hbox{\|\captionType{table}|}
\hbox{\|\caption{| \ldots \|}|}
\hbox{\|\ecaption{| \ldots \|}|}
\hbox{\|\label{| \ldots \|}|}
\hbox{\|\makebox[\textwidth][c]{%|}
\hbox{\|\begin{tabular}[t]{lcr}|}
\hbox{\|\hline\hline|}
\hbox{\|left&center&right\\\hline|}
\hbox{\|L1&C1&R1\\|}
\hbox{\|L2&C2&R2\\\hline|}
\hbox{\|\end{tabular}}|}
\hbox{\|\end{minipage}|}}
\hbox{}
\centerline{\fbox{\box0}}
\caption{Contents of table \protect\ref{tab:right}}
\label{fig:left}
\end{minipage}%
\begin{minipage}[t]{0.5\columnwidth}
\CaptionType{table}
\caption{A table built by Fig.\ \protect\ref{fig:left}}
\label{tab:right}
\makebox[\textwidth][c]{\begin{tabular}[t]{lcr}\hline\hline
left&center&right\\\hline
L1&C1&R1\\
L2&C2&R2\\\hline
\end{tabular}}
\end{minipage}
\end{figure}

\begin{figure}[t]
\setbox0\vbox{\it
\hbox{\|\begin{figure}[tb]|}
\hbox{\quad \|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure}\|}}
\centerline{\fbox{\box0}}
\caption{Single column figure with caption\\
explicitly broken by $\backslash\backslash$}
\end{figure}

\begin{figure*}[t]
\setbox0\vbox{\large
\hbox{\|\begin{figure*}[t]|}
\hbox{\quad\|<|figure-body\|>|}
\hbox{\|\caption{<|caption\|>}|}
\hbox{\|\label{| $\ldots$ \|}|}
\hbox{\|\end{figure*}|}}
\centerline{\fbox{\hbox to.9\textwidth{\hss\box0\hss}}}
\caption{Double column figure}
\label{fig:double}
\end{figure*}

%4.5
\subsection{Figures}

A figure fit to one column is specified by the form shown in
\figref{fig:single}. Note that you must not specify the \|h| option.

The \|\caption| of a figure should be given below the figure body
together with a \|\label| command.  A long caption will be automatically
broken into two or more lines and centered with respect to the widest
line.  You can assist, however, with the line breaking by adding \|\\|
to obtain a more beautiful result, especially for two-line captions, as
shown in \figref{fig:single}.

If you want to rank two or more figures and/or tables in a \|figure| (or
\|table|) environment in order to save space, enclose each figure\slash
table and its \|\caption| in a \|minipage| environment as shown in
\figref{fig:left} and \tabref{tab:right}. Also, as in a \|figure|
environment, the caption for \tabref{tab:right} is correctly typeset
because the \|minipage| for it has the \|\captionType{table}| command to
specify the type of caption.  The command can of course be used with the
\|figure| argument to give a figure caption.

\Figref{fig:double} shows how to make a double column figure.

You may use any size font, as shown in \figref{fig:double}. Also, you
may include an encapsulated PostScript file (so called EPS file) as the
body of a figure. To include, use
%
\begin{quote}
\|\usepackage{graphicx}|
\end{quote}
%
in the preamble and put the \|\includegraphics| command where you wish
to embed the EPS graphics with its file name (and options if necessary).

You might have noticed that the first reference to \figref{fig:single}
is bold-faced, while the second and third are typed in roman fonts.
This font switching is a rule of the Journal\slash Transactions and will
be automatically performed if you use \|\figref{<|label\|>}| instead of
\|Fig.~\ref{<|label\|>}|.  Another rule is that ``Figure'' must be used
instead of ``Fig.''\ if the reference is the first word of a sentence,
such as was the first reference to \figref{fig:double} above.
Unfortunately, this switching is too hard to do automatically, so you
must use \|\figref{<|label\|>}| in such cases.

%4.6
\subsection{Tables}

A table with many rules is not very beautiful. \tabref{tab:example}
shows an example of a table with standard style rules. Note that the
uppermost rule is doubled, and no rules are drawn on the left and right
edges. The caption should be put above the table. The default font size
for tables is \|\footnotesize|. Any reference to a table should be made
using \|\tabref{<|label\|>}|.

\begin{table}[tb]
\caption{Sections and sub-sections in which list-like environments are used (example of table)}
\label{tab:example}
\hbox to\hsize{\hfil
\begin{tabular}{l|lll}\hline\hline
&enumerate&itemize&description\\\hline
type-1&	2 & 3 & 4.5 \\
type-2&	---& 4.11 & 4.7 \\
type-3&	2 & --- & 4.5\\
type-4&	--- & 4.8 & 4.3 \\\hline
\multicolumn{4}{l}{type-1\,: {\tt enumerate}, etc.\quad
	type-2\,: {\tt enumerate*}, etc.}\\
\multicolumn{4}{l}{type-3\,: {\tt Enumerate}, etc.\quad
	type-4\,: {\tt ENUMERATE}, etc.}\\
\end{tabular}\hfil}
\end{table}

%4.7
\subsection{Citations, Reference, Acknowledgements}

%4.7.1
\subsubsection{Citations}

The command \|\cite| is used to add citations in the text.  Cited labels
are sorted automatically and separated by using square brackets \|[ ]|.
Thus,
\begin{quote}
\|The paper \cite{companion,latex} is|\\
\|an overview of \LaTeX|.
\end{quote}
will produce
\begin{quote}
The paper \cite{companion,latex} is an overview of \LaTeX.
\end{quote}

%4.7.2
\subsubsection{List of References}

References should be arranged in alphabetical or cited order.
It is recommended to use BiB{\TeX} and style files 
\|ipsjsort-e.bst|
(alphabetical order) or \|ipsjunsort-e.bst| (cited order) to make
references fit to the traditional style.
Remember that you must include \|.bbl| file in the file package, instead of
\|.bib|.
If you cannot use BiB{\TeX} and have to make references manually using the
bibliography environment, observe the references of this guide carefully
and follow its style.

%4.7.3
\subsubsection{Acknowledgments and Appendices}

If you want to acknowledge people, put your acknowledgments just before
the references and enclose them in the \|acknowledgment| environment.

Appendices, if there are any, should be put just after the references
and \|\appendix| command.  Sectioning commands produces headings like
{\bf \ref{A1}}, {\bf \ref{A2}}, and so on in the appendices.

%4.8
\subsection{Biography}

Biographies of authors are positioned at the end of the document, just
before \|\end{document}|, as follows.
%
\begin{quote}
\|\begin{biography}|\\
\|\profile{<|1st-author's-name\|>}|\\
\mbox{}\quad\|{<|biography-of-1st-author\|>}|\\
\|\author{<|2nd-author's-name\|>}|\\
\mbox{}\quad\|{<|biography-of-2nd-author\|>}|\\
\mbox{}\quad $\ldots\ldots\ldots$ \\
\|\end{biography}|
\end{quote}

Generally, photographs used in author biographies should be identification photographs.

The printers will crop these photographs to a size of 30\,mm by 25\,mm. 
Avoid using photographs that contain missing portions of the face or photographs 
in which the outline of the face is difficult to distinguish against the background. 
It is recommended to use photographs that have no background or that 
have light-colored backgrounds. 
When digitally submitting photographs for the author biography, 
the photograph must have a resolution of at least 300\,dpi and must 
have been captured using a camera with at least one megapixel resolution. 
Since photographs for the author biographies will be incorporated into 
digital data by the printers at the time the composition is prepared, 
it is not necessary to digitally insert the photographs into the draft.

%5
\section{Check List of ``Dos and Don'ts''}

%5.1
\subsection{The basics of writing}

\begin{itemize}
\item[$\Box$] Describe a paper so that readers understand the novelty,
	      availability, and reliability of the research.
\item[$\Box$] Try to make a paper easy to read (discontinuity in the
	      story and obscure backgrounds or themes are a burden to
	      readers). 
\item[$\Box$] Revisit the paper if the problem to be solved is not
	      generalized (entirely focused on a problem at XX
	      University, etc.) or if the paper reports deliverables
	      only and does not describe the problem itself. 
\item[$\Box$] Rethink the paper if its conclusion is not clearly
	      described, it does not adequately point out its
	      applicability, limits, and controversial points, or its
	      conclusion does not follow the contents. 
\item[$\Box$] Expressions that are inappropriate for scientific papers
	      and that are hard to understand should be reconsidered. 
\item[$\Box$] Second thought is necessary if sentences are in colloquial
	      style. 
\item[$\Box$] Check the structure of chapters and sections and the
	      organization of the paper. 
\item[$\Box$] Do not make the paper so that grasping the meaning is
	      difficult without guessing from the context. 
\item[$\Box$] Confirm if the explanation of the hypotheses is enough and
	      does not contain any gaps in meaning. 
\item[$\Box$] The authors should not submit a manuscript that includes
	      redundant and/or too brief descriptions.
\item[$\Box$] The authors should eliminate undefined terminologies.
\end{itemize}

%5.2
\subsection{Show novelty and usefulness clearly}

\begin{itemize}
\item[$\Box$] The authors should not submit a manuscript that does not
	      clarify the motivation and the goal of their study and the
	      relationship to other existing studies.
\item[$\Box$] The authors should not submit a manuscript that does not
	      clarify what technologies are well/publicly known and what
	      idea they are newly/originally proposing. 
\item[$\Box$] The authors should provide sufficient references in their
	      manuscript to back up the originality of their study. 
\item[$\Box$] The authors should not submit a manuscript in which the
	      readers cannot understand their proposal (or cannot find
	      any originality in it) because it consists entirely of
	      abstractive and/or conceptual descriptions. 
\item[$\Box$] The authors should not submit a manuscript that lacks
	      discussions on the effectiveness of their proposal. 
\end{itemize}

%5.3
\subsection{Concrete attention to writing}

\begin{itemize}
\item[$\Box$] The authors should not submit a manuscript whose Japanese
	      title does not match its content correctly.
\item[$\Box$] The authors should not submit a manuscript whose English
	      title does not match its content correctly or that
	      contains incorrect English usage.
\item[$\Box$] The paper should be revised when its abstract does not
	      show its purpose or is written in inadequate English.
\item[$\Box$] The paper should be revised when symbols and abbreviations
	      are not popular, wordings are not adequate, or the
	      explanations of its pictures and tables are not adequate.
\item[$\Box$] The paper should be revised when special wordings, which
	      are popular only in an individual or local group or a
	      small company, are used without any explanations.
\item[$\Box$] The paper should be revised when its pictures or tables
	      are not semantically clear or they contain mistakes.
\item[$\Box$] The paper should be revised when its pictures or tables
	      are not visually clear.
\item[$\Box$] The paper should be revised when the size or the scale of
	      its pictures or tables are not adequate.
\end{itemize}

%5.4
\subsection{Regarding references}

\begin{itemize}
\item[$\Box$] The number of references should be more than 10 (Some
	      opinions say more than 20 or 30 in some research areas.
\item[$\Box$] A sufficient number of references are required to show the
	      paper's novelty.
\item[$\Box$] The paper should be revised when it has an insufficient
	      number of references.
\item[$\Box$] Referring to appropriate papers written by Japanese
	      authors contributes to the further progression of the
	      Japanese research community.
\item[$\Box$] Do not include self-citations excessively.
\end{itemize}

%5.5
\subsection{Double submission}

\begin{itemize}
\item[$\Box$] Double submission of the original paper is
	      prohibited. However, it is permissible to submit a paper
	      accepted at an international conference and free from
	      copyright issues.
\item[$\Box$] Do not use the same figures or charts already included in
	      other original papers, except those that have proper
	      citations.
\item[$\Box$] Be careful not to have overlap between the paper and other
	      published articles.
\end{itemize}

%5.6
\subsection{Check by other researchers}

\begin{itemize}
\item[$\Box$] Proofreading by experienced persons with many accepted
	      papers is strongly recommended.
\item[$\Box$] Take care to avoid leaps of logic from the viewpoint of
	      the readers.
\end{itemize}

%5.7
\subsection{Miscellaneous}

\begin{itemize}
\item[$\Box$] After the first review round, do not modify the paper
	      except for the stated conditions for acceptance without
	      the reviewers' approval.

\item[$\Box$] The authors cannot select reviewers.

\item[$\Box$] Fill the self-check sheet carefully before submitting the
	      paper.
\end{itemize}

\newpage%%

%6
\section{Concluding Remarks}

We dare not dream that the style files are perfect but rather wish to
improve them with your cooperation and hope that you will let us know of
any complaints, comments, suggestions by e-mail to: 
\begin{quote}
\|editt@ipsj.or.jp|.
\end{quote}

\begin{acknowledgment}
We wrote this article based on the guideline for A4 landscape layout.
We are grateful to Prof.\ Hiroshi Nakashima from Kyoto University,
for his valuable comments on making a class-file, 
and his consent to usage of BiB{\TeX} files.
We are also very thankful to the editorial committee for their
contributions in writing the guideline for the A4 landscape layout.
\end{acknowledgment}

\begin{thebibliography}{99}
\bibitem{companion}%1
Goossens, M., Mittelbach, F. and Samarin, A.:
{\it The LaTeX Companion},
Addison Wesley, Reading, 
Massachusetts (1993).

\bibitem{latex}%2
Lamport, L.: 
{\it A Document Preparation System {\LaTeX} User's Guide \& Reference Manual}, 
Addison Wesley, Reading, Massachusetts (1986).

\bibitem{article1}%3
Itoh, S. and Goto, N.: 
An Adaptive Noiseless Coding for Sources with Big Alphabet Size, 
{\it Trans.\ IEICE},  
Vol.E74, No.9, pp.2495--2503 (1991).

\bibitem{article2}%4
Abrahamson, K., Dadoun, N., Kirkpatrick, D.G. and Przytycka, T.: 
A Simple Parallel Tree Contraction Algorithm, 
{\it J.\ Algorithms},  
Vol.10, No.2,
pp.287--302 (1989).

\bibitem{article3}%5
Yamakami, T.: Exploratory Session Analysis in the Mobile Clickstream, 
{\it IPSJ Digital Courier},  
Vol.3, pp.14--20 (online), \\
\doi{10.2197/ipsjdc.3.14} (2007).

\bibitem{book1}%6
Foley, J.D. et al.: 
Computer Graphics --- Principles and Practice, 
System Programming Series, Addison-Wesley, 
Reading, Massachusetts, 2nd edition (1990).

\bibitem{book2}%7
Chang, C.L. and Lee, R.C.T.: 
Symbolic Logic and Mechanical Theorem Proving, 
Academic Press, New York (1973).

\bibitem{booklet1}%8
{Institute for New Generation Computer Technology}: 
Overview of the Fifth Generation Computer Project, 
distributed in {FGCS'92} (1992).
(in Japanese).

\bibitem{inbook1}%9
Knuth, D.E.: 
Art of Computer Programming,
{\it Fundamental Algorithms}, 
Vol.1, chapter 2, 
pp.371--381, 
Addison-Wesley, 2nd edition (1973).

\bibitem{incollection1}%10
Schwartz, A.J.: 
Subdividing B{\'e}zier Curves and Surfaces, 
{\it Geometric Modeling: Algorithms and New Trends\/} 
(Farin, G.E., ed.), 
SIAM, Philadelphia,
pp.55--66 (1987).

\bibitem{inproceedings1}%11
Baraff, D.:
Curved Surfaces and Coherence for Non-penetrating Rigid Body
Simulation, 
{\it Proc.\ SIGGRAPH '90\/} (Beach, R.J., ed.), 
Dallas,
Texas, ACM, Addison-Wesley, 
pp.19--28 (1990).

\bibitem{inproceedings2}%12
Nakashima, H. et al.: 
OhHelp: A Scalable Domain-Decomposing Dynamic Load
Balancing for Particle-in-Cell Simulations, 
{\it Proc.\ Intl.\ Conf. Supercomputing}, 
pp.90--99 (online),\\
\doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).

\bibitem{manual1}%13
Adobe Systems Inc.: 
{\it PostScript Language Reference Manual}, 
Reading,
Massachusetts (1985).

\bibitem{mastersthesis1}%14
Ohno, K.: 
Efficient Message Communication of Concurrent Logic Programming
Language KL1 Based on Static Analysis, 
Master's thesis, 
Dept.\ Information Science, Kyoto University (1995).

\bibitem{misc1}%15
Saito, Y. and Nakashima, H.: 
{\tt ipsjpapers.sty} (1995).
(Style file for Trans. IPSJ distributed to authors.).

\bibitem{phdthesis1}%16
Weihl, W.: 
Specification and Implementation of Atomic Data Types, 
PhD Thesis,
MIT, Boston (1984).

\bibitem{proceedings1}%17
Institute for New Generation Computer Technology: 
{\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
Vol.1 (1992).

\bibitem{WarD:WAM-1}%18
Warren, D.H.D.: An Abstract {Prolog} Instruction Set, 
Technical Report 309,
Artificial Intelligence Center, 
SRI International (1983).

\bibitem{unpublished}%19
Editorial Board of Trans.\ IPSJ:
How to Typeset Your Papers in {\LaTeX}
(Version 1) (1995).
(distributed to authors).

\bibitem{webpage1}%20
Kay, A.: Welcome to Squeakland, Squeakland (online),\\
\urle{http://www.squeakland.org/community/biography/\\
alanbio.html}
\refdatee{2007-4-5}.

\bibitem{webpage2}%21
Nakashima, H.: 
A {WEB} Page, Kyoto University (online),\\
\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
a.web.page.of.long.url/}
\refdatee{2010-10-30}.

\bibitem{webpage3}%22
Nakashima, H.: 
Another {WEB} Page, 
Kyoto University (online),\\
\urle{http://www.para.media.kyoto-u.ac.jp/\~{}nakashima/\\
a.web.page.of.much.longer.url/} 
\refdatee{2010-10-30}.

\end{thebibliography}

\appendix

%A.1
\section{How to Write an Appendix}
\label{A1}

To add an appendix, write the command \|\appendix| immediately following
the reference list.  Within the appendix, the \|\section| command creates
numbered headings such as \ref{A1} and \ref{A2}.

%A.1.1
\subsection{Example of a Heading}
The command \|\subsection| in the appendix gives this kind of heading.

%A.2
\section{Commands for Transactions}
\label{A2}

Each transaction has its own subtitle, abbreviation code, and serial
number. This information is given by using the following commands for
the \|\documentclass| option in the final version.

\begin{itemize}
\item \|PRO| (Trans.\ Programming)
\item \|TOM| (Trans.\ Mathematical Modeling and Its Applications)
\item \|TOD| (Trans.\ Database)
\item \|ACS| (Trans.\ Advanced Computing Systems)
\item \|CDS| (Trans.\ Consumer Device \& System)
\item \|DC | (Trans.\ Digital Content)
\item \|TCE| (Trans.\ Computer and Education)
\item \|TBIO| (Bioinformatics)
\item \|SLDM| (System LSI Design Methodology)
\item \|CVA| (Computer Vision and Applications)
\end{itemize}

Moreover, for papers in English, the command \|english| can be added. For
example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
English document.

Note that the research group has a ``month of publication'' number that
does not correspond to the ``issue month number'' of the
transaction. You may be notified by the IPSJ or the Editorial Board of
the \|<month>| in order to set the month of publication counter as
follows.

\begin{quote}
\|\setcounter{month}{month of publication}|
\end{quote}

In addition, commands are provided for executing unique functions for
several transactions, as shown in the following sections.

%A.3
\section{Unique Commands for Each Part}

Since each of the parts has its own detailed specifications, the same
command may produce different results in two different parts.

In some cases, the \|<Revised date>| and \|<Second revised| \|date>| are
inputted. These can be added as a preamble by using

\begin{quote}
\|\rereceived{<year>}{<month>}{<day>}|\\
\|\rerereceived {<year>}{<month>}{<day>}|
\end{quote}

%A.3.1
\subsection{Unique Functions for Programming (PRO)}

Issues of Transactions on Programming (PRO) includes not only regular
papers but also abstracts from research presentations delivered in the
research groups of SIGPRO\@. The file for an abstract consists of
material from the \|\documentclass| to the \maketitle of the format
shown in Section~\ref{body}. That is, the file does not have a main
text. Note that the reception and acceptance dates are not required, but
the date of presentation has to be given:
\begin{quote}
\|\Presented{<year>}{<month>}{<day>}|
\end{quote}

%A.3.2
\subsection{Unique Functions for Database (TOD)}

The name of the editor in charge for the paper included in The
Transactions on Database (TOD) is specified by
\begin{quote}
\|\edInCharge{<name-of-editor>}|
\end{quote}

Also, following a change in style, the command is entered at the end of
the paper, directly before \|\end{document}|.

%A.3.3
\subsection{Unique Functions for Consumer Devices \& Systems (CDS)}

In the ``Transactions on Consumer Devices \& Systems,'' since the
headings differ depending on the type of document, the type of heading
is to be changed with the option.

The types are:
\begin{itemize}
\item \|systems  | Paper on Consumer Systems
\item \|services | Paper on Consumer Services
\item \|devices  | Paper on Consumer Devices
\item \|Research | Research Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.4
\subsection{Unique Functions for Digital Content (DCON)}

In the ``Transactions on Digital Content,'' since the
headings differ depending on the type of document, the type of heading
is to be changed with the option.

The types are:
\begin{itemize}
\item \|Research | Research Paper
\item \|Practice | Practice Paper
\item \|Content  | Content Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.5
\subsection{Unique Functions for Computer and Education (TCE)}

In the ``Transactions on Computer and Education,'' since the headings
differ depending on the type of document, the type of heading is
to be changed with the option.

The types are:
\begin{itemize}
\item \|No specification  | Regular Paper (Default)
\item \|Short             | Short Paper
\end{itemize}
For English papers, you simply need to add \|english|.

%A.3.6
\subsection{Unique Functions for Bioinformatics (TBIO)}

Since papers in Transactions on Bioinformatics (TBIO) are in English,
specifying the TBIO option will cause the program to assume that the
English option has been specified. This effectively means that the
English option can be omitted.

The following three categories define the different types of papers.
\begin{itemize}
\item \|No specification | Original Paper (Default)
\item \|Data             | Database/Software Paper
\item \|Survey           | Survey Paper
\end{itemize}

Therefore, \|\documentclass[TBIO]{ipsj}| will be an original paper, and
\|\documentclass[TBIO,Survey]{ipsj}| will be a survey paper.

Moreover, as with TOD, the name of the editor in charge of the paper is
specified by using \|\Editor|, but in this case, the text is introduced with ``Communicated by.'' Therefore, the name of the editor is positioned directly before \|\end{document}|, as with TOD.

%A.3.7
\subsection{Unique Functions for Computer Vision and Applications (CVA)}

The Transactions of Computer Vision and Applications is also an English
language journal, allowing the English option to be omitted.

There are three classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Research         | Research Paper
\item \|system           | Systems Paper
\item \|Express          | Express Paper
\end{itemize}

As with TBIO, the name of the editor in charge is inserted, and the
inserted text is introduced with ``Communicated by.''

%A.3.8
\subsection{Unique Functions for System LSI Design Methodology (SLDM)}

The Transactions of System LSI Design and Methodology (SLDM) is also an
English language journal, allowing the English option to be omitted.

There are two classes of documents:
\begin{itemize}
\item \|No specification | Regular Paper (Default)
\item \|Short            | Short Paper
\end{itemize}

SDLM also enters the name of the editor in charge, but automatic
insertion is treated differently depending on the paper.

Normally, text is inserted using ``Recommended by Associate Editor:,''
but it is only when the ``invited'' option is included that the
insertion text becomes ``Invited by Editor-in-Chief:.''

\begin{biography}
\profile{Taro Joho}{was born in 1970. He received his M.S.\ degree from
Johoshori University in 1994.
He joined
the Information
Processing Society of Japan in 1994.
He is currently an associate professor at
\mbox{Johoshori} University.
His research interest is online
publishing systems. He is a member of the IEEE and ACM\@.}
%
\profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
became an associate professor at Gakkai University in 1992 and a
professor at Johoshori University in 1997. Her current research
interest is online publishing systems. She received the Kiyasu Kinen
award in 2010. She is a Board Member of the IPSJ and a member of the
IEICE, IEEE-CS, and ACM\@.} 
%
\profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
from Johoshori University in 1994 and has been engaged in the
Information Processing Society of Japan since 1994. His research
interest is online publishing systems. He is a member of the IEEE and
ACM\@.}
%
\end{biography}
\end{document}

### 2018-06-06 SJIS/tech-esample.tex
Copied SWoPP template into the directory.

--- 2018-06-06 SJIS/esample.tex
@@
-\documentclass[JIP]{ipsj}
-
-\usepackage{graphicx}
+%%
+%% 研究報告用スイッチ
+%% [techrep]
+%%
+%% 欧文用スイッチ(keywordは任意)
+%% [english]
+%%
+
+\documentclass[techrep,english]{ipsj}
+
+\usepackage[dvips]{graphicx}
 \usepackage{latexsym}
@@
 
-\setcounter{volume}{22}% vol22=2014
-\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
+\setcounter{volume}{21}% vol21=2013
+\setcounter{number}{1}
 \setcounter{page}{1}
 
-\received{2014}{3}{4}
+%\received{2011}{7}{1}
 %\rereceived{2011}{10}{1}   % optional
 %\rerereceived{2011}{10}{31} % optional
-\accepted{2014}{8}{1}
+%\accepted{2011}{11}{5}
 
@@
 
-\title{How to Prepare Your Papers for the JIP\\
-(ipsj.cls version 1.7)}
+\title{How to Prepare Your Papers for the JIP}
 
@@
 
-\author{Taro Joho}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
-\author{Hanako Shori}{JU}[shori.hanako@johosyori-u.ac.jp]
-\author{Jiro Gakkai}{IPSJ}
+\author{Joho Taro}{IPSJ,PJU}[joho.taro@ipsj.or.jp]
+\author{Shori Hanako}{JU}[shori.hanako@johosyori-u.ac.jp]
+\author{Gakkai Jiro}{JU}
 
@@
 
-\begin{keyword}
-Journal of Information Processing, \LaTeX, style files, ``Dos and
- Don'ts'' list
-\end{keyword}
+%\begin{keyword}
+%Journal of Information Processing, \LaTeX, style files, ``Dos and
+% Don'ts'' list
+%\end{keyword}
 
@@
 The kit includes the following files:
-\begin{enumerate}
+\begin{enumerate}%{
 \item \|ipsj.cls|: style file for ipsj journals
+\item \|ipsjdraft.sty|: style for drafts to be submitted
 \item \|ipsjpref.sty|: style for the foreword
@@
 \item \|ebibsample.bib|: sample of bibliographic data (English)
-
-\item \|ipsjtech.sty|: style file for technical report
-\item \ \|tech-jsample.tex|: source for the Japanese version of technical report
-\item \ \|tech-esample.tex|: source for the English version of technical report
-\end{enumerate}
+\end{enumerate}%}
 
@@
 
-The JIP adopts \textit{single blind review}, 
-where you will not know reviewers names.
+The JIP adopts \textit{double blind review}, where reviewers of your
+paper will not know your name, and you will not know theirs.  To ensure
+that this is possible, the submitted draft version should not contain
+information about the authors.
 
@@
 After you receive the notification of acceptance, revise your paper in
-accordance with the comments from the referees.
-The layout of
+accordance with the comments from the referees and add the required
+omissions from the draft, such as a biography, if any. The layout of
 figures and tables should be fixed. After that, \textit{check your paper
@@
 \noindent
-\|\documentclass[JIP]{ipsj}|\\
+\|\documentclass[JIP]{ipsj}|\ or\\
+\|\documentclass[JIP,draft]{ipsj}|\\
 \quad Specify other option styles if necessary.\\
@@
 \begin{enumerate}
-\item\|JIP|\footnote{English should be used for the English version of the Transactions.}
-\quad For English documents
-\item\|invited| \quad For invited papers
-\item\|sigrecommended| \quad For recommended papers
-\item\|technote| \quad For technical notes
-\item\|preface| \quad For the preface of an issue
+\item\|JIP| For English documents
+\item\|draft| For draft versions
+\item\|invited| For invited papers
+\item\|sigrecommended| For a paper recommended by a SIG
+\item\|technote| For technical notes
+\item\|preface| For the preface of an issue
 \end{enumerate}
@@
 
-If you specify auxiliary style files with the
+If you use \|\documentclass[JIP,draft]{ipsj}|, the ``draft'' option
+style will be applied.  If you specify auxiliary style files with the
 \|\usepackage|, you must include them in the file package when you send
@@
 incompatible with the style of the Journal Transaction.
-
-%4.1.1
-\subsubsection{Optional style exclusively for technical reports}
-
-In addition to the options described above, 
-an option intended exclusively for technical reports is available.
-\begin{quote}
-\|techrep|\quad technical report
-\end{quote}
-
-If \|\documentclass[techrep,JIP]{ipsj}| is used,
-the technical-report style will be applied.
 
@@
 
-%4.3
-\subsection{Main part}
-
-%4.3.1
-\subsubsection{Sectioning}
+%5
+\section{Main part}
+%5.1
+\subsection{Sectioning}
 
@@
 
-%4.3.2
-\subsubsection{Fixed Baselines}
+%5.2
+\subsection{Fixed Baselines}
 
@@
 
-%4.3.3
-\subsubsection{Font Size}
+%5.3
+\subsection{Font Size}
 
@@
 
-%4.3.4
-\subsubsection{Itemizing}
+%5.4
+\subsection{Itemizing}\label{sec:item*}
 
@@
 
-%4.3.5
-\subsubsection{Footnotes}
+%5.5
+\subsection{Footnotes}
 
@@
 
-%4.3.6
+%5.5.1
 \subsubsection{Overfulls and Underfulls}
@@
 \end{quote}
-by inserting \|\\| at the end of a paragraph.  This message is also
+, by inserting \|\\| at the end of a paragraph.  This message is also
 output when you use \|\\| just before a list-like environment, just
@@
 
-%4.4
+%5.6
 \subsection{Formulas}\label{sec:ITEM}
-
-%4.4.1
+%5.6.1
 \subsubsection{In-text Formulas}
@@
 
-%4.4.2
+%5.6.2
 \subsubsection{Displayed Formulas}
@@
 
-%4.4.3
+%5.6.3
 \subsubsection{Eqnarray environment}
@@
 
-%4.4.4
+%5.6.4
 \subsubsection{Special Fonts}
@@
 \centerline{\fbox{\box0}}
-\caption{Contents of table \protect\ref{tab:right}}
+\caption{Contents of Table \protect\ref{tab:right}}
 \label{fig:left}
@@
 \setbox0\vbox{\large
-\hbox{\|\begin{figure*}[t]|}
+\hbox{\|\begin{figure}*[t]|}
 \hbox{\quad\|<|figure-body\|>|}
@@
 
-%4.5
+%5.7
 \subsection{Figures}
@@
 
-%4.6
+%5.8
 \subsection{Tables}
@@
 
-%4.7
+%5.9
 \subsection{Citations, Reference, Acknowledgements}
-
-%4.7.1
+%5.9.1
 \subsubsection{Citations}
@@
 
-%4.7.2
+%5.9.2
 \subsubsection{List of References}
@@
 
-%4.7.3
+%5.9.3
 \subsubsection{Acknowledgments and Appendices}
@@
 If you want to acknowledge people, put your acknowledgments just before
-the references and enclose them in the \|acknowledgment| environment.
+the references and enclose them in the \|acknowledgment|
+environment. Acknowledgments will not be printed in drafts.
 
@@
 
-%4.8
+%5.10
 \subsection{Biography}
@@
 
-Generally, photographs used in author biographies should be identification photographs.
-
-The printers will crop these photographs to a size of 30\,mm by 25\,mm. 
-Avoid using photographs that contain missing portions of the face or photographs 
-in which the outline of the face is difficult to distinguish against the background. 
-It is recommended to use photographs that have no background or that 
-have light-colored backgrounds. 
-When digitally submitting photographs for the author biography, 
-the photograph must have a resolution of at least 300\,dpi and must 
-have been captured using a camera with at least one megapixel resolution. 
-Since photographs for the author biographies will be incorporated into 
-digital data by the printers at the time the composition is prepared, 
-it is not necessary to digitally insert the photographs into the draft.
-
-%5
+%6
 \section{Check List of ``Dos and Don'ts''}
-
-%5.1
+%6.1
 \subsection{The basics of writing}
@@
 
-%5.2
+%6.2
 \subsection{Show novelty and usefulness clearly}
@@
 
-%5.3
+%6.3
 \subsection{Concrete attention to writing}
@@
 
-%5.4
+%6.4
 \subsection{Regarding references}
@@
 
-%5.5
+%6.5
 \subsection{Double submission}
@@
 
-%5.6
+%6.6
 \subsection{Check by other researchers}
@@
 
-%5.7
+%6.7
 \subsection{Miscellaneous}
@@
 	      the reviewers' approval.
-
-\item[$\Box$] The authors cannot select reviewers.
-
+\item[$\Box$] Since the IPSJ uses a double-blind review system, in which
+	      both author(s) and reviewers remain anonymous, the authors
+	      cannot select reviewers.
 \item[$\Box$] Fill the self-check sheet carefully before submitting the
@@
 
-\newpage%%
-
-%6
+%7
 \section{Concluding Remarks}
@@
 \bibitem{companion}%1
-Goossens, M., Mittelbach, F. and Samarin, A.:
+Goossens, M., Mittelbach, F., and Samarin, A.:
 {\it The LaTeX Companion},
@@
 Lamport, L.: 
-{\it A Document Preparation System {\LaTeX} User's Guide \& Reference Manual}, 
+{\it A Document Preparation System {\LaTeX} User's Guide \&
+Reference Manual}, 
 Addison Wesley, Reading, Massachusetts (1986).
@@
 Itoh, S. and Goto, N.: 
-An Adaptive Noiseless Coding for Sources with Big Alphabet Size, 
+An Adaptive Noiseless Coding for Sources with Big
+Alphabet Size, 
 {\it Trans.\ IEICE},  
-Vol.E74, No.9, pp.2495--2503 (1991).
+Vol. E74, No. 9, pp. 2495--2503 (1991).
 
 \bibitem{article2}%4
-Abrahamson, K., Dadoun, N., Kirkpatrick, D.G. and Przytycka, T.: 
+Abrahamson, K., Dadoun, N., Kirkpatrick, D.G., and Przytycka, T.: 
 A Simple Parallel Tree Contraction Algorithm, 
 {\it J.\ Algorithms},  
-Vol.10, No.2,
-pp.287--302 (1989).
+Vol. 10, No. 2,
+pp. 287--302 (1989).
 
@@
 {\it IPSJ Digital Courier},  
-Vol.3, pp.14--20 (online), \\
+Vol. 3, pp. 14--20 (online), \\
 \doi{10.2197/ipsjdc.3.14} (2007).
@@
 Foley, J.D. et al.: 
-Computer Graphics --- Principles and Practice, 
+{\it Computer Graphics --- Principles and Practice},
 System Programming Series, Addison-Wesley, 
@@
 Chang, C.L. and Lee, R.C.T.: 
-Symbolic Logic and Mechanical Theorem Proving, 
+{\it Symbolic Logic and Mechanical Theorem Proving}, 
 Academic Press, New York (1973).
@@
 Knuth, D.E.: 
+{\it Fundamental Algorithms}, 
 Art of Computer Programming,
-{\it Fundamental Algorithms}, 
-Vol.1, chapter 2, 
-pp.371--381, 
+Vol. 1, chapter 2, 
+pp. 371--381, 
 Addison-Wesley, 2nd edition (1973).
@@
 SIAM, Philadelphia,
-pp.55--66 (1987).
+pp. 55--66 (1987).
 
@@
 Simulation, 
-{\it Proc.\ SIGGRAPH '90\/} (Beach, R.J., ed.), 
+{\it SIGGRAPH '90 Proceedings\/} (Beach, R.J., ed.), 
 Dallas,
 Texas, ACM, Addison-Wesley, 
-pp.19--28 (1990).
+pp. 19--28 (1990).
 
@@
 {\it Proc.\ Intl.\ Conf. Supercomputing}, 
-pp.90--99 (online),\\
+pp. 90--99 (online),\\
 \doi{http://doi.acm.org/10.1145/1542275.1542293} (2009).
@@
 {\it Proc.\ Intl.\ Conf.\ on Fifth Generation Computer Systems}, 
-Vol.1 (1992).
+Vol. 1 (1992).
 
@@
 
-%A.1
+%8
 \section{How to Write an Appendix}
@@
 
-%A.1.1
+%8.1
 \subsection{Example of a Heading}
@@
 
-%A.2
+%9
 \section{Commands for Transactions}
@@
 \item \|CDS| (Trans.\ Consumer Device \& System)
-\item \|DC | (Trans.\ Digital Content)
-\item \|TCE| (Trans.\ Computer and Education)
 \item \|TBIO| (Bioinformatics)
@@
 
-Moreover, for papers in English, the command \|english| can be added. For
+Moreover, for papers in English, the command English can be added. For
 example, writing \|\documentclass[PRO,| \|english]{ipsj}| will create an
@@
 
-%A.3
+%10
 \section{Unique Commands for Each Part}
@@
 
-%A.3.1
+%10.1
 \subsection{Unique Functions for Programming (PRO)}
@@
 \begin{quote}
-\|\Presented{<year>}{<month>}{<day>}|
-\end{quote}
-
-%A.3.2
+\|\Presents{<year>}{<month>}{<day>}|
+\end{quote}
+
+%10.2
 \subsection{Unique Functions for Database (TOD)}
@@
 
-%A.3.3
+%10.3
 \subsection{Unique Functions for Consumer Devices \& Systems (CDS)}
@@
 \item \|devices  | Paper on Consumer Devices
-\item \|Research | Research Paper
+\item \|research | Research Paper
 \end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.4
-\subsection{Unique Functions for Digital Content (DCON)}
-
-In the ``Transactions on Digital Content,'' since the
-headings differ depending on the type of document, the type of heading
-is to be changed with the option.
-
-The types are:
-\begin{itemize}
-\item \|Research | Research Paper
-\item \|Practice | Practice Paper
-\item \|Content  | Content Paper
-\end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.5
-\subsection{Unique Functions for Computer and Education (TCE)}
-
-In the ``Transactions on Computer and Education,'' since the headings
-differ depending on the type of document, the type of heading is
-to be changed with the option.
-
-The types are:
-\begin{itemize}
-\item \|No specification  | Regular Paper (Default)
-\item \|Short             | Short Paper
-\end{itemize}
-For English papers, you simply need to add \|english|.
-
-%A.3.6
+For English papers, you simply need to add English.
+
+%10.4
 \subsection{Unique Functions for Bioinformatics (TBIO)}
@@
 
-%A.3.7
+%10.5
 \subsection{Unique Functions for Computer Vision and Applications (CVA)}
@@
 \item \|system   | Systems Paper
-\item \|Express          | Express Paper
 \end{itemize}
@@
 
-%A.3.8
+%10.6
 \subsection{Unique Functions for System LSI Design Methodology (SLDM)}
@@
 \begin{itemize}
-\item \|No specification | Regular Paper (Default)
-\item \|Short            | Short Paper
+\item \|No specification| Regular Paper (Default)
+\item \|Short| Short Paper
 \end{itemize}
@@
 
+%% 以降無視されます
+
 \begin{biography}
-\profile{Taro Joho}{was born in 1970. He received his M.S.\ degree from
-Johoshori University in 1994.
-He joined
-the Information
-Processing Society of Japan in 1994.
-He is currently an associate professor at
-\mbox{Johoshori} University.
-His research interest is online
+\profile{Joho Taro}{was born in 1970. He received his M.S.\ degree from
+ Johoshori University in 1994 and has been engaged in the Information
+ Processing Society of Japan since 1994. His research interest is online
  publishing systems. He is a member of the IEEE and ACM\@.}
 %
-\profile{Hanako Shori}{was born in 1960. She received her M.E.\ and
+\profile{Shori Hanako}{was born in 1960. She received her M.E.\ and
  Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
@@
 %
-\profile{Jiro Gakkai}{was born in 1970. He received his M.S.\ degree
+\profile{Gakkai Jiro}{was born in 1970. He received his M.S.\ degree
  from Johoshori University in 1994 and has been engaged in the

### 2018-06-20 SWoPP2018 Paper/paper.tex
Merged paper and moved files around, included patched class.
Make with latexmk

\documentclass[techrep,english]{ipsj}
\usepackage[utf8]{inputenc}

\usepackage[dvips]{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{adjustbox}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{26} % vol21=2013, 22=14, 23=15, 24=16, 25=17, 26=18
\setcounter{number}{1}
\setcounter{page}{1}

%\received{2011}{7}{1}
%\rereceived{2011}{10}{1}   % optiona
%\rerereceived{2011}{10}{31} % optional
%\accepted{2011}{11}{5}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\begin{document}

\title{Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}

\affiliate{TiTech}{Tokyo Institute of Technology, 
Meguro, Tokyo 152--8550, Japan}
\affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}

\author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
\author{Arthur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
\author{Satoshi Matsuoka}{TiTech}

\begin{abstract}
The race for larger and deeper neural networks are leading researchers, vendors and practitioners to re-think architectural design decisions taken decades ago in hope to improve performance.
Among these decisions, reducing the numerical format is thought to be one of prime candidates to increasing performance.
Unfortunately, modern hardware has limited support for this, and the impact of modifying floating-point formats and its size remains shrouded in mystery.
To help investigate what the effects of varying the precision during deep-learning training are, first an architecture using reconfigurable hardware needs to be developed.
Through this work, we seek to accelerate arbitrary precision deep-learning training using Field-Programmable Gate-Arrays by leveraging Intel FPGA SDK for OpenCL.
Preliminary results show promise for implementations based on precisions or number formats that currently only have low performing implementations on conventional CPU and GPU hardware.
\end{abstract}

%\begin{keyword}
%Journal of Information Processing, \LaTeX, style files, ``Dos and
% Don'ts'' list
%\end{keyword}

\maketitle

%1
\section{Introduction}
Artur helps writing this.

\section{Related Work}
Artur can write this.

\section{A FPGA-based CNN Framework}
\subsection{Field-Programmable Gate-Arrays}
Small intro to FPGAs.

\subsection{(Convolutional) Neural Networks}
Small intro to Neural Networks.

\subsection{FPGA CNN Framework}
Small intro to the framework.
\subsubsection{Design overview}
Overview design + picture.
\subsubsection{Design details}
Gruesome details of the design.
\subsubsection{Design decisions}
Decisions taken while designing. The *why* we did as we did.

\section{Methodology}
\subsection{Experimental Platform}
Compiler, version, flags, fpga boards, host, etc.
\subsection{Network Tested + Data-set}
MNIST, Multilayer Perceptron?
number of runs, batch size, etc.

\section{Results}

\subsection{FPGA Resource Utilization}
Area, DSP, Fmax, etc.

\subsection{Training Performance}
Convergence, performance, accuracy, etc.

\begin{biography}
\profile{Joho Taro}{was born in 1970. He received his M.S.\ degree from
 Johoshori University in 1994 and has been engaged in the Information
 Processing Society of Japan since 1994. His research interest is online
 publishing systems. He is a member of the IEEE and ACM\@.}
%
\profile{Shori Hanako}{was born in 1960. She received her M.E.\ and
 Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
 became an associate professor at Gakkai University in 1992 and a
 professor at Johoshori University in 1997. Her current research
 interest is online publishing systems. She received the Kiyasu Kinen
 award in 2010. She is a Board Member of the IPSJ and a member of the
 IEICE, IEEE-CS, and ACM\@.} 
%
\profile{Gakkai Jiro}{was born in 1970. He received his M.S.\ degree
 from Johoshori University in 1994 and has been engaged in the
 Information Processing Society of Japan since 1994. His research
 interest is online publishing systems. He is a member of the IEEE and
 ACM\@.}
%
\end{biography}
\end{document}

### 2018-06-25 SWoPP2018 Paper/paper.tex
Added email for Matsuoka-sensei.
Lines for FPGA intro.

@@
 \author{Arthur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
-\author{Satoshi Matsuoka}{TiTech}
+\author{Satoshi Matsuoka}{TiTech}[matsu@is.titech.ac.jp]
 
@@
 \subsection{Field-Programmable Gate-Arrays}
-Small intro to FPGAs.
+%Small intro to FPGAs.
+FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementating a hardware design before taping out full chip.
+They are devices that can represent reconfigurable hardware. 
+The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAM and look up tables, in any way possible.
+This makes them very suitable for the research described in this paper.
+It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting.
 

### 2018-06-25 SWoPP2018 Paper/paper.tex
Added preliminary Introduction and their references.

@@
 \author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
-\author{Arthur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
+\author{Artur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
 \author{Satoshi Matsuoka}{TiTech}[matsu@is.titech.ac.jp]
@@
 \section{Introduction}
-Artur helps writing this.
+The present paper describes our efforts toward a customized and generalized framework for design-space exploration using alternative numerical floating-point formats through FPGAs.
+
+The recent explosion in artificial intelligence – in particular that of deep neural networks based on backpropagation – has triggered a storm in the introduction and creation of specialized compute devices.
+Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high-performance Deep-Learning (DL) training and/or inference.
+Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
+It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture – today and in the near future.
+
+In the pursuit for faster and more energy efficient deep-learning architecture, there is a need to critically question the long-standing architectural design decision taken by computer architects decades ago.
+One of the oldest design decision concerns the representation of real-valued numbers, otherwise known as the floating-point representation.
+The IEEE-754 floating-point representation is one of the few relics still used unchanged in computing today.
+However, several alternatives to the IEEE-754 format are emerging, such as Microsoft’s Deep-Learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
+
+However, exploring the space around IEEE-754 floating-point representations and its alternatives pose a significant engineering problem: hardware and software infrastructure is to tightly coupled to the IEEE-754 standard that changing any part of it incurs a high engineering overhead.
+One alternative is to simulate alternative floating-point representations in software, for example using soft-float or MPFR libraries~\cite{softfloat}, but the resulting performance is often several magnitudes lower than hardware implementations, limiting the size of the study conducted.
+Furthermore, simulating alternative numerical formats in software are incapable of using any compiler optimizations, nor can they leverage the vector instruction often crucial to reach application performance in modern processors.
+Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.
+calling convention).
+
+A better way to explore floating-point representation is to leverage Field-Programmable Gate-Arrays (FPGAs).
+An FPGA is a device consisting of several millions re-programmable look-up tables (LUTs) that together with programmable routers give a very malleable silicon substrate second only in performance to Application-Specific Integrate Circuits (ASICs).
+Modern FPGAs can be clocked at several hundreds MHz, and contain enough compute to rival even Graphics-Processing Units (GPUs), making them ideal to study architectural design choices.
+Furthermore, with the recent growth in popularity of High-Level Synthesis (HLS) tools, programming these devices can be as simple as writing C/C++ code, and delegate the software-to-hardware transformation effort to the compiler.
+
+We contribute with the following:
+\begin{itemize}
+\item Proposed design for a generalized FPGA training architecture targeting variable numerical formats, and
+\item Evaluation and analysis of core computation patterns, including FPGA resource utilization
+\end{itemize}
+
+The remainder of our paper is structure in the following way: Section~\ref{sec:relwork} position our work against other, similar efforts.
+Section~\ref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
+Section~\ref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in section~\ref{sec:result}.
+We conclude in section~\ref{sec:conclusion}.
 
 \section{Related Work}
+\label{sec:relwork}
 Artur can write this.
@@
 \section{A FPGA-based CNN Framework}
+\label{sec:framework}
 \subsection{Field-Programmable Gate-Arrays}
@@
 \section{Methodology}
+\label{sec:method}
 \subsection{Experimental Platform}
@@
 \section{Results}
+\label{sec:result}
 
@@
 
-\begin{biography}
-\profile{Joho Taro}{was born in 1970. He received his M.S.\ degree from
- Johoshori University in 1994 and has been engaged in the Information
- Processing Society of Japan since 1994. His research interest is online
- publishing systems. He is a member of the IEEE and ACM\@.}
-%
-\profile{Shori Hanako}{was born in 1960. She received her M.E.\ and
- Ph.D.\ from Johoshori University in 1984 and 1987, respectively. She
- became an associate professor at Gakkai University in 1992 and a
- professor at Johoshori University in 1997. Her current research
- interest is online publishing systems. She received the Kiyasu Kinen
- award in 2010. She is a Board Member of the IPSJ and a member of the
- IEICE, IEEE-CS, and ACM\@.} 
-%
-\profile{Gakkai Jiro}{was born in 1970. He received his M.S.\ degree
- from Johoshori University in 1994 and has been engaged in the
- Information Processing Society of Japan since 1994. His research
- interest is online publishing systems. He is a member of the IEEE and
- ACM\@.}
-%
-\end{biography}
+\section{Conclusion}
+\label{sec:conclusion}
+
+\begin{thebibliography}{99}
+
+\bibitem{msbrainwave}
+  Chung, Eric and Fowers, Jeremy and Ovtcharov, Kalin and Papamichael, Michael and Caulfield, Adrian and Massengill, Todd and Liu, Ming and Lo, Daniel and Alkalay, Shlomi and Haselman, Michael and others:
+  Serving DNNs in Real Time at Datacenter Scale with Project Brainwave:
+  {\it IEEE Micro},
+  vol. 38, number. 2, pp 8--20, 2018
+
+\bibitem{googletpu}
+  Google Blog (online):
+  Google Supercharges Machine Learning Tasks with TPU Custom Chip,
+  {\it https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}
+  Accessed: 2018-06-25
+
+\bibitem{fujitsudlu}
+  Fujitsu:
+  Post-K Development and Introducing DLU - Fujitsu,
+  {\it http://www.fujitsu.com/global/Images/post-k-development-and-introducing-dlu.pdf},
+  2016
+
+\bibitem{knm}
+  Bradford, Dennis and Chinthamani, Sundarama and Corbral, Jesus and Hassan, Adhiraj and Janik, Ken:
+  Knights Mill: Intel Xeon Phi Processor for Machine Learning,
+  {\it Hot Chips 2017},
+  2017
+
+\bibitem{volta100}
+  NVIDIA:
+  Artificial Intelligence Architecture,
+  {\it https://www.nvidia.com/en-us/data-center/volta-gpu-architecture/},
+  Accessed: 2018-06-25
+
+\bibitem{intelflexpoint}
+  Koster, Urs and Webb, Tristan and Wang, Xin and Nassar, Marcel and Bansal, Arjun K and Constable, William and Elibol, Oguz and Gray, Scott and Hall, Stewart and Hornof, Luke and others:
+  FlexPoint: An Adaptive Numerical Format for Efficient Training of Deep Neural Networks,
+  {\it Advances in Neural Information Processing Systems},
+  pp 1742--1752, 2017
+
+\bibitem{tpuformat}
+  The Next Platform:
+  Tearing Apart Google’s TPU 3.0 AI CoProcessor,
+  {\it https://www.nextplatform.com/2018/05/10/tearing-apart-googles-tpu-3-0-ai-coprocessor},
+  Accessed: 2018-06-25
+
+\bibitem{posits}
+  Gustafson, John L and Yonemoto, Isaac T:
+  Beating Floating Point at its Own Game: Posit Arithmetic,
+  {\it Supercomputing Frontiers and Innovations},
+  vol. 4, num. 2, pp 71--86, 2017
+
+\bibitem{softfloat}
+  Fousse, Laurent and Hanrot, Guillaume and Lef{\`e}vre, Vincent and P{\'e}lissier, Patrick and Zimmermann, Paul:
+  MPFR: A Multiple-Precision Binary Floating-Point Library with Correct Rounding,
+  {\it ACM Transactions on Mathematical Software (TOMS)},
+  vol. 32, num. 2, pp. 13, 2007
+
+\end{thebibliography}
+
 \end{document}

### 2018-06-26 SWoPP2018 Paper/paper.tex
Added related work section draft.

@@
 Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
-It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture – today and in the near future.
+It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
 
@@
 The IEEE-754 floating-point representation is one of the few relics still used unchanged in computing today.
-However, several alternatives to the IEEE-754 format are emerging, such as Microsoft’s Deep-Learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
+Reducing the size of the floating-point representation can have dramatical (and positive) impacts on the performance: more compute per unit silicon, more compute per unit bandwidth, and lower power consumption.
+Several alternatives to the IEEE-754 format are indeed emerging, such as Microsoft’s Deep-Learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
 
@@
 \label{sec:relwork}
-Artur can write this.
+Field-Programmable Gate-Arrays (FPGAs) have extensively been used to probe and explore various architectural design decision, including those of deep-learning.
+The large majority of existing work limit themselves to inference, primarily due to the simpler design layout (little intermediate data needs storing).
+Levering FPGAs have allowed researchers to decrease the number of bits allocate to the numerical representation, going as far as inferring popular networks such as  AlexNET~\cite{krizhevsky2012imagenet} using as few as binary~\cite{shimoda2017all,umuroglu2017finn} (1-bit) weights.
+Inferring networks that uses few bits to represents weights (called Quantized Neural Networks~\cite{courbariaux2016binarized}) requires subtle yet necessary changes to the training phase~\cite{binaryconnect,courbariaux2016binarized,zhou2016dorefa}.
+Lately, modern deep-learning framework are having support for reduced precision training, some driven by leading FPGA vendors such as Xilinx~\cite{xilinxml}.
+Dicecco et al.~\cite{dicecco2017fpga} are are working on a framework similar to ours – training neural networks using FPGAs while modifying the numerical format.
+Their work primary focus on the IEEE-754 format and convolution layers where-as we aspire to include alternative format such as posits~\cite{posits}.
+Using posits in deep-learning was intended the focus of Langroudi et al.~\cite{langroudi2018deep}’s work; however, they only compared the performance against fixed-point and only \textit{stored} the weights as posit (the computation was still done using IEEE-754).
+
+FPGAs are not unique to vary the numerical precision of deep neural networks, and several ASICs have been produced for quantized neural networks.
+Most of these focus only on inference (for embedded deployment)  for low-power embedded domains; these include YodaNN~\cite{yodann}, BinaryEYE~\cite{binaryeye} and ChipMunk~\cite{chipmunk}; these ASICs were shown to consume up-to two magnitudes low power compared to similar FPGA solutions.
+
+Commercially most vendors do support some form of reduced precision mode.
+Intel’s Knight’s Milll~\cite{knm} architecture replaces one of the AVX-512 vector units of Knight’s Landing with a Vector Neural Network Instruction (VNNI) unit, capable of performing dot-products in a mixed IEEE-754 16-bit and 32-bit mode.
+A similar process (reduced precision multiplication, full precision accumulation) is also applied in NVIDIA’s Volta-100 line GPUs.
+These mixed-precision units drastically improve the Artificial-Intelligence compute capabilities (AI-FLOPs) of modern systems, trading silicon resource for increased compute with arguable small impact on training performance.
+Vendors also embrace drastically different formats, notably in Intel’s NERVANA~\cite{nervana} (likely where FlexPoint~\cite{intelflexpoint} is used) and Google’s TPU~\cite{tpuformat} (which have more bits in the exponent compared to the mantissa).
 
@@
 
+\bibitem{langroudi2018deep}
+  Langroudi, Seyed HF and Pandit, Tej and Kudithipudi, Dhireesha:
+  Deep Learning Inference on Embedded Devices: Fixed-Point vs Posit,
+  {\it arXiv preprint arXiv:1805.08624},
+  2018
+
+\bibitem{nervana}
+  Intel:
+  Intel Nervana Neural Network Processor,
+  {\it https://ai.intel.com/intel-nervana-neural-network-processor/},
+  Access: 2018-06
+
+\bibitem{xilinxml}
+  Xilinx:
+  Xilinx ML Suite,
+  {\it https://www.xilinx.com/applications/megatrends/machine-learning.html},
+  Accessed: 2018-16
+
+\bibitem{krizhevsky2012imagenet}
+  Krizhevsky, Alex and Sutskever, Ilya and Hinton, Geoffrey E:
+  Imagenet classification with deep convolutional neural networks,
+  {\it Advances in neural information processing systems},
+  pp 1097–1105, 2012
+
+\bibitem{binaryconnect}
+  Courbariaux, Matthieu and Bengio, Yoshua and David, Jean-Pierr:
+  Binaryconnect: Training deep neural networks with binary weights during propagations,
+  {\it Advances in neural information processing systems},
+  pp 3123–3131, 2015
+
+\bibitem{zhou2016dorefa}
+  Zhou, Shuchang and Wu, Yuxin and Ni, Zekun and Zhou, Xinyu and Wen, He and Zou, Yuheng:
+  DoReFa-Net: Training low bitwidth convolutional neural networks with low bitwidth gradients
+  {\it  arXiv preprint arXiv:1606.06160},
+  2016
+
+\bibitem{yodann}
+  Andri, Renzo and Cavigelli, Lukas and Rossi, Davide and Benini, Luca:
+  YodaNN: An Architecture for Ultralow Power Binary-Weight CNN Acceleration
+  {\it IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems},
+  vol. 37, num. 1, pp 48–60, 2018
+
+\bibitem{binaryeye}
+  Moons, Bert and Bankman, Daniel and Yang, Lita and Murmann, Boris and Verhelst, Marian:
+  BinarEye: An always-on energy-accuracy-scalable binary CNN processor with all memory on chip in 28nm CMOS,
+  {\it Custom Integrated Circuits Conference (CICC), 2018 IEEE},
+  pp 1–4, 2018
+
+\bibitem{chipmunk}
+  Conti, Francesco and Cavigelli, Lukas and Paulin, Gianna and Susmelj, Igor and Benini, Luca:
+  Chipmunk: A systolically scalable 0.9 mm 2, 3.08 Gop/s/mW@ 1.2 mW accelerator for near-sensor recurrent neural network inference,
+  {\it Custom Integrated Circuits Conference (CICC), 2018 IEEE},
+  pp 1–4, 2018
+
+\bibitem{dicecco2017fpga}
+  DiCecco, Roberto and Sun, Lin and Chow, Paul:
+  FPGA-based training of convolutional neural networks with a reduced precision floating-point library,
+  {\it  Field Programmable Technology (ICFPT), 2017 International Conference on},
+  pp 239–242, 2016
+
+\bibitem{shimoda2017all}
+  Shimoda, Masayuki and Sato, Shimpei and Nakahara, Hiroki:
+  All binarized convolutional neural network and its implementation on an FPGA,
+  {\it  Field Programmable Technology (ICFPT), 2017 International Conference on},
+  pp 291–294, 2017
+
+\bibitem{umuroglu2017finn}
+  Umuroglu, Yaman and Fraser, Nicholas J and Gambardella, Giulio and Blott, Michaela and Leong, Philip and Jahre, Magnus and Vissers, Kees:
+  Finn: A framework for fast, scalable binarized neural network inference,
+  {\it  Proceedings of the 2017 ACM/SIGDA International Symposium on Field-Programmable Gate Arrays},
+  pp 65–74, 2017
+
+\bibitem{courbariaux2016binarized}
+  Courbariaux, Matthieu and Hubara, Itay and Soudry, Daniel and El-Yaniv, Ran and Bengio, Yoshua:
+  Binarized neural networks: Training deep neural networks with weights and activations constrained to+ 1 or-1,
+  {\it arXiv preprint arXiv:1602.02830},
+  2016
+
 \end{thebibliography}

### 2018-06-28 SWoPP2018 Paper/paper.tex
Added code project.

@@
 \usepackage{adjustbox}
+\usepackage{booktabs}
+\usepackage{siunitx}
 
@@
 
-\subsection{(Convolutional) Neural Networks}
-Small intro to Neural Networks.
+\subsection{Neural Networks}
+Intro to neural networks.
 
-\subsection{FPGA CNN Framework}
+\subsection{FPGA NN Framework}
 Small intro to the framework.
@@
 \subsubsection{Design details}
-Gruesome details of the design.
+All weight matrices are transposed in memory.
+The main inference is done using an blocking implementation of the matrix multiplication.
+So a block is fetched from the activations and the wieghts and place in the block RAM on the FPGA.
+The block RAM is much faster then the global memory.
+This speeds up through put by a large margin.
+Block RAM is equivalent to the shared or local memory of contemporary GPUs.
+
 \subsubsection{Design decisions}
@@
 
-\section{Methodology}
-\label{sec:method}
+\section{Methodology}\label{sec:method}
 \subsection{Experimental Platform}
+\begin{table}[h]\label{tab:software-versions}
+  \caption{Used software versions}
+  \begin{tabular}{ll}
+    \toprule
+    \textbf{Software} & \textbf{Version} \\
+    \midrule
+    Python & v3.6.3 \\
+    Keras & v2.2.0 \\
+    TensorFlow & v1.8.0 \\
+    Intel Quartus & v17.1.0 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+\begin{table}[h]\label{tab:test-hardware}
+  \caption{Test hardware}
+  \begin{tabular}{ll}
+    \toprule
+    \textbf{Hardware} & \textbf{Configuration} \\
+    \midrule
+    Intel i7-3930K & 3.20 GHz \\
+    Arria 10 & Nallatech N510T \\
+    TensorFlow & v1.8.0 \\
+    Intel Quartus & v17.1.0 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 Compiler, version, flags, fpga boards, host, etc.
 \subsection{Network Tested + Data-set}
-MNIST, Multilayer Perceptron?
-number of runs, batch size, etc.
+The used example network is a simple multilayer perceptron.
+The main dataset used was MNIST with a layer depth of 1 and the first layer output size of 128.
+The data set was trained using the first \num{50000} images from the MNIST dataset.
+The last \num{10000} images are used as the test dataset.
+Training was done using a batch size of 128.
 
-\section{Results}
-\label{sec:result}
+\section{Results}\label{sec:result}
 
@@
 
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Conclusion}\label{sec:conclusion}
 

### 2018-06-28 SimpleNN/build.sh

@@ -1,0 +1,3 @@
+#!/usr/bin/env bash
+
+PROJECT=nn_blocking make -C /nfshome/erwin/SimpleNN

### 2018-06-28 SimpleNN/build_hw.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env bash
+
+if [ $# -eq 0 ]
+  then
+    EXTRA='default'
+else
+    EXTRA=$1
+fi
+
+DATE=`date +'%Y-%m-%dT%H.%M.%S'`
+
+echo Current Project 'nn_blocking' Date: $DATE
+
+#make -C /home/erwin/SimpleNN clean
+FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -C /home/erwin/SimpleNN fpga
+EXIT_CODE=$?
+BUILD_DIR=`FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -s -C /home/erwin/SimpleNN get_build_dir`
+project_name=$(basename $BUILD_DIR)
+
+if [ $EXIT_CODE -eq 0 ]; then       
+    if [ -f $BUILD_DIR/acl_quartus_report.txt ]; then
+    fmax=`awk -F ":" '/Kernel fmax/ {print $2}' $BUILD_DIR/acl_quartus_report.txt | sed -e 's/^[[:space:]]*//' -e 's/[[:space:]]*$//'`
+    info="fmax: $fmax"
+    else
+    info=
+    fi
+    ./send_notification.sh "$project_name" Success "$info"
+else    
+    ./send_notification.sh "$project_name" Failure "Exit code $EXIT_CODE"
+fi

### 2018-06-28 SimpleNN/build_reportonly.sh

@@ -1,0 +1,15 @@
+#!/usr/bin/env bash
+
+if [ $# -eq 0 ]
+  then
+    EXTRA='default'
+else
+    EXTRA=$1
+fi
+
+DATE=`date +'%Y-%m-%dT%H.%M.%S'`
+
+echo Current Project 'nn_blocking' Date: $DATE
+
+#make -C /home/erwin/SimpleNN clean
+FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -C /home/erwin/SimpleNN report

### 2018-06-28 SimpleNN/fpga_test.py

@@ -1,0 +1,432 @@
+import numpy as np
+import argparse
+import pyopencl as cl
+import pyopencl.array
+from sys import platform
+import time
+import math
+import keras
+from keras.datasets import mnist
+import pickle
+import sys
+
+import itertools
+
+if platform == "darwin":
+    VENDOR_NAME = "apple"
+else:
+    VENDOR_NAME = "intel"
+DEVICE_TYPE = cl.device_type.GPU if VENDOR_NAME == 'apple' or VENDOR_NAME == 'nvidia' else cl.device_type.ACCELERATOR
+
+
+NN_T = np.float32
+
+class FPGATest:
+    minibatch_size = 128
+    rows_in_1 = 28*28
+    rows_out_1 = 128
+
+    rows_in_2 = rows_out_1
+    rows_out_2 = 10
+
+    fpga_iter = 20
+    cpu_iter = 20
+
+    data_max = 1
+    data_min = -data_max
+
+    learn_rate = 0.005
+    regulation_strength = 0.002
+
+    act_1 = []
+    act_2 = []
+    bias_1 = []
+    bias_2 = []
+    weights_1 = []
+    weights_2 = []
+    act_out_2 = []
+    act_out_2_cpu = []
+    ground_truth = []
+
+    act_1Array = None
+    act_2Array = None
+    bias_1Array = None
+    bias_2Array = None
+    weights_1Array = None
+    weights_2Array = None
+    act_out_2Array = None
+
+    def __init__(self, kernel_file):
+        print("OpenCL Version v{}".format(".".join([str(i) for i in cl.get_cl_header_version()])))
+        print("Finding platform....")
+        platform = self.findPlatform(VENDOR_NAME)
+        if not platform:
+            print("ERROR: Platform not found for name {0}".format(VENDOR_NAME))
+            exit(1)
+
+        print("Getting devices...")
+        devices = platform.get_devices(device_type=DEVICE_TYPE)
+        if len(devices) < 1:
+            print("ERROR: No device found for type {0}.".format(DEVICE_TYPE))
+            exit(1)
+
+        devices = [devices[1]]
+
+        self.ctx = cl.Context(devices=devices)
+
+        if DEVICE_TYPE == cl.device_type.ACCELERATOR:
+            print("Reading binary...")
+            binary = kernel_file.read()
+
+            binaries = [binary] * len(devices)
+
+            print("Building...")
+            program = cl.Program(self.ctx, devices, binaries)
+        else:
[…]

### 2018-06-28 SimpleNN/get_reports.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+#--filter="merge reports_filter.txt"
+
+rsync -zarv -R roma7.m.gsic.titech.ac.jp:/local/erwin/build_cache/kernel_**/reports/ .
+
+rsync -zarv -R roma7.m.gsic.titech.ac.jp:/local/erwin/build_cache/kernel_**/*.txt .

### 2018-06-28 SimpleNN/install-requirements.sh

@@ -1,0 +1,4 @@
+#!/usr/bin/env bash
+source ./.bashrc_arria10_rcx2
+
+CFLAGS=`aocl compile-config` LDFLAGS=`aocl link-config` pip3 install --user -r requirements.txt

### 2018-06-28 SimpleNN/main.py

@@ -1,0 +1,212 @@
+import numpy as np
+import sklearn
+import sklearn.datasets
+import matplotlib.pyplot as plt
+
+num_inputs = 2
+num_hidden = 32
+num_output = 10
+num_passes = 200
+num_examples = 32000
+num_testexamples = 2500
+num_batches = 1000
+num_batchsize = int(num_examples / num_batches)
+layers = 1 + 2
+n_l = [num_inputs] + [num_hidden] * (layers - 1) + [num_output]
+n = tuple(n_l)
+
+learn_rate = 0.001
+regulation_strength = 0.001
+
+
+def plot_decision_boundary(X, y, pred_func):
+    # Set min and max values and give it some padding
+    x_min, x_max = X[:, 0].min() - .5, X[:, 0].max() + .5
+    y_min, y_max = X[:, 1].min() - .5, X[:, 1].max() + .5
+    h = 0.01
+    # Generate a grid of points with distance h between them
+    xx, yy = np.meshgrid(np.arange(x_min, x_max, h), np.arange(y_min, y_max, h))
+    # Predict the function value for the whole gid
+    Z = pred_func(np.c_[xx.ravel(), yy.ravel()])
+    Z = Z.reshape(xx.shape)
+    # Plot the contour and training examples
+    plt.contourf(xx, yy, Z, cmap=plt.cm.Spectral)
+    plt.scatter(X[:, 0], X[:, 1], c=y, cmap=plt.cm.Spectral)
+
+
+# Helper function to evaluate the total loss on the dataset
+def calculate_loss(X, y, W, B):
+    a = {}
+    z = {}
+    a[0] = X
+    forward(a, W, B, z)
+    probs = a[layers]
+    # Calculating the loss
+    corect_logprobs = -np.log(probs[range(y.shape[0]), y])
+    data_loss = np.sum(corect_logprobs)
+    # Add regulatization term to loss (optional)
+    sum = 0
+    for i in range(1, layers + 1):
+        sum += np.sum(np.square(W[i]))
+    data_loss += regulation_strength / 2 * sum
+    return 1. / num_examples * data_loss
+
+def make_data(num):
+    #mnist = fetch_mldata('MNIST original', data_home=custom_data_home)
+    return sklearn.datasets.make_blobs(num, n_features=num_inputs, centers=num_output, cluster_std=0.5, random_state=0)
+
+def main_func():
+    # Generate a dataset and plot it
+    np.random.seed(0)
[…]

### 2018-06-28 SimpleNN/mainMNIST.py

@@ -1,0 +1,214 @@
+import numpy as np
+import sklearn
+import sklearn.datasets
+import matplotlib.pyplot as plt
+
+num_inputs = 784
+num_hidden = 1000
+num_output = 10
+num_passes = 200
+num_examples = 32000
+num_testexamples = 2500
+num_batches = 1000
+num_batchsize = int(num_examples / num_batches)
+layers = 1 + 2
+n_l = [num_inputs] + [num_hidden] * (layers - 1) + [num_output]
+n = tuple(n_l)
+
+learn_rate = 0.001
+regulation_strength = 0.001
+
+
+def plot_decision_boundary(X, y, pred_func):
+    # Set min and max values and give it some padding
+    x_min, x_max = X[:, 0].min() - .5, X[:, 0].max() + .5
+    y_min, y_max = X[:, 1].min() - .5, X[:, 1].max() + .5
+    h = 0.01
+    # Generate a grid of points with distance h between them
+    xx, yy = np.meshgrid(np.arange(x_min, x_max, h), np.arange(y_min, y_max, h))
+    # Predict the function value for the whole gid
+    Z = pred_func(np.c_[xx.ravel(), yy.ravel()])
+    Z = Z.reshape(xx.shape)
+    # Plot the contour and training examples
+    plt.contourf(xx, yy, Z, cmap=plt.cm.Spectral)
+    plt.scatter(X[:, 0], X[:, 1], c=y, cmap=plt.cm.Spectral)
+
+
+# Helper function to evaluate the total loss on the dataset
+def calculate_loss(X, y, W, B):
+    a = {}
+    z = {}
+    a[0] = X
+    forward(a, W, B, z)
+    probs = a[layers]
+    # Calculating the loss
+    corect_logprobs = -np.log(probs[range(y.shape[0]), y])
+    data_loss = np.sum(corect_logprobs)
+    # Add regulatization term to loss (optional)
+    sum = 0
+    for i in range(1, layers + 1):
+        sum += np.sum(np.square(W[i]))
+    data_loss += regulation_strength / 2 * sum
+    return 1. / num_examples * data_loss
+
+def get_data(num):
+    mnist = sklearn.datasets.fetch_mldata('MNIST original', data_home='./data/')
+    return mnist.data, mnist.target
+    #return sklearn.datasets.make_blobs(num, n_features=num_inputs, centers=num_output, cluster_std=0.5, random_state=0)
+
+def main_func():
+    # Generate a dataset and plot it
[…]

### 2018-06-28 SimpleNN/nohup_build_hw.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+
+if [ $# -eq 0 ]
+  then
+    EXTRA='default'
+else
+    EXTRA=$1
+fi
+LOGDIR=/local/erwin/build_logs
+
+DATE=`date +'%Y-%m-%dT%H.%M.%S'`
+
+LOGNAME=$LOGDIR/kernel_build_hw_${DATE}_${EXTRA}.log
+ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && bash -login -i -c 'source .bashrc_arria10_rcx2; mkdir -p $LOGDIR; ./build_hw.sh $EXTRA &>> $LOGNAME &'"
+
+echo "Tailing $LOGNAME"
+
+ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && tail -n 40 -f $LOGNAME"

### 2018-06-28 SimpleNN/rsync_hw.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+rsync . roma7.m.gsic.titech.ac.jp:/home/erwin/SimpleNN -av --exclude .idea --exclude test_hw --exclude test2_hw --exclude "local" --exclude "kernel_*" --exclude archive --exclude .idea --exclude .DS_Store --exclude "*.aocx"
+#ssh erwin@rcx0.m.gsic.titech.ac.jp 'cd /home/erwin/SimpleNN && bash -login -i -c "./run_hw.sh"'
+# ssh erwin@rcx0.m.gsic.titech.ac.jp bash -c << EOF
+#source ~/.bash_profile
+#source ~/.bashrc_stratixv
+#ll
+#pwd
+#cd /home/erwin/SimpleNN
+#
+#echo $PATH
+#./build.sh
+#./run.sh
+#
+#EOF

### 2018-06-28 SimpleNN/run.sh

@@ -1,0 +1,10 @@
+#!/usr/bin/env bash
+#PYOPENCL_CTX='0' PYOPENCL_COMPILER_OUTPUT=1
+KERNEL_NAME=`ls -t kernels/kernel_*_sw_emu*.aocx | head -1`
+
+if [ -f $KERNEL_NAME ]; then
+    echo "Running script with kernel: $KERNEL_NAME"
+    CL_CONTEXT_EMULATOR_DEVICE_INTELFPGA=4 /usr/bin/python3 ./fpga_test.py $KERNEL_NAME
+else
+    echo "There was no emulator kernel found."
+fi

### 2018-06-28 SimpleNN/run_hw.sh

@@ -1,0 +1,17 @@
+#!/usr/bin/env bash
+#PYOPENCL_CTX='0' PYOPENCL_COMPILER_OUTPUT=1
+
+if [ $# -eq 0 ]
+  then
+    EXTRA='default'
+else
+    EXTRA=$1
+fi
+
+KERNEL_NAME=`ls -t kernels/kernel_*${EXTRA}*hw*.aocx 2>/dev/null | head -1`
+if [ !  -z  $KERNEL_NAME ] && [ -f $KERNEL_NAME ]; then
+    echo "Running script with kernel: $KERNEL_NAME"
+    /usr/bin/python36 ./fpga_test.py $KERNEL_NAME
+else
+    echo "There was no matching kernel found."
+fi

### 2018-06-28 SimpleNN/send_notification.sh

@@ -1,0 +1,22 @@
+#!/bin/bash
+
+event_name="aoc-status"
+api_key="cdgfxgGqbIS7A9mdYAouB2"
+
+if [ $# -eq 3 ]
+  then
+    project=$1
+    status=$2
+    info=$3   
+else
+    echo Usage: PROJECT STATUS INFO
+    exit 1
+fi
+
+reminder=$1
+echo "Sending notification for $project with status $status and info $info"
+
+curl --silent --show-error -X POST -H "Content-Type: application/json" --data '{"value1": "'"$project"'","value2": "'"$status"'","value3": "'"$info"'"}' \
+https://maker.ifttt.com/trigger/$event_name/with/key/$api_key
+
+echo .

### 2018-06-28 SimpleNN/syncd.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+fswatch -e .idea -o . | xargs -n1 ./rsync_hw.sh
+

### 2018-06-28 SimpleNN/test.py

@@ -1,0 +1,61 @@
+import sys
+
+minibatch_size = 4
+rows_in = 4
+rows_out = 4
+
+N = minibatch_size
+M = rows_in
+K = rows_out
+
+BLOCK_SIZE = 2
+
+def render_matrix(y,x,y_size,x_size):
+    """
+
+    :param y: Row
+    :param x: Col
+    :param y_size: Number of Rows
+    :param x_size: Number of Cols
+    :return:
+    """
+    for j in range(0,y_size):
+        sys.stdout.write('|')
+        for i in range(0, x_size):
+            if i == x and j == y:
+                sys.stdout.write(" @ ")
+            else:
+                sys.stdout.write(" * ")
+        sys.stdout.write('|\n')
+    sys.stdout.write('\n')
+
+
+for i0 in range(0,N,BLOCK_SIZE):
+    imax = N if i0 + BLOCK_SIZE > N else i0 + BLOCK_SIZE
+
+    for j0 in range(0,M,BLOCK_SIZE):
+        jmax = M if j0 + BLOCK_SIZE > M else j0 + BLOCK_SIZE
+
+        for k0 in range(0,K,BLOCK_SIZE):
+            kmax = K if k0 + BLOCK_SIZE > K else k0 + BLOCK_SIZE
+            print("A: {2:.0f},{0:.0f}; W: {2:.0f},{1:.0f}; O: {1:.0f},{0:.0f}".format(i0/BLOCK_SIZE,j0/BLOCK_SIZE,k0/BLOCK_SIZE))
+
+            render_matrix(i0/BLOCK_SIZE,k0/BLOCK_SIZE,2,2)
+
+            ## Load block ram here. Or NDRange
+            print("Load act {1:.0f},{0:.0f}".format(i0 / BLOCK_SIZE, k0/BLOCK_SIZE))
+            print("Load weights {1:.0f},{0:.0f}".format(j0 / BLOCK_SIZE, k0 / BLOCK_SIZE))
+
+            for i1 in range(i0,imax):
+                mi = M * i1;
+                ki = K * i1;
+
+                for j1 in range(j0, jmax):
+                    kij = ki + j1;
+                    sj = M * j1
+
+                    for k1 in range(k0,kmax):
+                        #C[kij] += A[mi + k1] * B[sj + k1];
[…]

### 2018-06-28 SimpleNN/train.py

@@ -1,0 +1,67 @@
+"""Trains a simple deep NN on the MNIST dataset.
+
+Gets to 98.40% test accuracy after 20 epochs
+(there is *a lot* of margin for parameter tuning).
+2 seconds per epoch on a K520 GPU.
+"""
+
+from __future__ import print_function
+
+import keras
+from keras.datasets import mnist
+from keras.models import Sequential
+from keras.layers import Dense
+from keras.optimizers import RMSprop
+
+import pickle
+import numpy
+
+batch_size = 128
+num_classes = 10
+epochs = 10
+
+# the data, split between train and test sets
+(x_train, y_train), (x_test, y_test) = mnist.load_data()
+
+x_train = x_train.reshape(60000, 784)
+x_test = x_test.reshape(10000, 784)
+x_train = x_train.astype('float32')
+x_test = x_test.astype('float32')
+x_train /= 255
+x_test /= 255
+print(x_train.shape[0], 'train samples')
+print(x_test.shape[0], 'test samples')
+
+# convert class vectors to binary class matrices
+y_train = keras.utils.to_categorical(y_train, num_classes)
+y_test = keras.utils.to_categorical(y_test, num_classes)
+
+model = Sequential()
+model.add(Dense(128, activation='relu', input_shape=(784,)))
+# model.add(Dropout(0.2))
+# model.add(Dense(512, activation='relu'))
+# model.add(Dropout(0.2))
+model.add(Dense(num_classes, activation='softmax'))
+
+model.summary()
+
+model.compile(loss='categorical_crossentropy',
+              optimizer=RMSprop(),
+              metrics=['accuracy'])
+
+history = model.fit(x_train, y_train,
+                    batch_size=batch_size,
+                    epochs=epochs,
+                    verbose=1,
+                    validation_data=(x_test, y_test))
+score = model.evaluate(x_test, y_test, verbose=0)
+print('Test loss:', score[0])
+print('Test accuracy:', score[1])
+
+i = 0
+for layer in model.layers:
+    data = {"weights": layer.get_weights()[0], "bias": layer.get_weights()[1]}
+
+    pickle.dump(data, open("layer_h128_{}.p".format(i), "wb"))
+
+    i = i + 1

### 2018-06-28 SimpleNN/nohup_build_hw.sh
Stop leaving abandoned bash sessions on the server.

@@ -15,4 +15,4 @@ ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && bash -login -i -c 'source 
 
 echo "Tailing $LOGNAME"
 
-ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && tail -n 40 -f $LOGNAME"
+ssh erwin@roma7.m.gsic.titech.ac.jp -t "cd ~/SimpleNN && tail -n 40 -f $LOGNAME"

### 2018-06-28 SWoPP2018 Paper/paper.tex
Fixed some spacing issues.

@@
 Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high-performance Deep-Learning (DL) training and/or inference.
-Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
+Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill\`\cite{knm} and NVIDIA’s Volta-100\`\cite{volta100}.
 It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
@@
 Furthermore, simulating alternative numerical formats in software are incapable of using any compiler optimizations, nor can they leverage the vector instruction often crucial to reach application performance in modern processors.
-Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.
-calling convention).
+Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.\`calling convention).
 
@@
 Section~\ref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
-Section~\ref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in section~\ref{sec:result}.
+Section~\ref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in Section\`\ref{sec:result}.
 We conclude in section~\ref{sec:conclusion}.
 
-\section{Related Work}
-\label{sec:relwork}
+\section{Related Work}\label{sec:relwork}
 Field-Programmable Gate-Arrays (FPGAs) have extensively been used to probe and explore various architectural design decision, including those of deep-learning.
@@
 
-\section{A FPGA-based CNN Framework}
-\label{sec:framework}
+\section{A FPGA-based CNN Framework}\label{sec:framework}
 \subsection{Field-Programmable Gate-Arrays}
@@
 Training was done using a batch size of 128.
+The CPU code was implemented using the NumPy array.dot function.
 

### 2018-06-29 SWoPP2018 Paper/paper.tex
Took out the out of order loops and wrote some more for the paper.

@@
-\documentclass[techrep,english]{ipsj}
-\usepackage[utf8]{inputenc}
+\documentclass[techrep,english]{ipsj} % techrep,
 
-\usepackage[dvips]{graphicx}
+  \usepackage[nocompress]{cite}
+
+  %\usepackage[dvips]{graphicx}
   \usepackage{latexsym}
-\usepackage{amsmath}
-\usepackage{adjustbox}
-\usepackage{booktabs}
-\usepackage{siunitx}
+  \usepackage{url}
+
+  \usepackage{diagbox}
+
+  \usepackage{tabu}
+  \usepackage{footnote}
+  \usepackage{tablefootnote}
+  \usepackage{enumitem}
+  \usepackage{times}
+  \usepackage{float}
+  \usepackage[binary-units=true,quotient-mode=fraction,table-auto-round]{siunitx}
+  \sisetup{detect-all}
+  \sisetup{range-phrase=--}
+  \sisetup{range-units=single}
+  \DeclareSIUnit\years{years}
+  \usepackage{graphicx}
+  \usepackage{subfigure}
+  \usepackage{amsmath,amsfonts,amssymb}
+  \usepackage{comment}
+  \usepackage{multirow}
+  \usepackage{bbding}
+  \newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
+  \usepackage{times}
+  \usepackage{soul}
+  \usepackage{color}
+  \usepackage{latexsym}
+  \usepackage{booktabs,multirow,multicol}
+  \usepackage{todonotes}
+  \usepackage{multirow}
+  \usepackage{comment}
+  \usepackage{tabularx}
+  \usepackage{url}
 
@@
 
+\graphicspath{
+    {resources/}
+}
+
+%\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
+%\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
+%\def\|{\verb|}
+
 \setcounter{volume}{26} % vol21=2013, 22=14, 23=15, 24=16, 25=17, 26=18
@@
 \setcounter{page}{1}
-
-%\received{2011}{7}{1}
-%\rereceived{2011}{10}{1}   % optiona
-%\rerereceived{2011}{10}{31} % optional
-%\accepted{2011}{11}{5}
 
@@
 \makeatother%
+
+\usepackage[hidelinks]{hyperref}
+\usepackage[nameinlink,noabbrev,capitalise]{cleveref}
 
@@
 
-%1
 \section{Introduction}
@@
 Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high-performance Deep-Learning (DL) training and/or inference.
-Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill\`\cite{knm} and NVIDIA’s Volta-100\`\cite{volta100}.
+Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
 It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
@@
 
-The remainder of our paper is structure in the following way: Section~\ref{sec:relwork} position our work against other, similar efforts.
-Section~\ref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
-Section~\ref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in Section\`\ref{sec:result}.
-We conclude in section~\ref{sec:conclusion}.
+The remainder of our paper is structure in the following way: \cref{sec:relwork} position our work against other, similar efforts.
+\cref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
+\cref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in \cref{sec:result}.
+We conclude in \cref{sec:conclusion}.
 
@@
 They are devices that can represent reconfigurable hardware.
+
 The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAM and look up tables, in any way possible.
@@
 Intro to neural networks.
+%TODO
 
 \subsection{FPGA NN Framework}
-Small intro to the framework.
+A small framework was built, consisting of multiple kernels.
+One simple forward propagation kernel with optional Relu activation function integrated and a forward softmax kernel.
 \subsubsection{Design overview}
-Overview design + picture.
+\Cref{fig:block-diagram} shows a overview of the system.
+The backwards kernels are a work in progress, so for now we use an external training script.
+The host code, written in python, does a kernel call for every layer.
+
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\linewidth]{block-diagram.pdf}
+  \caption{Block diagram of implementation}\label{fig:block-diagram}
+\end{figure*}
+
 \subsubsection{Design details}
@@
 \subsubsection{Design decisions}
-Decisions taken while designing. The *why* we did as we did.
+Decisions taken while designing.
+The *why* we did as we did.
 
@@
 \subsection{Experimental Platform}
-\begin{table}[h]\label{tab:software-versions}
-  \caption{Used software versions}
+The software versions and hardware configuration are shown in respectively \cref{tab:software-versions} and \cref{tab:test-hardware}.
+All kernels were compiled with \texttt{-O3 -fp-relaxed}.
+\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit without changing the numerical output.
+\begin{table}[h]
+  \centering
+  \caption{Used software versions}\label{tab:software-versions}
   \begin{tabular}{ll}
@@
 \end{table}
-\begin{table}[h]\label{tab:test-hardware}
-  \caption{Test hardware}
+\begin{table}[h]
+  \centering
+  \caption{Test hardware}\label{tab:test-hardware}
   \begin{tabular}{ll}
@@
     \midrule
-    Intel i7-3930K & 3.20 GHz \\
-    Arria 10 & Nallatech N510T \\
-    TensorFlow & v1.8.0 \\
-    Intel Quartus & v17.1.0 \\
+    Intel i7-3930K & \SI{3.20}{\giga\hertz} \\
+    Host RAM & DDR3-\SI{1333}{\mega\hertz} Dual Channel \\
+    Arria 10 (x1) & Nallatech 510T \\
     \bottomrule
@@
 \end{table}
-Compiler, version, flags, fpga boards, host, etc.
+
 \subsection{Network Tested + Data-set}
 The used example network is a simple multilayer perceptron.
-The main dataset used was MNIST with a layer depth of 1 and the first layer output size of 128.
+The main dataset used was MNIST with a layer depth of 1 and a first layer output size of 128.
+So in total a two layer network.
 The data set was trained using the first \num{50000} images from the MNIST dataset.
-The last \num{10000} images are used as the test dataset.
+The last \num{10000} images are used as the test data set.
 Training was done using a batch size of 128.
@@
 \section{Results}\label{sec:result}
+The host (numpy based) code benchmarked at \num{41} GFLOPS for simple inference.
+Our first naive implementation clocked about \num{2.5} GFLOPS for this problem size.
+The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
+
+\begin{table}[h]
+  \centering
+  \caption{FPGA Kernel performance}\label{tab:kernel-performance}
+  \begin{tabular}{ll}
+    \toprule
+    \textbf{Block size} & \textbf{GFLOPS}  \\
+    \midrule
+    128x128 & \num{0}  \\
+    100x100 & \num{0} \\
+    84x84 & \num{0}  \\
+    64x64 & \num{14.3}  \\
+    32x32 & \num{0}  \\
+    16x16 & \num{4.1}  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
 \subsection{FPGA Resource Utilization}
-Area, DSP, Fmax, etc.
+The kernel resource utilization is shown in \cref{tab:fpga-util}.
+
+\begin{table}[h]
+  \centering
+  \caption{FPGA Hardware utilisation for different blocksizes}\label{tab:fpga-util}
+  \begin{tabular}{lllll}
+    \toprule
+    \textbf{Block size} & \textbf{Logic} & \textbf{DSPs} & \textbf{RAMs} & \textbf{Fmax} \\
+    \midrule
+    128x128 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    100x100 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    84x84 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    64x64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\
+    32x32 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    16x16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
 \subsection{Training Performance}
-Convergence, performance, accuracy, etc.
+The accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
+The FPGA gets slightly different floaing point results due to rounding differences but is matches the accuracy.
 
@@
   {\it IEEE Micro},
-  vol. 38, number. 2, pp 8--20, 2018
+  vol.
+38, number.
+2, pp 8--20, 2018
 
@@
   {\it Supercomputing Frontiers and Innovations},
-  vol. 4, num. 2, pp 71--86, 2017
+  vol.
+4, num.
+2, pp 71--86, 2017
 
@@
   {\it ACM Transactions on Mathematical Software (TOMS)},
-  vol. 32, num. 2, pp. 13, 2007
+  vol.
+32, num.
+2, pp.
+13, 2007
 
@@
   {\it IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems},
-  vol. 37, num. 1, pp 48–60, 2018
+  vol.
+37, num.
+1, pp 48–60, 2018
 

### 2018-06-29 SimpleNN/build_hw.sh

@@ -1,10 +1,16 @@
 #!/usr/bin/env bash
 
-if [ $# -eq 0 ]
+if [ $# -eq 2 ]
   then
-    EXTRA='default'
-else
     EXTRA=$1
+    TARGET=$2
+elif [ $# -eq 1 ]
+  then
+    EXTRA=$1
+    TARGET='fpga'
+else
+    EXTRA='default'
+    TARGET='fpga'
 fi
 
 DATE=`date +'%Y-%m-%dT%H.%M.%S'`
@@ -12,7 +18,7 @@ DATE=`date +'%Y-%m-%dT%H.%M.%S'`
 echo Current Project 'nn_blocking' Date: $DATE
 
 #make -C /home/erwin/SimpleNN clean
-FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -C /home/erwin/SimpleNN fpga
+FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -C /home/erwin/SimpleNN $TARGET
 EXIT_CODE=$?
 BUILD_DIR=`FLOW=hw PROJECT=nn_blocking BUILDTIME=$DATE EXTRA=$EXTRA make -s -C /home/erwin/SimpleNN get_build_dir`
 project_name=$(basename $BUILD_DIR)
@@ -24,7 +30,7 @@ if [ $EXIT_CODE -eq 0 ]; then
     else
     info=
     fi
-    ./send_notification.sh "$project_name" Success "$info"
+    ./send_notification.sh "$project_name: $TARGET" Success "$info"
 else    
-    ./send_notification.sh "$project_name" Failure "Exit code $EXIT_CODE"
+    ./send_notification.sh "$project_name: $TARGET" Failure "Exit code $EXIT_CODE"
 fi

### 2018-06-29 SimpleNN/fpga_test.py

@@ -10,7 +10,6 @@ from keras.datasets import mnist
 import pickle
 import sys
 
-import itertools
 
 if platform == "darwin":
     VENDOR_NAME = "apple"
@@ -22,7 +21,9 @@ DEVICE_TYPE = cl.device_type.GPU if VENDOR_NAME == 'apple' or VENDOR_NAME == 'nv
 NN_T = np.float32
 
 class FPGATest:
-    minibatch_size = 128
+
+    LAYER_FILENAME = "layer_h128_{0}.p"
+    minibatch_size = 10000
     rows_in_1 = 28*28
     rows_out_1 = 128
 
@@ -90,14 +91,14 @@ class FPGATest:
 
         self.kForward = program.forward
         self.kForwardSoftMax = program.forward_softmax
-        self.kBackWardFirstDelta = program.backward_first_delta
-        self.kBackward = program.backward
+        # self.kBackWardFirstDelta = program.backward_first_delta
+        # self.kBackward = program.backward
 
         self.kForward.set_scalar_arg_dtypes([None, None, None, None, np.int32, np.int32, np.int32, np.int32])
         self.kForwardSoftMax.set_scalar_arg_dtypes([None, np.int32, np.int32])
-        self.kBackWardFirstDelta.set_scalar_arg_dtypes([None, None, None, np.int32, np.int32])
-        self.kBackward.set_scalar_arg_dtypes(
-            [None, None, None, None, NN_T, NN_T, np.int32, np.int32, np.int32])
+        # self.kBackWardFirstDelta.set_scalar_arg_dtypes([None, None, None, np.int32, np.int32])
+        # self.kBackward.set_scalar_arg_dtypes(
+        #    [None, None, None, None, NN_T, NN_T, np.int32, np.int32, np.int32])
 
         self.queue = cl.CommandQueue(self.ctx)
 
@@ -237,7 +238,8 @@ class FPGATest:
         # Bias additions and broadcast plus matrix mult.
         ops = self.rows_out_1 * self.minibatch_size + (2 * self.rows_in_1 - 1) * self.minibatch_size * self.rows_out_1
         ops += self.rows_out_2 * self.minibatch_size + (2 * self.rows_in_2 - 1) * self.minibatch_size * self.rows_out_2
-        print("Total operations: {0} billion.".format(ops / 1e9))
+        ops += self.rows_out_2 * (4 + 60) + 1
+        print("Total operations: {0} billion per batch.".format(ops / 1e9))
         return ops
 
[…]

### 2018-06-29 SimpleNN/get_reports.sh

@@ -5,3 +5,5 @@
 rsync -zarv -R roma7.m.gsic.titech.ac.jp:/local/erwin/build_cache/kernel_**/reports/ .
 
 rsync -zarv -R roma7.m.gsic.titech.ac.jp:/local/erwin/build_cache/kernel_**/*.txt .
+
+rsync -zarv -R roma7.m.gsic.titech.ac.jp:/local/erwin/build_logs/** .

### 2018-06-29 SimpleNN/nohup_build_hw.sh

@@ -1,17 +1,24 @@
 #!/bin/bash
 
-if [ $# -eq 0 ]
+if [ $# -eq 2 ]
   then
-    EXTRA='default'
-else
     EXTRA=$1
+    TARGET=$2
+elif [ $# -eq 1 ]
+  then
+    EXTRA=$1
+    TARGET='fpga'
+else
+    EXTRA='default'
+    TARGET='fpga'
 fi
+
 LOGDIR=/local/erwin/build_logs
 
 DATE=`date +'%Y-%m-%dT%H.%M.%S'`
 
 LOGNAME=$LOGDIR/kernel_build_hw_${DATE}_${EXTRA}.log
-ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && bash -login -i -c 'source .bashrc_arria10_rcx2; mkdir -p $LOGDIR; ./build_hw.sh $EXTRA &>> $LOGNAME &'"
+ssh erwin@roma7.m.gsic.titech.ac.jp "cd ~/SimpleNN && bash -login -i -c 'source .bashrc_arria10_rcx2; mkdir -p $LOGDIR; ./build_hw.sh $EXTRA $TARGET &>> $LOGNAME &'"
 
 echo "Tailing $LOGNAME"
 

### 2018-06-29 SWoPP2018 Paper/paper.tex
Small additions and edits.

@@
 
-\section{A FPGA-based CNN Framework}\label{sec:framework}
+\section{A FPGA-based NN Framework}\label{sec:framework}
 \subsection{Field-Programmable Gate-Arrays}
-%Small intro to FPGAs.
+
 FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementating a hardware design before taping out full chip.
@@
 A small framework was built, consisting of multiple kernels.
-One simple forward propagation kernel with optional Relu activation function integrated and a forward softmax kernel.
+One simple forward propagation kernel with optional Relu activation function integrated into it and a forward softmax kernel.
 \subsubsection{Design overview}
@@
 The host code, written in python, does a kernel call for every layer.
+And does a final softmax kernel call to get the final prediction.
+For perfomance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
+The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that formats, and an FPGA is better at accomodating that without a huge performance impact.
 
@@
 \subsubsection{Design decisions}
-Decisions taken while designing.
-The *why* we did as we did.
+One of the main choices with the largests effect on implementation as whenever to keep all weight matrices in memory transposed.
+During inference this is very benificial, this makes most reads sequential.
+During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
+But since the artihmetic density of training is higher, the effect might be slightly less pronounced.
 
@@
     Host RAM & DDR3-\SI{1333}{\mega\hertz} Dual Channel \\
-    Arria 10 (x1) & Nallatech 510T \\
+    Arria 10 ($\times$1) & Nallatech 510T \\
     \bottomrule
@@
 The used example network is a simple multilayer perceptron.
-The main dataset used was MNIST with a layer depth of 1 and a first layer output size of 128.
-So in total a two layer network.
+The main dataset used was MNIST.
+The input layer is has 128 outputs, adn the final layer 10 class outputs.
+So in total a two layer network, or two sets of weight matrices and bias vectors.
 The data set was trained using the first \num{50000} images from the MNIST dataset.
@@
     \midrule
-    128x128 & \num{0}  \\
-    100x100 & \num{0} \\
-    84x84 & \num{0}  \\
-    64x64 & \num{14.3}  \\
-    32x32 & \num{0}  \\
-    16x16 & \num{4.1}  \\
+    128$\times$128 & \num{0}  \\
+    100$\times$100 & \num{0} \\
+    84$\times$84 & \num{0}  \\
+    64$\times$64 & \num{14.3}  \\
+    32$\times$32 & \num{0}  \\
+    16$\times$16 & \num{4.1}  \\
     \bottomrule
@@
     \midrule
-    128x128 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    100x100 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    84x84 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    64x64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\
-    32x32 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    16x16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\
+    128$\times$128 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    100$\times$100 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    84$\times$84 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    64$\times$64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\
+    32$\times$32 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
+    16$\times$16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\
     \bottomrule

### 2018-06-29 SimpleNN/fpga_test.py
Updated script to run any densely connected network. Changed example network.

@@ -10,25 +10,23 @@ from keras.datasets import mnist
 import pickle
 import sys
 
-
 if platform == "darwin":
     VENDOR_NAME = "apple"
 else:
     VENDOR_NAME = "intel"
 DEVICE_TYPE = cl.device_type.GPU if VENDOR_NAME == 'apple' or VENDOR_NAME == 'nvidia' else cl.device_type.ACCELERATOR
 
-
 NN_T = np.float32
 
+
 class FPGATest:
+    hidden_layers = 1
+    layers = hidden_layers + 2
 
-    LAYER_FILENAME = "layer_h128_{0}.p"
+    LAYER_FILENAME = "layer_test2_{0}.p"
     minibatch_size = 10000
-    rows_in_1 = 28*28
-    rows_out_1 = 128
 
-    rows_in_2 = rows_out_1
-    rows_out_2 = 10
+    layer_height = [28 * 28, 512, 512, 10]
 
     fpga_iter = 20
     cpu_iter = 20
@@ -39,25 +37,25 @@ class FPGATest:
     learn_rate = 0.005
     regulation_strength = 0.002
 
-    act_1 = []
-    act_2 = []
-    bias_1 = []
-    bias_2 = []
-    weights_1 = []
-    weights_2 = []
-    act_out_2 = []
-    act_out_2_cpu = []
+    act = {}
+    act_cpu = {}
+    bias = {}
+    weights = {}
+
     ground_truth = []
 
-    act_1Array = None
-    act_2Array = None
-    bias_1Array = None
-    bias_2Array = None
-    weights_1Array = None
-    weights_2Array = None
-    act_out_2Array = None
+    act_buffers = {}
+    bias_buffers = {}
+    weights_buffers = {}
 
     def __init__(self, kernel_file):
+
+        if self.layers + 1 != len(self.layer_height):
+            print("Bad network config.")
+            exit()
+
+        print("Running with {} hidden layers and {} layers total.".format(self.hidden_layers,self.layers))
+
         print("OpenCL Version v{}".format(".".join([str(i) for i in cl.get_cl_header_version()])))
         print("Finding platform....")
         platform = self.findPlatform(VENDOR_NAME)
@@ -105,12 +103,12 @@ class FPGATest:
         print("Loading MNIST...")
         _, (self.x_test, self.y_test) = mnist.load_data()
 
-        self.x_test = self.x_test.reshape(10000, self.rows_in_1)
[…]

### 2018-06-29 SimpleNN/train.py

@@ -37,9 +37,9 @@ y_train = keras.utils.to_categorical(y_train, num_classes)
 y_test = keras.utils.to_categorical(y_test, num_classes)
 
 model = Sequential()
-model.add(Dense(128, activation='relu', input_shape=(784,)))
+model.add(Dense(512, activation='relu', input_shape=(784,)))
 # model.add(Dropout(0.2))
-# model.add(Dense(512, activation='relu'))
+model.add(Dense(512, activation='relu'))
 # model.add(Dropout(0.2))
 model.add(Dense(num_classes, activation='softmax'))
 
@@ -62,6 +62,6 @@ i = 0
 for layer in model.layers:
     data = {"weights": layer.get_weights()[0], "bias": layer.get_weights()[1]}
 
-    pickle.dump(data, open("layer_h128_{}.p".format(i), "wb"))
+    pickle.dump(data, open("layer_test2_{}.p".format(i), "wb"))
 
     i = i + 1

### 2018-06-29 SWoPP2018 Paper/paper.tex
Paper additions.

@@
 So a block is fetched from the activations and the wieghts and place in the block RAM on the FPGA.
-The block RAM is much faster then the global memory.
+The block RAM has a much lower latency than the global memory.
 This speeds up through put by a large margin.
@@
 The used example network is a simple multilayer perceptron.
-The main dataset used was MNIST.
-The input layer is has 128 outputs, adn the final layer 10 class outputs.
-So in total a two layer network, or two sets of weight matrices and bias vectors.
+The main dataset used was MNIST, so 784 input features.
+The structure of the sample MNIST network is.
+\begin{enumerate}
+  \item Dense(512)
+  \item Relu
+  \item Dense(512)  
+  \item Relu
+  \item Dense(10)
+  \item Softmax
+\end{enumerate}
+So in total a three layer network, or threes sets of weight matrices and bias vectors.
 The data set was trained using the first \num{50000} images from the MNIST dataset.
 The last \num{10000} images are used as the test data set.
-Training was done using a batch size of 128.
+Training was done using a batch size of \num{128}.
 The CPU code was implemented using the NumPy array.dot function.
@@
 \section{Results}\label{sec:result}
-The host (numpy based) code benchmarked at \num{41} GFLOPS for simple inference.
-Our first naive implementation clocked about \num{2.5} GFLOPS for this problem size.
+The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference.
+A first naive implementation clocked about \num{2.5} GFLOPS for this problem size.
 The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
@@
     \midrule
-    128$\times$128 & \num{0}  \\
-    100$\times$100 & \num{0} \\
+    128$\times$128 & \num{0}  \\ % Too big
+    100$\times$100 & \num{0} \\ % Too big (86 is also too big)
     84$\times$84 & \num{0}  \\
-    64$\times$64 & \num{14.3}  \\
+    64$\times$64 & \num{17.8}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network: [28 * 28, 512, 512, 10]
     32$\times$32 & \num{0}  \\
-    16$\times$16 & \num{4.1}  \\
+    16$\times$16 & \num{4.3}  \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network: [28 * 28, 512, 512, 10]
     \bottomrule
@@
     84$\times$84 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    64$\times$64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\
+    64$\times$64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx
     32$\times$32 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    16$\times$16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\
+    16$\times$16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx
     \bottomrule

### 2018-07-01 SWoPP2018 Paper/paper.tex
Added CIFAR training and inference.
Accuracy is really bad.

@@
 The used example network is a simple multilayer perceptron.
-The main dataset used was MNIST, so 784 input features.
+The first dataset used was MNIST, so \num{784} input features.
 The structure of the sample MNIST network is.
@@
 So in total a three layer network, or threes sets of weight matrices and bias vectors.
-The data set was trained using the first \num{50000} images from the MNIST dataset.
+The data set was trained using the first \num{60000} images from the MNIST dataset.
 The last \num{10000} images are used as the test data set.
-Training was done using a batch size of \num{128}.
+The second dataset used was CIFAR10, so \num{3072} input features.
+The structure of the sample CIFAR10 network is.
+\begin{enumerate}
+  \item Dense(1024)
+  \item Relu
+  \item Dense(512)  
+  \item Relu
+  \item Dense(512)  
+  \item Relu
+  \item Dense(10)
+  \item Softmax
+\end{enumerate}
+
+The data set was trained using the first \num{50000} images form the dataset.
+The last \num{10000} images were used as the test data set.
+All training was done using a batch size of \num{128}.
 The CPU code was implemented using the NumPy array.dot function.
@@
 \section{Results}\label{sec:result}
-The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference.
-A first naive implementation clocked about \num{2.5} GFLOPS for this problem size.
+The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
+A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
 The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
+Larger block sizes would exhaust the block RAM on the used FPGA device.
+The next logical size up from \num{64} would be \num{84} (\num{3}$\cdot$\num{28}), this would use to much of the block RAM already.
 
@@
   \caption{FPGA Kernel performance}\label{tab:kernel-performance}
-  \begin{tabular}{ll}
+  \begin{tabular}{llll}
     \toprule
-    \textbf{Block size} & \textbf{GFLOPS}  \\
+    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR10}  \\
     \midrule
-    128$\times$128 & \num{0}  \\ % Too big
-    100$\times$100 & \num{0} \\ % Too big (86 is also too big)
-    84$\times$84 & \num{0}  \\
-    64$\times$64 & \num{17.8}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network: [28 * 28, 512, 512, 10]
-    32$\times$32 & \num{0}  \\
-    16$\times$16 & \num{4.3}  \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network: [28 * 28, 512, 512, 10]
+    64$\times$64 & \num{17.8} & \num{18.9}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    16$\times$16 & \num{4.3} & \num{4.4} \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
     \bottomrule
@@
 \end{table}
+
+The performance is memory bandwidth limited for these kernels.
 
@@
     \midrule    
-    128$\times$128 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    100$\times$100 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
-    84$\times$84 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
     64$\times$64 & \SI{33}{\percent} & \SI{10}{\percent} & \SI{68}{\percent} & \SI{172.8}{\mega\hertz}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx
-    32$\times$32 & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\percent} & \SI{0}{\mega\hertz}  \\
     16$\times$16 & \SI{17}{\percent} & \SI{3}{\percent} & \SI{30}{\percent} & \SI{209.16}{\mega\hertz}  \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx
@@
 \subsection{Training Performance}
-The accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
+The MNIST network accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
+And the CIFAR10 accuracy after training is \SI{47.9}{\percent}
 The FPGA gets slightly different floaing point results due to rounding differences but is matches the accuracy.
@@
 \section{Conclusion}\label{sec:conclusion}
+This framework makes for a good basis to start some research in different number
 

### 2018-07-01 SimpleNN/fpga_test.py

@@ -6,7 +6,7 @@ from sys import platform
 import time
 import math
 import keras
-from keras.datasets import mnist
+from keras.datasets import cifar10 as input_data
 import pickle
 import sys
 
@@ -20,19 +20,14 @@ NN_T = np.float32
 
 
 class FPGATest:
-    hidden_layers = 1
+    hidden_layers = 2
     layers = hidden_layers + 2
 
-    LAYER_FILENAME = "layer_test2_{0}.p"
+    LAYER_FILENAME = "layer_cifar_{0}.p"
     minibatch_size = 10000
 
-    layer_height = [28 * 28, 512, 512, 10]
-
-    fpga_iter = 20
-    cpu_iter = 20
-
-    data_max = 1
-    data_min = -data_max
+    #layer_height = [28 * 28, 512, 512, 10] # MNIST
+    layer_height = [32 * 32 * 3, 1024, 512, 512, 10] # CIFAR-10
 
     learn_rate = 0.005
     regulation_strength = 0.002
@@ -100,15 +95,14 @@ class FPGATest:
 
         self.queue = cl.CommandQueue(self.ctx)
 
-        print("Loading MNIST...")
-        _, (self.x_test, self.y_test) = mnist.load_data()
+        print("Loading data...")
+        _, (self.x_test, self.y_test) = input_data.load_data()
 
+        self.y_test = self.y_test.reshape((10000,))
         self.x_test = self.x_test.reshape(10000, self.layer_height[0])
         self.x_test = self.x_test.astype('float32')
         self.x_test /= 255
-        # print(self.x_test[0])
 
-        # self.y_test = keras.utils.to_categorical(self.y_test, self.rows_out_2)
         self.correct_pred_fpga = 0
         self.wrong_pred_fpga = 0
         self.correct_pred_cpu = 0
@@ -226,7 +220,6 @@ class FPGATest:
 
             # Load layer file
             layer_file = pickle.load(open(self.LAYER_FILENAME.format(layer), 'rb'))
-
             # Layer weights
             self.weights[layer] = self.aligned(layer_file['weights'].reshape(size_weights), alignment=64)
             self.bias[layer] = self.aligned(layer_file['bias'].reshape(size_bias), alignment=64)
@@ -253,6 +246,8 @@ class FPGATest:
                                    alignment=64)
         self.act_cpu[0] = self.aligned(self.x_test[batch * self.minibatch_size:(batch + 1) * self.minibatch_size, :],
[…]

### 2018-07-01 SimpleNN/trainCIFAR.py

@@ -1,0 +1,79 @@
+"""Trains a simple deep NN on the MNIST dataset.
+
+Gets to 98.40% test accuracy after 20 epochs
+(there is *a lot* of margin for parameter tuning).
+2 seconds per epoch on a K520 GPU.
+"""
+
+from __future__ import print_function
+
+# Install the plaidml backend
+import plaidml.keras
+plaidml.keras.install_backend()
+
+import keras
+from keras.datasets import cifar10
+from keras.models import Sequential
+from keras.layers import Dense, Activation, Dropout
+
+import pickle
+import numpy
+
+batch_size = 128
+num_classes = 10
+epochs = 200
+
+# the data, split between train and test sets
+(x_train, y_train), (x_test, y_test) = cifar10.load_data()
+
+x_train = x_train.reshape(50000, 32 * 32 * 3)
+x_test = x_test.reshape(10000, 32 * 32 * 3)
+x_train = x_train.astype('float32')
+x_test = x_test.astype('float32')
+x_train /= 255
+x_test /= 255
+print(x_train.shape[0], 'train samples')
+print(x_test.shape[0], 'test samples')
+
+# convert class vectors to binary class matrices
+y_train = keras.utils.to_categorical(y_train, num_classes)
+y_test = keras.utils.to_categorical(y_test, num_classes)
+
+model = Sequential()
+model.add(Dense(1024, input_shape=(32 * 32 * 3,)))
+model.add(Activation('relu'))
+model.add(Dropout(0.2))
+
+model.add(Dense(512))
+model.add(Activation('relu'))
+model.add(Dropout(0.2))
+
+model.add(Dense(512))
+model.add(Activation('relu'))
+model.add(Dropout(0.2))
+
+model.add(Dense(num_classes))
+model.add(Activation('softmax'))
+
+model.compile(loss='categorical_crossentropy',
+              optimizer='adam',
+              metrics=['accuracy'])
+
+model.summary()
+
+history = model.fit(x_train, y_train,
+                    batch_size=batch_size,
+                    epochs=epochs,
+                    verbose=1,
+                    validation_data=(x_test, y_test))
+score = model.evaluate(x_test, y_test, verbose=0)
+print('Test loss:', score[0])
+print('Test accuracy:', score[1])
+
+i = 0
+for layer in model.layers:
+    data = {"weights": layer.get_weights()[0], "bias": layer.get_weights()[1]}
+
+    pickle.dump(data, open("layer_cifar_{}.p".format(i), "wb"))
+
+    i = i + 1

### 2018-07-01 SimpleNN/trainMNIST.py

@@ -7,6 +7,9 @@ Gets to 98.40% test accuracy after 20 epochs
 
 from __future__ import print_function
 
+import plaidml.keras
+plaidml.keras.install_backend()
+
 import keras
 from keras.datasets import mnist
 from keras.models import Sequential
@@ -62,6 +65,6 @@ i = 0
 for layer in model.layers:
     data = {"weights": layer.get_weights()[0], "bias": layer.get_weights()[1]}
 
-    pickle.dump(data, open("layer_test2_{}.p".format(i), "wb"))
+    pickle.dump(data, open("layer_mnist_{}.p".format(i), "wb"))
 
     i = i + 1

### 2018-07-02 SWoPP2018 Paper/paper.tex
Added some extra text.

@@
 For perfomance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
-The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that formats, and an FPGA is better at accomodating that without a huge performance impact.
+The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accomodating that without a huge performance impact.
 
@@
 \subsubsection{Design decisions}
-One of the main choices with the largests effect on implementation as whenever to keep all weight matrices in memory transposed.
-During inference this is very benificial, this makes most reads sequential.
+One of the main choices with the largests effect on implementation is whenever to keep all weight matrices in memory transposed.
+During inference this is very benificial, as this makes most reads sequential.
 During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
@@
 The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
-Larger block sizes would exhaust the block RAM on the used FPGA device.
-The next logical size up from \num{64} would be \num{84} (\num{3}$\cdot$\num{28}), this would use to much of the block RAM already.
 
@@
 The kernel resource utilization is shown in \cref{tab:fpga-util}.
+The main limiting factor is the available block RAM.
+To stop the calculation of extra padding lines in the matrices, the blocksize should be a multiple of most of the layer sizes.
+Larger block sizes would exhaust the block RAM on the used FPGA device.
+The next logical size up from \num{64} would be \num{84} (\num{3}$\cdot$\num{28}), this would use to much of the block RAM already.
+This is becasue there are three block buffers and the relationship between blocksize and used block RAM is square.
 
@@
 \section{Conclusion}\label{sec:conclusion}
-This framework makes for a good basis to start some research in different number
+This framework makes for a good basis to start some research into different number formats.
+CPU emulations of different formats reach very low performances.
+So the expect to reach about similar performance on FPGA implementation using alternative floating point formats. %TODO Arthur performance metrics?
 

### 2018-07-02 SimpleNN/trainCIFAR.py

@@ -42,15 +42,12 @@ y_test = keras.utils.to_categorical(y_test, num_classes)
 model = Sequential()
 model.add(Dense(1024, input_shape=(32 * 32 * 3,)))
 model.add(Activation('relu'))
-model.add(Dropout(0.2))
 
 model.add(Dense(512))
 model.add(Activation('relu'))
-model.add(Dropout(0.2))
 
 model.add(Dense(512))
 model.add(Activation('relu'))
-model.add(Dropout(0.2))
 
 model.add(Dense(num_classes))
 model.add(Activation('softmax'))

### 2018-07-02 SWoPP2018 Paper/paper.tex
Small changes.

@@
     Intel i7-3930K & \SI{3.20}{\giga\hertz} \\
-    Host RAM & DDR3-\SI{1333}{\mega\hertz} Dual Channel \\
+    DDR3 RAM & \SI{1333}{\mega\hertz} Dual Channel \\
     Arria 10 ($\times$1) & Nallatech 510T \\
@@
 \begin{enumerate}
-  \item Dense(512)
-  \item Relu
-  \item Dense(512)  
-  \item Relu
-  \item Dense(10)
-  \item Softmax
+  \item Dense(512)  \(\to\)  Relu
+  \item Dense(512)  \(\to\)  Relu
+  \item Dense(10)  \(\to\)  Softmax
 \end{enumerate}
@@
 \begin{enumerate}
-  \item Dense(1024)
-  \item Relu
-  \item Dense(512)  
-  \item Relu
-  \item Dense(512)  
-  \item Relu
-  \item Dense(10)
-  \item Softmax
+  \item Dense(1024)  \(\to\)  Relu
+  \item Dense(512)  \(\to\)  Relu
+  \item Dense(512)  \(\to\)  Relu
+  \item Dense(10)  \(\to\)  Softmax
 \end{enumerate}
 
-The data set was trained using the first \num{50000} images form the dataset.
+The data set was trained using the first \num{50000} images from the dataset.
 The last \num{10000} images were used as the test data set.

### 2018-07-02 SWoPP2018 Paper/paper.tex
Changed the title and small additon of one extra data point.

@@
 
-\title{Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}
+\title{Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}
 
@@
 A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
+Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.
 The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
@@
 CPU emulations of different formats reach very low performances.
-So the expect to reach about similar performance on FPGA implementation using alternative floating point formats. %TODO Arthur performance metrics?
+Due to the FPGA's ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
 

### 2018-07-02 SWoPP2018 Paper/paper.tex
Changed framework text.

@@
 \subsection{FPGA NN Framework}
-A small framework was built, consisting of multiple kernels.
-One simple forward propagation kernel with optional Relu activation function integrated into it and a forward softmax kernel.
+The goal of this framework is generality, in so far that when finished one can select which numerical format one wants to use and then compile the OpenCL kernel for that format.
+While keeping the same API, so easier comparative research can be done on training performance using the different formats.
+
 \subsubsection{Design overview}
@@
 During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
-But since the artihmetic density of training is higher, the effect might be slightly less pronounced.
+But since the artihmetic density of the training process is higher, the effect might be slightly less pronounced.
 

### 2018-07-02 SWoPP2018 Paper/paper.tex
Went over the paper with spellcheck.

@@
 
-The recent explosion in artificial intelligence – in particular that of deep neural networks based on backpropagation – has triggered a storm in the introduction and creation of specialized compute devices.
+The recent explosion in artificial intelligence – in particular that of deep neural networks based on back-propagation – has triggered a storm in the introduction and creation of specialized compute devices.
 Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high-performance Deep-Learning (DL) training and/or inference.
 Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
-It is clear that Artifical Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
+It is clear that Artificial Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
 
@@
 The IEEE-754 floating-point representation is one of the few relics still used unchanged in computing today.
-Reducing the size of the floating-point representation can have dramatical (and positive) impacts on the performance: more compute per unit silicon, more compute per unit bandwidth, and lower power consumption.
+Reducing the size of the floating-point representation can have dramatic (and positive) impacts on the performance: more compute per unit silicon, more compute per unit bandwidth, and lower power consumption.
 Several alternatives to the IEEE-754 format are indeed emerging, such as Microsoft’s Deep-Learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
@@
 Furthermore, simulating alternative numerical formats in software are incapable of using any compiler optimizations, nor can they leverage the vector instruction often crucial to reach application performance in modern processors.
-Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.\`calling convention).
+Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.\ calling convention).
 
@@
 Commercially most vendors do support some form of reduced precision mode.
-Intel’s Knight’s Milll~\cite{knm} architecture replaces one of the AVX-512 vector units of Knight’s Landing with a Vector Neural Network Instruction (VNNI) unit, capable of performing dot-products in a mixed IEEE-754 16-bit and 32-bit mode.
+Intel’s Knight’s Mill~\cite{knm} architecture replaces one of the AVX-512 vector units of Knight’s Landing with a Vector Neural Network Instruction (VNNI) unit, capable of performing dot-products in a mixed IEEE-754 16-bit and 32-bit mode.
 A similar process (reduced precision multiplication, full precision accumulation) is also applied in NVIDIA’s Volta-100 line GPUs.
@@
 
-FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementating a hardware design before taping out full chip.
+FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementing a hardware design before taping out full chip.
 They are devices that can represent reconfigurable hardware.
@@
 The goal of this framework is generality, in so far that when finished one can select which numerical format one wants to use and then compile the OpenCL kernel for that format.
-While keeping the same API, so easier comparative research can be done on training performance using the different formats.
+%TODO OpenCL explanation
+While keeping the same API, so easier comparative research can be done on training performance using the different formats. % TODO Figure (Arthur?)
 
@@
 The backwards kernels are a work in progress, so for now we use an external training script.
-The host code, written in python, does a kernel call for every layer.
+The backwards kernels are the kernels that calculate the error and back propagate the error while updating the weights and biases in the network used during training.
+During inference the host code, written in python, does one forward kernel call for every layer.
 And does a final softmax kernel call to get the final prediction.
-For perfomance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
-The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accomodating that without a huge performance impact.
+For performance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
+The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating that without a huge performance impact.
 
@@
 \subsubsection{Design details}
-All weight matrices are transposed in memory.
+All weight matrices are transposed in memory, this to optimized the memory access pattern of the matrix-matrix multiplication.
 The main inference is done using an blocking implementation of the matrix multiplication.
-So a block is fetched from the activations and the wieghts and place in the block RAM on the FPGA.
+So a block is fetched from the activations and the weights and placed in the block RAM on the FPGA.
+The computation result is also stored on the block RAM, before a routine writes it back to global memory.
 The block RAM has a much lower latency than the global memory.
-This speeds up through put by a large margin.
+This speeds up throughput by a large margin.
 Block RAM is equivalent to the shared or local memory of contemporary GPUs.
@@
 \subsubsection{Design decisions}
-One of the main choices with the largests effect on implementation is whenever to keep all weight matrices in memory transposed.
-During inference this is very benificial, as this makes most reads sequential.
-During training, using stochastic gradient descent, this can be a problem, the weight matrix should now be transposed back.
-But since the artihmetic density of the training process is higher, the effect might be slightly less pronounced.
+One of the main choices with the largest effect on implementation is whenever to keep all weight matrices in memory transposed.
+During inference this is very beneficial, as this makes most reads sequential.
+In early stages of development it sped up the kernel performance by a factor of \num{3}.
+During training, using stochastic gradient descent, this can be a problem though, the weight matrix should now be transposed back for the most efficient memory access patterns.
+But since the arithmetic density of the training process is higher, the effect might be slightly less pronounced.
+An other decision was to take the most outer loop, the loop over all the layers, to the host.
+This loop can not be pipelined since there is serial dependency, so it makes more sense execute this loop on the host CPU.
+This both saves space on the FPGA and it simplifies the generated hardware.
 
@@
 The used example network is a simple multilayer perceptron.
-The first dataset used was MNIST, so \num{784} input features.
+The first data set used was MNIST, so \num{784} input features.
 The structure of the sample MNIST network is.
@@
 So in total a three layer network, or threes sets of weight matrices and bias vectors.
-The data set was trained using the first \num{60000} images from the MNIST dataset.
+The data set was trained using the first \num{60000} images from the MNIST data set.
 The last \num{10000} images are used as the test data set.
-The second dataset used was CIFAR10, so \num{3072} input features.
+The second data set used was CIFAR10, so \num{3072} input features.
 The structure of the sample CIFAR10 network is.
@@
 
-The data set was trained using the first \num{50000} images from the dataset.
+The data set was trained using the first \num{50000} images from the data set.
 The last \num{10000} images were used as the test data set.
@@
 \section{Results}\label{sec:result}
-The host (numpy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
+The host (NumPy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
 A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
-Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.
+Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
 The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
@@
 The main limiting factor is the available block RAM.
-To stop the calculation of extra padding lines in the matrices, the blocksize should be a multiple of most of the layer sizes.
+To stop the calculation of extra padding lines in the matrices, the block size should be a multiple of most of the layer sizes.
 Larger block sizes would exhaust the block RAM on the used FPGA device.
-The next logical size up from \num{64} would be \num{84} (\num{3}$\cdot$\num{28}), this would use to much of the block RAM already.
-This is becasue there are three block buffers and the relationship between blocksize and used block RAM is square.
+The next logical size up from \num{64} would be \num{84} (\num{3}\(\times\)\num{28}), this would use to much of the block RAM already.
+This is because there are three block buffers and the relationship between block size and used block RAM is square.
 
@@
   \centering
-  \caption{FPGA Hardware utilisation for different blocksizes}\label{tab:fpga-util}
+  \caption{FPGA Hardware utilization for different block sizes}\label{tab:fpga-util}
   \begin{tabular}{lllll}
@@
 And the CIFAR10 accuracy after training is \SI{47.9}{\percent}
-The FPGA gets slightly different floaing point results due to rounding differences but is matches the accuracy.
+The FPGA gets slightly different floating point results due to rounding differences but is matches the accuracy.
 
@@
 CPU emulations of different formats reach very low performances.
-Due to the FPGA's ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
+Due to the FPGAs ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
 

### 2018-07-02 SWoPP2018 Paper/paper.tex
Small additions.

@@
 \subsection{Network Tested + Data-set}
-The used example network is a simple multilayer perceptron.
-The first data set used was MNIST, so \num{784} input features.
+The used example networks are a simple multi-layer perceptron.
+So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.
+These layers are often called ``Dense'' layers.
+The first data set used was MNIST, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
+So the data set provides \num{784} input features.
 The structure of the sample MNIST network is.

### 2018-07-03 SWoPP2018 Paper/paper.tex
added ann introduction + picture

@@
 
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\linewidth]{example_ann-crop.pdf}
+  \caption{The basics of artificial ``deep'' neural networks, showing the input (a) layer, the hidden (b) layer, and the output (c-d) layer.}\label{fig:ann-example}
+\end{figure}
+
 \subsection{Neural Networks}
-Intro to neural networks.
-%TODO
+An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system-- a system built around the concepts of \textit{neuron} as the main computational agents.
+Figure~\ref{fig:ann-example} illustrates an example of a typical “deep” neural network: a network that consists of a input layer, and output layer, and a number of \textit{hidden} layers in-between.
+The number of hidden layers in modern neural networks can be very large: AlexNet (2012)~\cite{krizhevsky2012imagenet} has eight, VGG16 (2014)~\cite{simonyan2014very} has 16 layers, GoogleNet (2014)~\cite{szegedy2015going} has 22 layers, and ResNet (2016)~\cite{he2016deep} has 152 layers.
+The trend tend seem to go towards larger and deeper neural network.
+The input layer of a neural network (in our example, a classifier) contains the (possibly preprocessed) inputs, such as images (for image recognition), words (in natural language processoing), or motifs (in graph processing).
+In our humble example, the input is an image of an apple, where each pixel has an all-to-all connection to the hidden layer-- a so-called \textit{dense} layer.
+The dense-layer (or fully-connected layer) is the most basic of all layers, and nearly all (e.g.
+convolution) layers are derived from it.
+Each layers consists of a number of \textit{neurons} – the main compute agent of the network.
+Each edge that connect to a particular neuron is called a \textit{synapse}, and comes with a \textit{weight}($w_{i,j}$ in the figure, where $i$ is the index of the neuron).
+The neuron integrates the weights (Figure~\ref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies a activation function to compute the output of the neuron.
+The activation function can varies between networks, but commonly used activation functions include: the sigmoid ($f(x) = \frac{1}{1+e^{-x}}$), the rectifier (ReLu, $f(x) = max(0,x)$), or hyperbolic tangent ($f(x) = tanh(x)$).
+In Figure~\ref{fig:ann-example}:b (and commonly in image processing network), the simple and compute-\textit{in}expensive ReLu activation function is used in the hidden-layers of the network.
+The final layer of our classifier neural network is an output layer, Figure~\ref{fig:ann-example}:c.
+In the output layer, the activation function is often a \textit{softmax} (Figure~\ref{fig:ann-example}:d), which scales all outputs such that their sum equals one.
+
+Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer -- from the front to the back of the network-- and propagating the output of each layer into the subsequent.
+This effort is called \textit{forward propagation}.
+Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
+At this point in time, our framework focuses on forward propagation.
 
@@
 
+\bibitem{simonyan2014very}
+    Simonyan, Karen and Zisserman, Andrew:
+    Very deep convolutional networks for large-scale image recognition,
+    {\it arXiv preprint arXiv:1409.1556},
+    2014
+
+\bibitem{szegedy2015going}
+    Szegedy, Christian and Liu, Wei and Jia, Yangqing and Sermanet, Pierre and Reed, Scott and Anguelov, Dragomir and Erhan, Dumitru and Vanhoucke, Vincent and Rabinovich, Andrew:
+    Going deeper with convolutions,
+    {\it Proceedings of the IEEE conference on computer vision and pattern recognition},
+    pp 1--9, 2015
+
+\bibitem{he2016deep}
+    He, Kaiming and Zhang, Xiangyu and Ren, Shaoqing and Sun, Jian:
+    Deep residual learning for image recognition,
+    {\it Proceedings of the IEEE conference on computer vision and pattern recognition},
+    pp 770--778, 2016
+
 \end{thebibliography}

### 2018-07-03 SWoPP2018 Paper/paper.tex
added framework overview

@@
 
-\subsection{FPGA NN Framework}
-The goal of this framework is generality, in so far that when finished one can select which numerical format one wants to use and then compile the OpenCL kernel for that format.
-%TODO OpenCL explanation
-While keeping the same API, so easier comparative research can be done on training performance using the different formats. % TODO Figure (Arthur?)
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=\linewidth]{training_overview.pdf}
+  \caption{Overview over our framework, showing blocks existing (white) and components currently worked on (gray)}\label{fig:overview}
+\end{figure*}
+
+\subsection{FPGA Neural Network Framework}
+We aspire to create a neural network framework that allows design-space exploration with different numerical data formats.
+Our framework, illustrated in Figure~\ref{fig:overview}, consists of a number of components.
+We have chosen to rely on Python as the high-level frontend for our frameowork.
+It is through python that a user create a networks, selects inputs, and decides what data formats to use.
+Once a particular configuration is selected, our framework generates data-type oblivious training and inference code that targets Intel's OpenCL SDK for FPGAs.
+By data-type oblivious we mean that all operations associated with any particular data-type representation remain unresolved at the point of creation, as they will not depend on any of the native data-types or functionality of the OpenCL language.
+Instead, our Python framework invokes a Data-type selector, which automatically generates a low-level hardware description lanague (HDL) library that contain commonly used operators for the selected data-type.
+Once the Register-Transfer Level (RTL) library has been generated, it is merged with the data-type oblivious OpenCL template to yield the final description, which now can be synthesized using EDA tools and used.
+Invisible to the user, our host runtime system handles all communication, invocation and control over the FPGA from the host side.
+
+The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.
 

### 2018-07-03 SWoPP2018 Paper/paper.tex
ChkTeX warnings fixed. Spellcheck.

@@
 An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system-- a system built around the concepts of \textit{neuron} as the main computational agents.
-Figure~\ref{fig:ann-example} illustrates an example of a typical “deep” neural network: a network that consists of a input layer, and output layer, and a number of \textit{hidden} layers in-between.
+\Cref{fig:ann-example} illustrates an example of a typical “deep” neural network: a network that consists of a input layer, and output layer, and a number of \textit{hidden} layers in-between.
 The number of hidden layers in modern neural networks can be very large: AlexNet (2012)~\cite{krizhevsky2012imagenet} has eight, VGG16 (2014)~\cite{simonyan2014very} has 16 layers, GoogleNet (2014)~\cite{szegedy2015going} has 22 layers, and ResNet (2016)~\cite{he2016deep} has 152 layers.
 The trend tend seem to go towards larger and deeper neural network.
-The input layer of a neural network (in our example, a classifier) contains the (possibly preprocessed) inputs, such as images (for image recognition), words (in natural language processoing), or motifs (in graph processing).
+The input layer of a neural network (in our example, a classifier) contains the (possibly pre-processed) inputs, such as images (for image recognition), words (in natural language processing), or motifs (in graph processing).
 In our humble example, the input is an image of an apple, where each pixel has an all-to-all connection to the hidden layer-- a so-called \textit{dense} layer.
-The dense-layer (or fully-connected layer) is the most basic of all layers, and nearly all (e.g.
-convolution) layers are derived from it.
+The dense-layer (or fully-connected layer) is the most basic of all layers, and nearly all (e.g.\ convolution) layers are derived from it.
 Each layers consists of a number of \textit{neurons} – the main compute agent of the network.
-Each edge that connect to a particular neuron is called a \textit{synapse}, and comes with a \textit{weight}($w_{i,j}$ in the figure, where $i$ is the index of the neuron).
-The neuron integrates the weights (Figure~\ref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies a activation function to compute the output of the neuron.
-The activation function can varies between networks, but commonly used activation functions include: the sigmoid ($f(x) = \frac{1}{1+e^{-x}}$), the rectifier (ReLu, $f(x) = max(0,x)$), or hyperbolic tangent ($f(x) = tanh(x)$).
-In Figure~\ref{fig:ann-example}:b (and commonly in image processing network), the simple and compute-\textit{in}expensive ReLu activation function is used in the hidden-layers of the network.
-The final layer of our classifier neural network is an output layer, Figure~\ref{fig:ann-example}:c.
-In the output layer, the activation function is often a \textit{softmax} (Figure~\ref{fig:ann-example}:d), which scales all outputs such that their sum equals one.
+Each edge that connect to a particular neuron is called a \textit{synapse}, and comes with a \textit{weight} (\(w_{i,j}\)) in the figure, where \(i\) is the index of the neuron).
+The neuron integrates the weights (\cref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies a activation function to compute the output of the neuron.
+The activation function can varies between networks, but commonly used activation functions include: the sigmoid (\(f(x) = \frac{1}{1+e^{-x}}\)), the rectifier (ReLu, \(f(x) = max(0,x)\)), or hyperbolic tangent (\(f(x) = tanh(x)\)).
+In \cref{fig:ann-example}:b (and commonly in image processing network), the simple and compute-\textit{in}expensive ReLu activation function is used in the hidden-layers of the network.
+The final layer of our classifier neural network is an output layer, \cref{fig:ann-example}:c.
+In the output layer, the activation function is often a \textit{softmax} (\cref{fig:ann-example}:d), which scales all outputs such that their sum equals one.
 
-Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer -- from the front to the back of the network-- and propagating the output of each layer into the subsequent.
-This effort is called \textit{forward propagation}.
-Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
+Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer --from the front to the back of the network-- and propagating the output of each layer into the subsequent.
+This effort is called \textit{forward propagation}. Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
 At this point in time, our framework focuses on forward propagation.
@@
 We aspire to create a neural network framework that allows design-space exploration with different numerical data formats.
-Our framework, illustrated in Figure~\ref{fig:overview}, consists of a number of components.
-We have chosen to rely on Python as the high-level frontend for our frameowork.
+Our framework, illustrated in \cref{fig:overview}, consists of a number of components.
+We have chosen to rely on Python as the high-level frontend for our framework.
 It is through python that a user create a networks, selects inputs, and decides what data formats to use.
@@
 By data-type oblivious we mean that all operations associated with any particular data-type representation remain unresolved at the point of creation, as they will not depend on any of the native data-types or functionality of the OpenCL language.
-Instead, our Python framework invokes a Data-type selector, which automatically generates a low-level hardware description lanague (HDL) library that contain commonly used operators for the selected data-type.
+Instead, our Python framework invokes a Data-type selector, which automatically generates a low-level hardware description language (HDL) library that contain commonly used operators for the selected data-type.
 Once the Register-Transfer Level (RTL) library has been generated, it is merged with the data-type oblivious OpenCL template to yield the final description, which now can be synthesized using EDA tools and used.

### 2018-07-03 SWoPP2018 Paper/paper.tex
Fixed weird margin issues with the bibliography, added some text on FGPAs and the II.

@@
   \usepackage{latexsym}
-  \usepackage{url}
+  \usepackage[hyphens]{url}
+  \Urlmuskip=0mu plus 1mu
 
@@
 They are devices that can represent reconfigurable hardware.
+A normal FPGA work-flow consists of writing in a hardware description language.
+Then synthesizing the design and finally placing and routing the design.
+This is a lengthy process and complex designs in hardware description languages are hard to maintain.
+In this work we will focus on using the OpenCL interface to the FPGA.
+OpenCL is a framework specified by the Khronos Group\footnote{Specification available at: \url{https://www.khronos.org/opencl/}} in 2009, to work with all kinds of processors, accelerators and other heterogenous compute devices, in recent years the FPGA vendors have made efforts to make it easier to leverage FPGA resources by computer scientists and not only hardware designers.
+So OpenCL is one of the ways to leverage high level synthesis.
+High level synthesis take a design specification in a high level language like C or in this case the modified version of C99 that is used for OpenCL kernels.
+And the synthesizer makes an RTL design description from this design automatically after which the normal work-flow is resumed.
 
-The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAM and look up tables, in any way possible.
+FPGAs are made up of a reconfigurable fabric.
+The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAMs and LUTs, in any way possible.
+The LUTs can be used to implement any mathematical function, like addition, logical function et cetera.
 This makes them very suitable for the research described in this paper.
-It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting.
+It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting without having to resort to software simulations and the performance limitations that follow from that.
 
@@
 The number of hidden layers in modern neural networks can be very large: AlexNet (2012)~\cite{krizhevsky2012imagenet} has eight, VGG16 (2014)~\cite{simonyan2014very} has 16 layers, GoogleNet (2014)~\cite{szegedy2015going} has 22 layers, and ResNet (2016)~\cite{he2016deep} has 152 layers.
-The trend tend seem to go towards larger and deeper neural network.
+The trend tend seem to go towards larger and deeper neural networks.
 The input layer of a neural network (in our example, a classifier) contains the (possibly pre-processed) inputs, such as images (for image recognition), words (in natural language processing), or motifs (in graph processing).
@@
 
+The OpenCL SDK from Intel used for this design, tries to pipeline loops in single work item kernels, as opposed to NDRange kernels. % Reference to Intel OpenCL Manual?
+To get maximum performance the aim is to get an initiation interval of one.
+That is to say that a new loop iteration is scheduled every clock cycle.
+To get this to work on the inner most loop, one that is essentially a reduction.
+An array is used to store all output in separate locations, this way the loop can be fully unrolled.
+For the containing loops, serial dependencies are to be avoided whenever possible.
+So different loop iterations are fully data-independent.
+For the outer most loop that processes one block this behavior is not possible, since the output block is written to multiple times.
+If there was enough space on the FPGA theoretically multiple blocks would be able to be processed in parallel.
+In the future the training kernel also needs to fit, so it was decided not to try parallelize this further.
+
 \subsubsection{Design decisions}
@@
     Intel Quartus & v17.1.0 \\
+    Intel OpenCL & v1.1 \\
     \bottomrule
@@
 These layers are often called ``Dense'' layers.
-The first data set used was MNIST, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
+The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
 So the data set provides \num{784} input features.
@@
 The last \num{10000} images are used as the test data set.
-The second data set used was CIFAR10, so \num{3072} input features.
-The structure of the sample CIFAR10 network is.
+
+The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, so \num{3072} input features.
+The structure of the sample CIFAR-10 network is.
 \begin{enumerate}
@@
     \toprule
-    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR10}  \\
+    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR-10}  \\
     \midrule
@@
 \subsection{Training Performance}
-The MNIST network accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
-And the CIFAR10 accuracy after training is \SI{47.9}{\percent}
+The MNIST network test set accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
+And the CIFAR-10 accuracy after training is \SI{47.9}{\percent}
 The FPGA gets slightly different floating point results due to rounding differences but is matches the accuracy.
@@
 
+\bibitem{lecun2010mnist}
+  LeCun, Yann and Cortes, Corinna and Burges, CJ:
+  MNIST handwritten digit database,
+  {\it AT\&T Labs \url{http://yann.lecun.com/exdb/mnist}},
+  Accessed: 2018-07, 2010
+
+\bibitem{krizhevsky2014cifar}
+  Krizhevsky, Alex, Vinod Nair, and Geoffrey Hinton:
+  The CIFAR-10 dataset,
+  {\it \url{http://www.cs.toronto.edu/kriz/cifar.html}},
+  Accessed: 2018-07, 2014
+
 \bibitem{msbrainwave}
   Chung, Eric and Fowers, Jeremy and Ovtcharov, Kalin and Papamichael, Michael and Caulfield, Adrian and Massengill, Todd and Liu, Ming and Lo, Daniel and Alkalay, Shlomi and Haselman, Michael and others:
-  Serving DNNs in Real Time at Datacenter Scale with Project Brainwave:
+  Serving DNNs in Real Time at Datacenter Scale with Project Brainwave,
   {\it IEEE Micro},
-  vol.
-38, number.
-2, pp 8--20, 2018
+  vol. 38, number. 2, pp 8--20, 2018
 
@@
   Google Supercharges Machine Learning Tasks with TPU Custom Chip,
-  {\it https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}
+  {\it \url{https://cloudplatform.googleblog.com/2016/05/Google-supercharges-machine-learning-tasks-with-custom-chip.html}},
   Accessed: 2018-06-25
@@
   Post-K Development and Introducing DLU - Fujitsu,
-  {\it http://www.fujitsu.com/global/Images/post-k-development-and-introducing-dlu.pdf},
+  {\it \url{http://www.fujitsu.com/global/Images/post-k-development-and-introducing-dlu.pdf}},
   2016
@@
   Artificial Intelligence Architecture,
-  {\it https://www.nvidia.com/en-us/data-center/volta-gpu-architecture/},
+  {\it \url{https://www.nvidia.com/en-us/data-center/volta-gpu-architecture/}},
   Accessed: 2018-06-25
@@
   Tearing Apart Google’s TPU 3.0 AI CoProcessor,
-  {\it https://www.nextplatform.com/2018/05/10/tearing-apart-googles-tpu-3-0-ai-coprocessor},
+  {\it \url{https://www.nextplatform.com/2018/05/10/tearing-apart-googles-tpu-3-0-ai-coprocessor}},
   Accessed: 2018-06-25
@@
   {\it Supercomputing Frontiers and Innovations},
-  vol.
-4, num.
-2, pp 71--86, 2017
+  vol. 4, num. 2, pp 71--86, 2017
 
@@
   {\it ACM Transactions on Mathematical Software (TOMS)},
-  vol.
-32, num.
-2, pp.
-13, 2007
+  vol. 32, num. 2, pp. 13, 2007
 
@@
   Intel Nervana Neural Network Processor,
-  {\it https://ai.intel.com/intel-nervana-neural-network-processor/},
+  {\it \url{https://ai.intel.com/intel-nervana-neural-network-processor/}},
   Access: 2018-06
@@
   Xilinx ML Suite,
-  {\it https://www.xilinx.com/applications/megatrends/machine-learning.html},
+  {\it \url{https://www.xilinx.com/applications/megatrends/machine-learning.html}},
   Accessed: 2018-16
@@
   {\it IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems},
-  vol.
-37, num.
-1, pp 48–60, 2018
+  vol. 37, num. 1, pp 48–60, 2018
 

### 2018-07-03 SWoPP2018 Paper/paper.tex
Updated the figure and changed the captions slightly.

@@
   \includegraphics[width=\linewidth]{training_overview.pdf}
-  \caption{Overview over our framework, showing blocks existing (white) and components currently worked on (gray)}\label{fig:overview}
+  \caption{Overview over our framework, showing blocks existing (black) and components currently worked on (gray).}\label{fig:overview}
 \end{figure*}
@@
   \includegraphics[width=\linewidth]{block-diagram.pdf}
-  \caption{Block diagram of implementation}\label{fig:block-diagram}
+  \caption{Block diagram of the implementation, On the left the host code, and on the right side the device code.
+The host side orchestrates all the computation on the device side.}\label{fig:block-diagram}
 \end{figure*}

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added Acknowledgment section
Added conclusion and acknowledgement

@@
 \section{Conclusion}\label{sec:conclusion}
-This framework makes for a good basis to start some research into different number formats.
-CPU emulations of different formats reach very low performances.
-Due to the FPGAs ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
+We have introduced and described our efforts to create a general-purpose Deep-Learning framework for design-space exploration of numerical formats.
+While still in the early stages, we have focused on generality.
+We have shown interoperability with Keras, where we can train weights offline and import them into our framework with little effort.
+We evaluated the performance and resource consumption of our design on the FPGAs, and made sure that the inferred accuracy is correct.
+We are currently working on implementing the training phase, as well as the choice of numerical format to be used in both the inference and training part of our framework.
+
+\section{Acknowledgment}\label{sec:acknowledgment}
+This work was partially supported by JSPS KAKENHI Grant Number JP16F16764, the JSPS Postdoctoral fellowship under grant P16764.
 

### 2018-07-03 SWoPP2018 Paper/paper.tex
Small cosmetic changes.

@@
 
-In the pursuit for faster and more energy efficient deep-learning architecture, there is a need to critically question the long-standing architectural design decision taken by computer architects decades ago.
+In the pursuit for faster and more energy efficient deep-learning architecture, there is a need to critically review long-standing architectural design decisions taken by computer architects decades ago.
 One of the oldest design decision concerns the representation of real-valued numbers, otherwise known as the floating-point representation.
-The IEEE-754 floating-point representation is one of the few relics still used unchanged in computing today.
+The IEEE-754 floating-point representation is one of the few relics that remain unchanged in computing today.
 Reducing the size of the floating-point representation can have dramatic (and positive) impacts on the performance: more compute per unit silicon, more compute per unit bandwidth, and lower power consumption.
@@
 
-The remainder of our paper is structure in the following way: \cref{sec:relwork} position our work against other, similar efforts.
+The remainder of our paper is structure in the following way: \cref{sec:relwork} positions our work against other, similar efforts.
 \cref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
@@
 Lately, modern deep-learning framework are having support for reduced precision training, some driven by leading FPGA vendors such as Xilinx~\cite{xilinxml}.
-Dicecco et al.~\cite{dicecco2017fpga} are are working on a framework similar to ours – training neural networks using FPGAs while modifying the numerical format.
+Dicecco et al.~\cite{dicecco2017fpga} are working on a framework similar to ours that trains neural networks using FPGAs while modifying the numerical format.
 Their work primary focus on the IEEE-754 format and convolution layers where-as we aspire to include alternative format such as posits~\cite{posits}.
@@
 The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAMs and LUTs, in any way possible.
-The LUTs can be used to implement any mathematical function, like addition, logical function et cetera.
+The LUTs can be used to implement any mathematical function, like addition, multiplication, boolean functions and more.
 This makes them very suitable for the research described in this paper.
@@
 \subsection{Neural Networks}
-An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system-- a system built around the concepts of \textit{neuron} as the main computational agents.
+An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system-- a system built around the concepts of \textit{neuron}s as the main computational agents.
 \Cref{fig:ann-example} illustrates an example of a typical “deep” neural network: a network that consists of a input layer, and output layer, and a number of \textit{hidden} layers in-between.
 The number of hidden layers in modern neural networks can be very large: AlexNet (2012)~\cite{krizhevsky2012imagenet} has eight, VGG16 (2014)~\cite{simonyan2014very} has 16 layers, GoogleNet (2014)~\cite{szegedy2015going} has 22 layers, and ResNet (2016)~\cite{he2016deep} has 152 layers.
-The trend tend seem to go towards larger and deeper neural networks.
+The trend seem to favor larger and deeper neural networks.
 The input layer of a neural network (in our example, a classifier) contains the (possibly pre-processed) inputs, such as images (for image recognition), words (in natural language processing), or motifs (in graph processing).
@@
 The neuron integrates the weights (\cref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies a activation function to compute the output of the neuron.
-The activation function can varies between networks, but commonly used activation functions include: the sigmoid (\(f(x) = \frac{1}{1+e^{-x}}\)), the rectifier (ReLu, \(f(x) = max(0,x)\)), or hyperbolic tangent (\(f(x) = tanh(x)\)).
+The activation function varies between networks, but commonly used activation functions include: the sigmoid (\(f(x) = \frac{1}{1+e^{-x}}\)), the rectifier (ReLu, \(f(x) = max(0,x)\)), or hyperbolic tangent (\(f(x) = tanh(x)\)).
 In \cref{fig:ann-example}:b (and commonly in image processing network), the simple and compute-\textit{in}expensive ReLu activation function is used in the hidden-layers of the network.
@@
 
-Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer --from the front to the back of the network-- and propagating the output of each layer into the subsequent.
+Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer --from the front to the back of the network-- and propagating the output of each layer into the next.
 This effort is called \textit{forward propagation}. Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
@@
 So different loop iterations are fully data-independent.
-For the outer most loop that processes one block this behavior is not possible, since the output block is written to multiple times.
+For the outermost loop that processes one block this behavior is not possible, since the output block is written to multiple times.
 If there was enough space on the FPGA theoretically multiple blocks would be able to be processed in parallel.
@@
 All kernels were compiled with \texttt{-O3 -fp-relaxed}.
-\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit without changing the numerical output.
+\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
 \begin{table}[h]
@@
 \subsection{Network Tested + Data-set}
-The used example networks are a simple multi-layer perceptron.
+The used example networks are multi-layer perceptron (MLP).
 So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added network drawings.

--- 2018-07-03 SWoPP2018 Paper/paper.tex
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[p]
   \centering
-  \includegraphics[width=\linewidth]{training_overview.pdf}
+  \includegraphics[width=0.7\linewidth]{training_overview.pdf}
   \caption{Overview over our framework, showing blocks existing (black) and components currently worked on (gray).}\label{fig:overview}
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[p]
   \centering
-  \includegraphics[width=\linewidth]{block-diagram.pdf}
-  \caption{Block diagram of the implementation, On the left the host code, and on the right side the device code.
+  \includegraphics[width=0.7\linewidth]{block-diagram.pdf}
+  \caption{Block diagram of the implementation, on the left the host code, and on the right side the device code.
 The host side orchestrates all the computation on the device side.}\label{fig:block-diagram}
+\end{figure*}
+
+\begin{figure*}[p]
+  \centering
+  \includegraphics[width=0.6\linewidth]{mnist-network.pdf}
+  \caption{MNIST sample network configuration}\label{fig:mnist-network}
+\end{figure*}
+\begin{figure*}[p]
+  \centering
+  \includegraphics[width=0.8\linewidth]{cifar10-network.pdf}
+  \caption{CIFAR-10 sample network configuration}\label{fig:cifar10-network}
 \end{figure*}
@@
 \subsection{Network Tested + Data-set}
-The used example networks are a simple multi-layer perceptron.
-So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.
+The used example networks are a multi-layer perceptron.
+So all layers are an array neurons and every neuron is connected to every neuron in the next layer.
 These layers are often called ``Dense'' layers.
@@
 So the data set provides \num{784} input features.
-The structure of the sample MNIST network is.
-\begin{enumerate}
-  \item Dense(512)  \(\to\)  Relu
-  \item Dense(512)  \(\to\)  Relu
-  \item Dense(10)  \(\to\)  Softmax
-\end{enumerate}
-So in total a three layer network, or threes sets of weight matrices and bias vectors.
+The structure of the sample MNIST network is shown in \cref{fig:mnist-network}.
+In total a three layer network plus the input layer, or three sets of weight matrices and bias vectors.
 The data set was trained using the first \num{60000} images from the MNIST data set.
-The last \num{10000} images are used as the test data set.
-
+The last \num{10000} images are used as the test data set.\\
 The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, so \num{3072} input features.
-The structure of the sample CIFAR-10 network is.
-\begin{enumerate}
-  \item Dense(1024)  \(\to\)  Relu
-  \item Dense(512)  \(\to\)  Relu
-  \item Dense(512)  \(\to\)  Relu
-  \item Dense(10)  \(\to\)  Softmax
-\end{enumerate}
-
+The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.\\
 The data set was trained using the first \num{50000} images from the data set.
@@
 \section{Results}\label{sec:result}
-The host (NumPy based) code benchmarked at \num{60} GFLOPS for simple inference of the first network and about \num{160} GFLOPS for the second network.
+The host (NumPy based) code benchmarked at \num{60} GFLOPS for straight-forward inference of the first network and about \num{160} GFLOPS for the second network.
 A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
@@
 Due to the FPGAs ability to use any numerical format that is required, the current implementation should not show the same performance degradation.
+
+\section{Acknowledgment}\label{sec:acknowledgment}
+%TODO
 

### 2018-07-03 SWoPP2018 Paper/paper.tex

--- 2018-07-03 SWoPP2018 Paper/paper.tex
@@
 \subsection{Network Tested + Data-set}
+
 The used example networks are multi-layer perceptron (MLP).
-So all layers are a simple array neurons and every neuron is connected to every neuron in the next layer.
+So all layers are an array of neurons and every neuron is connected to every neuron in the next layer.
 These layers are often called ``Dense'' layers.

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added second affiliation for sensei
Reordered affliations and changed section title.

@@
 \affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}
+\affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}
 
@@
 \author{Artur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
-\author{Satoshi Matsuoka}{TiTech}[matsu@is.titech.ac.jp]
+\author{Satoshi Matsuoka}{TiTech,Riken}[matsu@is.titech.ac.jp]
 
@@
 
-\subsection{Network Tested + Data-set}
+\subsection{Test Networks and Inputs}
 
@@
   \caption{FPGA Kernel performance}\label{tab:kernel-performance}
-  \begin{tabular}{llll}
+  \begin{tabular}{lSS}
     \toprule
@@
     \midrule
-    64$\times$64 & \num{17.8} & \num{18.9}  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
-    16$\times$16 & \num{4.3} & \num{4.4} \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    64$\times$64 & 17.8 & 18.9  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    16$\times$16 & 4.3 & 4.4 \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
     \bottomrule

### 2018-07-03 SWoPP2018 Paper/paper.tex
Added a reference

@@
 The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.
+Althought we do have a posit~\cite{podobasposit} generator ready to be used, it has yet to be integrated into our flow.
 
@@
 
-The performance is memory bandwidth limited for these kernels.
+The performance is memory-bound for these kernels.
+However, given our experience with alterantive numerical formats (most noticable posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
 
@@
 
+\bibitem{podobasposit}
+  Podobas, Artur and Matsuoka, Satoshi:  
+  Hardware Implementation of POSITs and their application in FPGAs
+  {\it International Parallel and Distributed Processing Symposium Workshops},
+  to appear, 2018
+
 \end{thebibliography}

### 2018-07-03 SWoPP2018 Paper/paper.tex
Minor changes to abstract.

@@
 Through this work, we seek to accelerate arbitrary precision deep-learning training using Field-Programmable Gate-Arrays by leveraging Intel FPGA SDK for OpenCL.
-Preliminary results show promise for implementations based on precisions or number formats that currently only have low performing implementations on conventional CPU and GPU hardware.
+We present our design decision and the future outlook of our framework, and quantitively describe its resource consumption and inferrence performance on modern FPGAs.
+%Preliminary results show promise for implementations based on precisions or number formats that currently only have low performing implementations on conventional CPU and GPU hardware.
 \end{abstract}

### 2018-07-03 SWoPP2018 Paper/paper.tex
Processed Arthur's feedback.

--- 2018-07-03 SWoPP2018 Paper/paper.tex
@@
 \subsection{Field-Programmable Gate-Arrays}
-
 FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementing a hardware design before taping out full chip.
-They are devices that can represent reconfigurable hardware.
-A normal FPGA work-flow consists of writing in a hardware description language.
-Then synthesizing the design and finally placing and routing the design.
-This is a lengthy process and complex designs in hardware description languages are hard to maintain.
-In this work we will focus on using the OpenCL interface to the FPGA.
-OpenCL is a framework specified by the Khronos Group\footnote{Specification available at: \url{https://www.khronos.org/opencl/}} in 2009, to work with all kinds of processors, accelerators and other heterogenous compute devices, in recent years the FPGA vendors have made efforts to make it easier to leverage FPGA resources by computer scientists and not only hardware designers.
-So OpenCL is one of the ways to leverage high level synthesis.
-High level synthesis take a design specification in a high level language like C or in this case the modified version of C99 that is used for OpenCL kernels.
-And the synthesizer makes an RTL design description from this design automatically after which the normal work-flow is resumed.
-
+They are devices that can belong to the class of fine-grained reconfigurable devices.\\
 FPGAs are made up of a reconfigurable fabric.
@@
 It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting without having to resort to software simulations and the performance limitations that follow from that.
+
+The usual FPGA work-flow consists of writing in a hardware description language, synthesizing the design and finally place and routing the desig onto the FGPA resources.
+This is a lengthy process and complex designs in hardware description languages are hard to maintain.
+In this work we will focus on using the OpenCL interface to the FPGA.
+OpenCL is a framework specified by the Khronos Group\footnote{Specification available at: \url{https://www.khronos.org/opencl/}} in 2009, to work with all kinds of processors, accelerators and other heterogenous compute devices, in recent years the FPGA vendors have made efforts to make it easier to leverage FPGA resources by computer scientists and not only hardware designers.
+So OpenCL is one of the ways to leverage high level synthesis.
+High-level synthesis takes a design specification in a high level language like C or in this case the modified version of C99 that is used for OpenCL kernels and creates an RTL design description for this design automatically after which the normal work-flow is resumed.
 
@@
 We have chosen to rely on Python as the high-level frontend for our framework.
-It is through python that a user create a networks, selects inputs, and decides what data formats to use.
+It is through Python that a user creates networks, selects inputs, and decides what data formats to use.
 Once a particular configuration is selected, our framework generates data-type oblivious training and inference code that targets Intel's OpenCL SDK for FPGAs.
@@
 \Cref{fig:block-diagram} shows a overview of the system.
-The backwards kernels are a work in progress, so for now we use an external training script.
+The backwards kernels are a work in progress, so for now we leverage external frameworks for training.
 The backwards kernels are the kernels that calculate the error and back propagate the error while updating the weights and biases in the network used during training.
-During inference the host code, written in python, does one forward kernel call for every layer.
-And does a final softmax kernel call to get the final prediction.
+During inference the host code, written in Python, does one forward kernel call for every layer.
+Finally it does a final softmax kernel call to get the final prediction.
 For performance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
-The main goal to make replacing the numerical format easier, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating that without a huge performance impact.
+The main goal is to simplify changing the numerical format, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating that without a huge performance impact.
+% TODO add citation for "HUGE"
 
@@
 All weight matrices are transposed in memory, this to optimized the memory access pattern of the matrix-matrix multiplication.
-The main inference is done using an blocking implementation of the matrix multiplication.
-So a block is fetched from the activations and the weights and placed in the block RAM on the FPGA.
+The main inference is performed using an blocking implementation of the matrix multiplication.
+First a block is fetched from the matrices containing the activations and weights and is placed in the block RAM on the FPGA.
 The computation result is also stored on the block RAM, before a routine writes it back to global memory.
@@
 
-The OpenCL SDK from Intel used for this design, tries to pipeline loops in single work item kernels, as opposed to NDRange kernels. % Reference to Intel OpenCL Manual?
+The OpenCL SDK from Intel used for this design tries to pipeline loops in single work item kernels, as opposed to NDRange kernels (that are more truthful to the SIMT paradigm).
 To get maximum performance the aim is to get an initiation interval of one.
@@
 To get this to work on the inner most loop, one that is essentially a reduction.
-An array is used to store all output in separate locations, this way the loop can be fully unrolled.
-For the containing loops, serial dependencies are to be avoided whenever possible.
-So different loop iterations are fully data-independent.
+An array is used to store all output in separate locations, which enables the loop to be fully unrolled.
+For the loops surrounding the inner most loop, serial dependencies are to be avoided whenever possible, so different loop iterations are fully data-independent.
 For the outermost loop that processes one block this behavior is not possible, since the output block is written to multiple times.
-If there was enough space on the FPGA theoretically multiple blocks would be able to be processed in parallel.
-In the future the training kernel also needs to fit, so it was decided not to try parallelize this further.
+Multiple blocks can theoretically be processed on the FPGA should space allow for it.
+Future revisions of this framework will also include a training phase, and we thus postponed further parallelization efforts until the kernel is complete.
 
 \subsubsection{Design decisions}
-One of the main choices with the largest effect on implementation is whenever to keep all weight matrices in memory transposed.
-During inference this is very beneficial, as this makes most reads sequential.
+One of the main choices with the largest impact on implementation is whenever to keep all weight matrices in memory transposed.
+During inference this is very beneficial, as it makes most reads sequential.
 In early stages of development it sped up the kernel performance by a factor of \num{3}.
-During training, using stochastic gradient descent, this can be a problem though, the weight matrix should now be transposed back for the most efficient memory access patterns.
+During training, using stochastic gradient descent, this can be a problem though, since the weight matrix should now be transposed back for the most efficient memory access patterns.
 But since the arithmetic density of the training process is higher, the effect might be slightly less pronounced.
-An other decision was to take the most outer loop, the loop over all the layers, to the host.
-This loop can not be pipelined since there is serial dependency, so it makes more sense execute this loop on the host CPU.
-This both saves space on the FPGA and it simplifies the generated hardware.
+Another decision was to execute the outermost loop, the one that loops through all the layers, to the host.
+This loop cannot be pipelined due to a serial data-dependency, so it makes more sense execute this loop on the host CPU.
+This saves space on the FPGA and simplifies the hardware design.
 
@@
 The software versions and hardware configuration are shown in respectively \cref{tab:software-versions} and \cref{tab:test-hardware}.
-All kernels were compiled with \texttt{-O3 -fp-relaxed}.
-\texttt{-fp-relaxed} gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
+All kernels were compiled with ``\texttt{-O3 -fp-relaxed}''.
+``\texttt{-fp-relaxed}'' gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
 \begin{table}[h]
@@
 The used example networks are multi-layer perceptron (MLP).
-So all layers are an array of neurons and every neuron is connected to every neuron in the next layer.
+This means that all layers are an array of neurons and every neuron is connected to every neuron in the next layer.
 These layers are often called ``Dense'' layers.
 The first data set used was MNIST~\cite{lecun2010mnist}, MNIST is a collection of 28\(\times\)28 gray scale images of hand written arabic numerals.
-So the data set provides \num{784} input features.
+So the data set provides \num{784} inputs.
 The structure of the sample MNIST network is shown in \cref{fig:mnist-network}.
@@
 All training was done using a batch size of \num{128}.
-The CPU code was implemented using the NumPy array.dot function.
+We implemented the CPU code based on NumPy's array.dot function.
 
@@
 
-\subsection{Training Performance}
+\subsection{Inferrence Performance}
 The MNIST network test set accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.

### 2018-07-04 SWoPP2018 Paper/paper.tex
First round of feedback.

@@
 
-\title{Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision}
-
+\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}}
 \affiliate{TiTech}{Tokyo Institute of Technology, 
@@
 To help investigate what the effects of varying the precision during deep-learning training are, first an architecture using reconfigurable hardware needs to be developed.
-Through this work, we seek to accelerate arbitrary precision deep-learning training using Field-Programmable Gate-Arrays by leveraging Intel FPGA SDK for OpenCL.
+Through this work, we seek to accelerate arbitrary precision deep-learning training using Field-Programmable Gate-Arrays by leveraging the Intel FPGA SDK for OpenCL.
 We present our design decision and the future outlook of our framework, and quantitively describe its resource consumption and inferrence performance on modern FPGAs.
@@
 A better way to explore floating-point representation is to leverage Field-Programmable Gate-Arrays (FPGAs).
-An FPGA is a device consisting of several millions re-programmable look-up tables (LUTs) that together with programmable routers give a very malleable silicon substrate second only in performance to Application-Specific Integrate Circuits (ASICs).
+An FPGA is a device consisting of several millions of re-programmable look-up tables (LUTs) that together with programmable routers give a very malleable silicon substrate second only in performance to Application-Specific Integrate Circuits (ASICs).
 Modern FPGAs can be clocked at several hundreds MHz, and contain enough compute to rival even Graphics-Processing Units (GPUs), making them ideal to study architectural design choices.
@@
 
-The remainder of our paper is structure in the following way: \cref{sec:relwork} positions our work against other, similar efforts.
+The remainder of our paper is structure in the following way: \cref{sec:relwork} positions our work against other work, similar efforts.
 \cref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
@@
 \section{Related Work}\label{sec:relwork}
-Field-Programmable Gate-Arrays (FPGAs) have extensively been used to probe and explore various architectural design decision, including those of deep-learning.
-The large majority of existing work limit themselves to inference, primarily due to the simpler design layout (little intermediate data needs storing).
-Levering FPGAs have allowed researchers to decrease the number of bits allocate to the numerical representation, going as far as inferring popular networks such as  AlexNET~\cite{krizhevsky2012imagenet} using as few as binary~\cite{shimoda2017all,umuroglu2017finn} (1-bit) weights.
-Inferring networks that uses few bits to represents weights (called Quantized Neural Networks~\cite{courbariaux2016binarized}) requires subtle yet necessary changes to the training phase~\cite{binaryconnect,courbariaux2016binarized,zhou2016dorefa}.
-Lately, modern deep-learning framework are having support for reduced precision training, some driven by leading FPGA vendors such as Xilinx~\cite{xilinxml}.
+Field-Programmable Gate-Arrays (FPGAs) have extensively been used to probe and explore various architectural design decisions, including those of deep-learning.
+The large majority of existing work limits themselves to inference, primarily due to the simpler design layout (little intermediate data needs storing).
+Levering FPGAs has allowed researchers to decrease the number of bits allocated to the numerical representation, going as far as inferring popular networks such as  AlexNET~\cite{krizhevsky2012imagenet} using as few as single bit~\cite{shimoda2017all,umuroglu2017finn} (binary) weights.
+Inferring networks that use few bits to represents weights (called Quantized Neural Networks~\cite{courbariaux2016binarized}) requires subtle yet necessary changes to the training phase~\cite{binaryconnect,courbariaux2016binarized,zhou2016dorefa}.
+Lately, modern deep-learning frameworks are having support for reduced precision training, some driven by leading FPGA vendors such as Xilinx~\cite{xilinxml}.
 Dicecco et al.~\cite{dicecco2017fpga} are working on a framework similar to ours that trains neural networks using FPGAs while modifying the numerical format.
@@
 FPGAs are not unique to vary the numerical precision of deep neural networks, and several ASICs have been produced for quantized neural networks.
-Most of these focus only on inference (for embedded deployment)  for low-power embedded domains; these include YodaNN~\cite{yodann}, BinaryEYE~\cite{binaryeye} and ChipMunk~\cite{chipmunk}; these ASICs were shown to consume up-to two magnitudes low power compared to similar FPGA solutions.
+Most of these focus only on inference (for embedded deployment)  for low-power embedded domains; these include YodaNN~\cite{yodann}, BinaryEYE~\cite{binaryeye} and ChipMunk~\cite{chipmunk}; these ASICs were shown to consume up to two magnitudes lower power compared to similar FPGA solutions.
 
@@
 A similar process (reduced precision multiplication, full precision accumulation) is also applied in NVIDIA’s Volta-100 line GPUs.
-These mixed-precision units drastically improve the Artificial-Intelligence compute capabilities (AI-FLOPs) of modern systems, trading silicon resource for increased compute with arguable small impact on training performance.
+These mixed-precision units drastically improve the Artificial-Intelligence compute capabilities (AI-FLOPs) of modern systems, trading silicon resources for increased compute with arguably small impact on training performance.
 Vendors also embrace drastically different formats, notably in Intel’s NERVANA~\cite{nervana} (likely where FlexPoint~\cite{intelflexpoint} is used) and Google’s TPU~\cite{tpuformat} (which have more bits in the exponent compared to the mantissa).
@@
 This makes them very suitable for the research described in this paper.
-It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting without having to resort to software simulations and the performance limitations that follow from that.
+It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting without having to resort to software simulations and the performance limitations that follow from those.
 
-The usual FPGA work-flow consists of writing in a hardware description language, synthesizing the design and finally place and routing the desig onto the FGPA resources.
-This is a lengthy process and complex designs in hardware description languages are hard to maintain.
+The usual FPGA work-flow consists of writing in a hardware description language, synthesizing the design and finally place and routing the design onto the FGPA resources.
+This is a lengthy process and complex designs written in hardware description languages are hard to maintain.
 In this work we will focus on using the OpenCL interface to the FPGA.
 OpenCL is a framework specified by the Khronos Group\footnote{Specification available at: \url{https://www.khronos.org/opencl/}} in 2009, to work with all kinds of processors, accelerators and other heterogenous compute devices, in recent years the FPGA vendors have made efforts to make it easier to leverage FPGA resources by computer scientists and not only hardware designers.
-So OpenCL is one of the ways to leverage high level synthesis.
-High-level synthesis takes a design specification in a high level language like C or in this case the modified version of C99 that is used for OpenCL kernels and creates an RTL design description for this design automatically after which the normal work-flow is resumed.
+Now OpenCL is one of the ways to leverage high level synthesis.
+High-level synthesis takes a design specification in a high level language like C or in this case the modified version of C99 that is used for OpenCL kernels and creates an RTL design description for this design automatically after which the normal work-flow for synthesis, and place and route is resumed.
 
@@
 \subsection{Neural Networks}
-An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system-- a system built around the concepts of \textit{neuron}s as the main computational agents.
+An Artificial Neural Network (ANNs) is a system inspired by the biological nervous system -- a system built around the concepts of \textit{neuron}s as the main computational agents.
 \Cref{fig:ann-example} illustrates an example of a typical “deep” neural network: a network that consists of a input layer, and output layer, and a number of \textit{hidden} layers in-between.
 The number of hidden layers in modern neural networks can be very large: AlexNet (2012)~\cite{krizhevsky2012imagenet} has eight, VGG16 (2014)~\cite{simonyan2014very} has 16 layers, GoogleNet (2014)~\cite{szegedy2015going} has 22 layers, and ResNet (2016)~\cite{he2016deep} has 152 layers.
-The trend seem to favor larger and deeper neural networks.
+The trend seems to favor larger and deeper neural networks.
 The input layer of a neural network (in our example, a classifier) contains the (possibly pre-processed) inputs, such as images (for image recognition), words (in natural language processing), or motifs (in graph processing).

### 2018-07-04 SWoPP2018 Paper/paper.tex
Added AIST affiliation.

@@
 \affiliate{TiTech}{Tokyo Institute of Technology, 
-Meguro, Tokyo 152--8550, Japan}
+Meguro-ku, Tokyo 152--8550, Japan}
 \affiliate{TUDelft}{Delft University of Technology, Mekelweg 2, 2628 CD Delft, Netherlands}
 \affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}
+\affiliate{AIST}{National Institute of Advanced Industrial Science and Technology, Chiyoda-ku, Tokyo 100-8921 Japan}
 
@@
 \author{Artur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
-\author{Satoshi Matsuoka}{TiTech,Riken}[matsu@is.titech.ac.jp]
+\author{Satoshi Matsuoka}{TiTech,Riken,AIST}[matsu@is.titech.ac.jp]
 

### 2018-07-04 SWoPP2018 Paper/paper.tex
Final part of own feedback.

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage[nameinlink,noabbrev,capitalise]{cleveref}
+\usepackage[nameinlink,capitalise]{cleveref}
 
@@
 The recent explosion in artificial intelligence – in particular that of deep neural networks based on back-propagation – has triggered a storm in the introduction and creation of specialized compute devices.
-Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high-performance Deep-Learning (DL) training and/or inference.
-Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating-point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
-It is clear that Artificial Intelligence and Deep-Learning will have a prioritized presence in modern architecture -- today and in the near future.
+Commercial platforms such as Microsoft’s BrainWave~\cite{msbrainwave}, Google’s TPUs~\cite{googletpu}, and Fujitsu’s DLU~\cite{fujitsudlu} are all examples of specialized circuitry dedicated to low-power, high performance deep-learning (DL) training and/or inference.
+Meanwhile, existing general-purpose manufacturers are empowering their architecture with custom floating point units that trade precision for performance, such as Intel’s Knights-Mill~\cite{knm} and NVIDIA’s Volta-100~\cite{volta100}.
+It is clear that artificial intelligence and deep-learning will have a prioritized presence in modern architecture -- today and in the near future.
 
@@
 Reducing the size of the floating-point representation can have dramatic (and positive) impacts on the performance: more compute per unit silicon, more compute per unit bandwidth, and lower power consumption.
-Several alternatives to the IEEE-754 format are indeed emerging, such as Microsoft’s Deep-Learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
+Several alternatives to the IEEE-754 format are indeed emerging, such as Microsoft’s deep-learning format~\cite{msbrainwave}, Intel’s FlexPoint~\cite{intelflexpoint}, Google’s custom TPU format~\cite{tpuformat}, and Posits~\cite{posits}.
 
@@
 Modern FPGAs can be clocked at several hundreds MHz, and contain enough compute to rival even Graphics-Processing Units (GPUs), making them ideal to study architectural design choices.
-Furthermore, with the recent growth in popularity of High-Level Synthesis (HLS) tools, programming these devices can be as simple as writing C/C++ code, and delegate the software-to-hardware transformation effort to the compiler.
+Furthermore, with the recent growth in popularity of High-Level Synthesis (HLS) tools, programming these devices can be as simple as writing C/C++ code, and delegate the software to hardware transformation effort to the compiler.
 
@@
 Each layers consists of a number of \textit{neurons} – the main compute agent of the network.
-Each edge that connect to a particular neuron is called a \textit{synapse}, and comes with a \textit{weight} (\(w_{i,j}\)) in the figure, where \(i\) is the index of the neuron).
-The neuron integrates the weights (\cref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies a activation function to compute the output of the neuron.
+Each edge that connects to a particular neuron is called a \textit{synapse}, and comes with a \textit{weight} (\(w_{i,j}\)) in the figure, where \(i\) is the index of the neuron.
+The neuron integrates the weights (\cref{fig:ann-example}:b) of all input synapses, adds a local bias, and applies an activation function to compute the output of the neuron.
 The activation function varies between networks, but commonly used activation functions include: the sigmoid (\(f(x) = \frac{1}{1+e^{-x}}\)), the rectifier (ReLu, \(f(x) = max(0,x)\)), or hyperbolic tangent (\(f(x) = tanh(x)\)).
@@
 
-Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer --from the front to the back of the network-- and propagating the output of each layer into the next.
+Inferring (predicting) using a deep neural network is done by connecting the input to what is to be predicted, and sequentially activating each layer -- from the front to the back of the network -- and propagating the output of each layer into the next.
 This effort is called \textit{forward propagation}. Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
@@
 By data-type oblivious we mean that all operations associated with any particular data-type representation remain unresolved at the point of creation, as they will not depend on any of the native data-types or functionality of the OpenCL language.
-Instead, our Python framework invokes a Data-type selector, which automatically generates a low-level hardware description language (HDL) library that contain commonly used operators for the selected data-type.
+Instead, our Python framework invokes a data-type selector, which automatically generates a low-level hardware description language (HDL) library that contains commonly used operators for the selected data-type.
 Once the Register-Transfer Level (RTL) library has been generated, it is merged with the data-type oblivious OpenCL template to yield the final description, which now can be synthesized using EDA tools and used.
@@
 The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.
-Althought we do have a posit~\cite{podobasposit} generator ready to be used, it has yet to be integrated into our flow.
+Although we do have a posit~\cite{podobasposit} generator ready to be used, it has yet to be integrated into our flow.
 
 \subsubsection{Design overview}
-\Cref{fig:block-diagram} shows a overview of the system.
+\Cref{fig:block-diagram} shows an overview of the system.
 The backwards kernels are a work in progress, so for now we leverage external frameworks for training.
 The backwards kernels are the kernels that calculate the error and back propagate the error while updating the weights and biases in the network used during training.
-During inference the host code, written in Python, does one forward kernel call for every layer.
+The host code -- written in Python -- does one forward kernel call for every layer during inference.
 Finally it does a final softmax kernel call to get the final prediction.
 For performance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
-The main goal is to simplify changing the numerical format, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating that without a huge performance impact.
+The main goal is to simplify changing the numerical format, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating this without a huge performance impact.
 % TODO add citation for "HUGE"
@@
 \subsubsection{Design details}
-All weight matrices are transposed in memory, this to optimized the memory access pattern of the matrix-matrix multiplication.
+All weight matrices are transposed in memory, this to optimize the memory access pattern of the matrix-matrix multiplication.
 The main inference is performed using an blocking implementation of the matrix multiplication.
@@
 The block RAM has a much lower latency than the global memory.
-This speeds up throughput by a large margin.
+This increases the throughput by a significant margin, almost 3\(\times\) in a naive implementation.
 Block RAM is equivalent to the shared or local memory of contemporary GPUs.
@@
 That is to say that a new loop iteration is scheduled every clock cycle.
-To get this to work on the inner most loop, one that is essentially a reduction.
-An array is used to store all output in separate locations, which enables the loop to be fully unrolled.
-For the loops surrounding the inner most loop, serial dependencies are to be avoided whenever possible, so different loop iterations are fully data-independent.
+To get this to work on the inner most loop -- one that is essentially a reduction -- an array is used to store the output of every iteration in separate locations, which enables the loop to be fully unrolled.
+For the loops surrounding the inner most loop, serial data-dependencies are to be avoided whenever possible, so different loop iterations are fully data-independent.
 For the outermost loop that processes one block this behavior is not possible, since the output block is written to multiple times.
-Multiple blocks can theoretically be processed on the FPGA should space allow for it.
+Multiple different blocks can theoretically be processed on the FPGA should space allow for it.
 Future revisions of this framework will also include a training phase, and we thus postponed further parallelization efforts until the kernel is complete.
@@
 Another decision was to execute the outermost loop, the one that loops through all the layers, to the host.
-This loop cannot be pipelined due to a serial data-dependency, so it makes more sense execute this loop on the host CPU.
+This loop cannot be pipelined due to a serial data-dependency, so it makes more sense to execute this loop on the host CPU.
 This saves space on the FPGA and simplifies the hardware design.
@@
 The software versions and hardware configuration are shown in respectively \cref{tab:software-versions} and \cref{tab:test-hardware}.
-All kernels were compiled with ``\texttt{-O3 -fp-relaxed}''.
-``\texttt{-fp-relaxed}'' gives the compiler some more freedom with the order of operations, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
+All kernels were compiled with the flags ``\texttt{-O3 -fp-relaxed}''.
+``-O3'' is an optimization flag, configuring the compiler to enable resource-driven optimizations. % TODO verify
+The ``\texttt{-fp-relaxed}'' flag gives the compiler some more freedom with the order of operations using a balanced tree hardware implementation, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
 \begin{table}[h]
@@
 
-The used example networks are multi-layer perceptron (MLP).
-This means that all layers are an array of neurons and every neuron is connected to every neuron in the next layer.
+The used example networks are multi-layer perceptrons (MLPs).
+This means that all layers are arrays of neurons and every neuron is connected to every neuron in the next layer.
 These layers are often called ``Dense'' layers.
@@
 The last \num{10000} images are used as the test data set.\\
-The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, so \num{3072} input features.
+The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, CIFAR-10 is a collection of 32\(\times\)32 color images divided into 10 classes, providing \num{3072} inputs.
 The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.\\
@@
 The host (NumPy based) code benchmarked at \num{60} GFLOPS for straight-forward inference of the first network and about \num{160} GFLOPS for the second network.
-A first naive implementation on the FPGA clocked about \num{2.5} GFLOPS for this problem size.
+A first naive implementation on the FPGA clocked in at about \num{2.5} GFLOPS for this problem size.
 Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
@@
 The performance is memory-bound for these kernels.
-However, given our experience with alterantive numerical formats (most noticable posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
+However, given our experience with alternative numerical formats (most notably posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
 
@@
 Larger block sizes would exhaust the block RAM on the used FPGA device.
-The next logical size up from \num{64} would be \num{84} (\num{3}\(\times\)\num{28}), this would use to much of the block RAM already.
+The next logical size up from \num{64} would be \num{84} (\num{3}\(\times\)\num{28}) would use to much of the block RAM already.
 This is because there are three block buffers and the relationship between block size and used block RAM is square.
@@
 The MNIST network test set accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
-And the CIFAR-10 accuracy after training is \SI{47.9}{\percent}
+And the CIFAR-10 accuracy after training is \SI{47.9}{\percent}.
 The FPGA gets slightly different floating point results due to rounding differences but is matches the accuracy.
@@
 \section{Conclusion}\label{sec:conclusion}
-We have introduced and described our efforts to create a general-purpose Deep-Learning framework for design-space exploration of numerical formats.
+We have introduced and described our efforts to create a general-purpose deep-learning framework for design space exploration of numerical formats.
 While still in the early stages, we have focused on generality.

### 2018-07-04 SWoPP2018 Paper/paper.tex
Fixed paragraphing issue.

@@
 The data set was trained using the first \num{60000} images from the MNIST data set.
-The last \num{10000} images are used as the test data set.\\
+The last \num{10000} images are used as the test data set.
+
 The second data set used was CIFAR-10~\cite{krizhevsky2014cifar}, CIFAR-10 is a collection of 32\(\times\)32 color images divided into 10 classes, providing \num{3072} inputs.
-The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.\\
+The structure of the sample CIFAR-10 network is shown in \cref{fig:cifar10-network}.
 The data set was trained using the first \num{50000} images from the data set.

### 2018-07-04 SWoPP2018 Paper/paper.tex
Removed comment.
Minor change to contribution list.
Final affiliation changes.

@@
 \affiliate{Riken}{RIKEN Center for Computational Science, Chuo-ku, Kobe, Hyogo 650-0047 Japan}
-\affiliate{AIST}{National Institute of Advanced Industrial Science and Technology, Chiyoda-ku, Tokyo 100-8921 Japan}
+\affiliate{AIST}{AIST - Tokyo Tech Real World Big-Data Computation Open Innovation Laboratory, Meguro-ku, Tokyo 152-8550, Japan}{%National Institute of Advanced Industrial Science and Technology, Chiyoda-ku, Tokyo 100-8921 Japan}
 
@@
 \end{abstract}
-
-%\begin{keyword}
-%Journal of Information Processing, \LaTeX, style files, ``Dos and
-% Don'ts'' list
-%\end{keyword}
 
@@
 
-We contribute with the following:
+In this paper, we contribute with:
+%We contribute with the following:
 \begin{itemize}
 \item Proposed design for a generalized FPGA training architecture targeting variable numerical formats, and
-\item Evaluation and analysis of core computation patterns, including FPGA resource utilization
+\item Preliminary evaluation and analysis of core computation patterns for inference with respect to performance and resource utilization
 \end{itemize}

### 2018-11-27 Final Extra Project Paper/.library/preamble.tex
Added modified paper and final code for framework.

% Include all project wide packages here.
%\usepackage{fullpage}
\usepackage[a4paper]{geometry}
\usepackage{polyglossia}
\setmainlanguage{english}
\usepackage{csquotes}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[list=true]{subcaption}
\usepackage{float}
\usepackage{import}
\usepackage{wrapfig}
\usepackage{authblk}
\usepackage{array}
\usepackage{booktabs}
\usepackage{fontspec}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage[binary-units=true,quotient-mode=fraction,table-auto-round]{siunitx}
\usepackage{units}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{unicode-math}
\usepackage{rotating}
\usepackage{blindtext}
\usepackage{color}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage[final]{microtype}

\usetikzlibrary{matrix}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{automata}
\usetikzlibrary{arrows.meta}

\pgfplotsset{compat=newest}
\pgfplotsset{plot coordinates/math parser=false}
\usetikzlibrary{plotmarks}
\usepgfplotslibrary{patchplots}
\newlength\figureheight
\newlength\figurewidth
\newlength\bytewidth
\newlength\byteheight
\setlength\bytewidth{1cm}
\setlength\byteheight{6ex}

\tikzset{every axis/.style={xticklabel style={align=right}}}

\tikzstyle{every state}=[fill=tu-cyan,align=center,draw=black,line width=1pt,node distance=3cm,minimum width = 1.8cm]%for FSMs casper
\tikzstyle{every initial by arrow}=[initial text={Reset}]
\newcommand{\setpathasarrows}{\tikzstyle{every path}=[auto,line width=1.5pt,line cap=round,line join=round]}
\tikzstyle{pijl}=[->,line width=1.5pt,line cap=round,line join=round]

%TODO fix black diamond in decision center
\tikzset{%for flow charts casper
    treenode/.style = {shape=rectangle,
                        draw=black,anchor=center,
                        fill=blue!20,align=center,
                        line width=1pt,
                        text centered
                        %inner sep=1ex},
                        },
    start/.style = {treenode, circle, inner sep=0pt,minimum width=1.5cm},
    decision/.style = {treenode, diamond,text badly centered,inner sep=0pt,minimum width = 1.8cm,text width=4cm,aspect=4},
    action/.style   = {treenode,        align=center,minimum width = 3.75cm,text width=3cm},
    action_wide/.style   = {treenode,        align=center,minimum width = 1.8cm,text width=4cm},
    statedashed/.style={state,circle,dashed,draw=black,fill=none},
    goto/.style = {treenode,isosceles triangle,align=center,text width=3cm},
    hidden/.style = {treenode,coordinate,fill=none,anchor=center,minimum width = 0.5cm},
    line_custom/.style = {-,thick,auto,draw=black,line width=1.5pt},
    >={Latex[width=3mm,length=3mm]}
}

\tikzstyle{byte}=[draw, fill=blue!20, minimum width=6cm,line width=0.4pt,node distance=-0.4pt, minimum height=\byteheight,text width=6cm,font={\fontsize{9pt}{0}\selectfont}]
\tikzstyle{data}=[byte, fill=red!20]
\tikzstyle{padding}=[byte, fill=green!20]
\tikzstyle{byte_small}=[draw, fill=blue!20, minimum width=1.5cm,line width=0.4pt,node distance=-0.4pt, minimum height=\byteheight,text width=1.5cm]
\tikzstyle{data_small}=[byte_small, fill=red!20]

\usepackage[
%backend=bibtex,
backend=biber,
	texencoding=utf8,
bibencoding=utf8,
style=numeric,
citestyle=numeric,
    sortlocale=en_US,
    language=auto,
    backref=true,
    abbreviate=false,
    seconds=true,
    date=iso,
    urldate=iso
]{biblatex}

\usepackage{listings}
\newcommand{\includecode}[4][c]{\lstinputlisting[caption=#2, escapechar=, style=#1,label=#4]{#3}}
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}

\setlist[enumerate]{labelsep=*, leftmargin=1.5pc}
\setlist[enumerate,1]{label=\arabic*., ref=\arabic*}
\setlist[enumerate,2]{label=\arabic*.,ref=\theenumi.\arabic*}
\setlist[enumerate,3]{label=\arabic*., ref=\theenumii.\arabic*}

%\setcounter{chapter}{-1} %start chapter numbers with 0

\usepackage[hidelinks]{hyperref} %<--------ALTIJD ALS LAATSTE
\usepackage[nameinlink,noabbrev,capitalise]{cleveref} %<------- Clever Ref moet na hyperref

### 2018-11-27 Final Extra Project Paper/paper.tex
Added modified paper and final code for framework.

--- 2018-07-04 SWoPP2018 Paper/paper.tex
@@
 
-\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)}}
+\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)} \\ \large{This version is amended from it's original version submitted to SWoPP 2018}}
 \affiliate{TiTech}{Tokyo Institute of Technology, 
@@
 \cref{sec:framework} gives a background to machine learning and FPGAs, and describes our proposed architecture.
-\cref{sec:method} overviews our experimental methodology, and is followed by our preliminary results in \cref{sec:result}.
+\cref{sec:method} overviews our experimental methodology, and is followed by our results in \cref{sec:result}.
 We conclude in \cref{sec:conclusion}.
@@
 
-The present paper focuses on the IEEE-754 part of inference, where training and alternative data-types are on-going and future work.
+The present paper focuses on the IEEE-754 part of inference and training, where alternative data-types are on-going and future work.
 Although we do have a posit~\cite{podobasposit} generator ready to be used, it has yet to be integrated into our flow.
@@
 \Cref{fig:block-diagram} shows an overview of the system.
-The backwards kernels are a work in progress, so for now we leverage external frameworks for training.
+The forward kernels are the kernels the run to calculate the current activation and prediction values.
 The backwards kernels are the kernels that calculate the error and back propagate the error while updating the weights and biases in the network used during training.
@@
 Finally it does a final softmax kernel call to get the final prediction.
+After which it runs the first delta kernel and continues on to run the backward kernel for all layers.
 For performance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
@@
 Multiple different blocks can theoretically be processed on the FPGA should space allow for it.
-Future revisions of this framework will also include a training phase, and we thus postponed further parallelization efforts until the kernel is complete.
+But due to the space required for the training logic, on our current hardware (\cref{tab:test-hardware}) this does not fit or at least it will not pass the optimization stage on the OpenCl SDK compiler.
+
+The training logic itself, requires two matrix-matrix multiplications and three more simple multiply substract block.
+Due to the size requirements and the fact that the compiler will not successfully optimize the larger designs, the blocksize of the whole design is now limited to 24 and implementing a similar acceleration as above is impossible without using vendor IP.
 
@@
 But since the arithmetic density of the training process is higher, the effect might be slightly less pronounced.
-Another decision was to execute the outermost loop, the one that loops through all the layers, to the host.
+Although it also increases the used area slightly because now the matrix multiplication block is distinct from the other ones.
+The transposing or indexing logic is different for each.
+Another decision was move the execution of the outermost loop, the one that loops through all the layers, to the host.
 This loop cannot be pipelined due to a serial data-dependency, so it makes more sense to execute this loop on the host CPU.
@@
 The host (NumPy based) code benchmarked at \num{60} GFLOPS for straight-forward inference of the first network and about \num{160} GFLOPS for the second network.
+For the backward implementation the host code runs at \numrange{500}{800} GFLOPS, due to the higher arithmetic density.
 A first naive implementation on the FPGA clocked in at about \num{2.5} GFLOPS for this problem size.
 Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
-The results for the different final FPGA kernels are shown in \cref{tab:kernel-performance}.
+The results for the different final FPGA block sizes are shown in \cref{tab:inference-kernel-performance} for the inference kernels.
+\Cref{tab:kernel-performance} shows the performance of the training kernels (they include an inference kernel), here it is clear that the training kernels are limiting the overall throughput.
+The backwards kernels have a lot of potential to be optimized if required, but much is dependant on the other data types and their implementation (size), so this is better done when actually implementing this flow for that data type.
 
@@
   \centering
-  \caption{FPGA Kernel performance}\label{tab:kernel-performance}
+  \caption{FPGA Inference Kernel performance}\label{tab:inference-kernel-performance}
   \begin{tabular}{lSS}
@@
     64$\times$64 & 17.8 & 18.9  \\ % kernel_nn_blocking_B64inorder_hw_2018-06-28T22.52.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
-    16$\times$16 & 4.3 & 4.4 \\ % kernel_nn_blocking_B16inorder_hw_2018-06-28T22.53.27.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    16$\times$16 & 4.3 & 4.4 \\ % kernel_nn_blocking_fixed2BS16_hw_2018-11-08T05.26.51.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
     \bottomrule
@@
 
-The performance is memory-bound for these kernels.
-However, given our experience with alternative numerical formats (most notably posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
+\begin{table}[h]
+  \centering
+  \caption{FPGA Full Kernel performance}\label{tab:kernel-performance}
+  \begin{tabular}{lSS}
+    \toprule
+    \textbf{Block size} & \textbf{GFLOPS MNIST}  & \textbf{GFLOPS CIFAR-10}  \\
+    \midrule
+    24$\times$24 & 6.6 & 6.8  \\ % kernel_nn_blocking_fixed2BS24_hw_2018-11-08T05.20.20.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    16$\times$16 & 6.3 & 6.4 \\ % kernel_nn_blocking_fixed2BS16_hw_2018-11-08T05.26.51.aocx Network MNIST: [28 * 28, 512, 512, 10] CIFAR: [32 * 32 * 3, 1024, 512, 512, 10]
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The performance is mostly memory-bound for these kernels. 
+Especially the backwards kernels seem to have a hard limit at around \numrange{6}{7} GFLOPS in their current form.
+Furthermore, given our experience with alternative numerical formats (most notably posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
 
 \subsection{FPGA Resource Utilization}
-The kernel resource utilization is shown in \cref{tab:fpga-util}.
-The main limiting factor is the available block RAM.
+The kernel resource utilization is shown in \cref{tab:fpga-inference-util} for the inference kernels only and \cref{tab:fpga-util} shows the utilization for the full implementation.
+The main limiting factor is the available block RAM and the ability for the compiler to runs its optimization phase without crashing.
 To stop the calculation of extra padding lines in the matrices, the block size should be a multiple of most of the layer sizes.
 Larger block sizes would exhaust the block RAM on the used FPGA device.
-The next logical size up from \num{64} would be \num{84} (\num{3}\(\times\)\num{28}) would use to much of the block RAM already.
+The next logical size up from \num{64} would be \num{84} (\num{3}\(\times\)\num{28}) would use to much of the block RAM already for the inference alone.
 This is because there are three block buffers and the relationship between block size and used block RAM is square.
+With the training kernels the theoretical need for block RAMs would triple if all matrix operations were implemented in the same way.
+Right now on a single device, make the limit to the block size rather small, in light of that, it was decided to postpone the further optimizations after different formats were added.
+Those will also take a much larger area themselves, making the problem worse.
 
@@
   \centering
-  \caption{FPGA Hardware utilization for different block sizes}\label{tab:fpga-util}
+  \caption{FPGA Inference Hardware utilization for different block sizes}\label{tab:fpga-inference-util}
   \begin{tabular}{lllll}
@@
 
-\subsection{Inferrence Performance}
-The MNIST network test set accuracy after training on the CPU using Keras is \SI{97.9}{\percent}.
+\begin{table}[h]
+  \centering
+  \caption{FPGA Full Hardware utilization for different block sizes}\label{tab:fpga-util}
+  \begin{tabular}{lllll}
+    \toprule
+    \textbf{Block size} & \textbf{Logic} & \textbf{DSPs} & \textbf{RAMs} & \textbf{Fmax} \\
+    \midrule    
+    24$\times$24 & \SI{30}{\percent} & \SI{7}{\percent} & \SI{50}{\percent} & \SI{223.51}{\mega\hertz}  \\ % kernel_nn_blocking_fixed2BS24_hw_2018-11-08T05.20.20.aocx
+    16$\times$16 & \SI{23}{\percent} & \SI{6}{\percent} & \SI{39}{\percent} & \SI{218.24}{\mega\hertz}  \\ % kernel_nn_blocking_fixed2BS16_hw_2018-11-08T05.26.51.aocx
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsection{Inference Performance}
+The MNIST network test set accuracy after training on the CPU is \SI{97.9}{\percent}.
 And the CIFAR-10 accuracy after training is \SI{47.9}{\percent}.
-The FPGA gets slightly different floating point results due to rounding differences but is matches the accuracy.
+The FPGA gets slightly different floating point results due to rounding differences and reaches \SI{95.4}{\percent} and \SI{45.2}{\percent} respectively after the same number of epochs.
 
@@
 We have shown interoperability with Keras, where we can train weights offline and import them into our framework with little effort.
+Also that we can correctly train on the CPU and FPGA with custom implementations of stochastic gradient descent.
 We evaluated the performance and resource consumption of our design on the FPGAs, and made sure that the inferred accuracy is correct.
-We are currently working on implementing the training phase, as well as the choice of numerical format to be used in both the inference and training part of our framework.
+And that the training performance sufficient for further testing.
+We are currently working on the choice of numerical format to be used in both the inference and training part of our framework.
 
@@
 This work was partially supported by JSPS KAKENHI Grant Number JP16F16764, the JSPS Postdoctoral fellowship under grant P16764.
+This work was also supported by JST CREST Grant Number(s) JPMJCR1303 and JPMJCR1687.
 

### 2018-11-27 SimpleNN/kernel_test_training.py

@@ -6,7 +6,7 @@ import keras
 
 
 RUN_ON_DEVICE = True
-VERIFY = True
+VERIFY = False
 
 def display_verify_result(res, name="Data"):
     total = len(res)
@@ -30,34 +30,16 @@ if __name__ == "__main__":
         fpga_engine = tnnf.FPGAEngine(args.kernel_file, set_verify_config=VERIFY)
         fpga_engine.create_buffers(pretrained=True)
 
-        # np.random.seed(0)
-        # input_cpu = np.random.randint(1, 4, size=(cpu_engine.minibatch_size, cpu_engine.layer_height[0])).astype(
-        #     dtype=np.float32)
-        # ground_truth_cpu = np.random.randint(0, cpu_engine.layer_height[cpu_engine.layers], size=cpu_engine.minibatch_size)
-        # ground_truth_cpu = keras.utils.to_categorical(ground_truth_cpu, cpu_engine.layer_height[cpu_engine.layers]).astype(
-        #     dtype=np.float32)
-        #
-        # cpu_engine.set_input(input_cpu, ground_truth_cpu)
-        #
-        # fpga_engine.set_input(np.copy(input_cpu), np.copy(ground_truth_cpu))
-
     print("Running CPU code...")
-    cpu_engine.train()
+    cpu_time = cpu_engine.train()
     cpu_engine.set_train_input(0)
-    #print(cpu_engine.act[0][0])
     cpu_engine.fw_function()
     
 
     if RUN_ON_DEVICE:
         print("Running FPGA code...")
-        
-        # fpga_engine.bw_function()
-        # fpga_engine.fw_function()
-        # fpga_engine.bw_function()
-        #fpga_engine.test()
-        fpga_engine.train()
+        fpga_time = fpga_engine.train()
         fpga_engine.set_train_input(0)
-        #print(fpga_engine.act[0][0])
         fpga_engine.fw_function()
         print("Getting all device buffers...")
 
@@ -65,34 +47,38 @@ if __name__ == "__main__":
 
         fpga_engine.finish_device_queue()
 
-        print("Verifying...")
+        ops = fpga_engine.get_trainops()
+        print("FPGA Time: {0} usec. {1:.3f} GFLOPS".format(fpga_time / fpga_engine.epochs / fpga_engine.minibatch_size * 1e6, ops / 1e9 / (fpga_time / fpga_engine.epochs / fpga_engine.minibatch_size)))
[…]

### 2018-11-27 SimpleNN/test_nn_framework/base_engine.py

@@ -1,7 +1,8 @@
 import numpy as np
 import tensorflow as tf
 import keras
-from keras.datasets import mnist as input_data
+#from keras.datasets import mnist as input_data
+from keras.datasets import cifar10 as input_data
 import pickle
 import sys
 
@@ -12,14 +13,14 @@ class BaseEngine:
 
     def __init__(self, set_verify_config=False):
 
-        self.LAYER_FILENAME = "layer_mnist_{0}.p"
+        self.LAYER_FILENAME = "layer_cifar_{0}.p"
         self.testbatch_size = 128
         self.minibatch_size = 128
         self.epochs = 10
-        self.batch_limit = 100
+        self.batch_limit = 10
 
-        self.layer_height = [28 * 28, 512, 256, 10] # MNIST
-        # self.layer_height = [32 * 32 * 3, 1024, 512, 512, 10]  # CIFAR-10
+        #self.layer_height = [28 * 28, 512, 512, 10] # MNIST
+        self.layer_height = [32 * 32 * 3, 1024, 512, 512, 10]  # CIFAR-10
 
         self.layers = len(self.layer_height) - 1
         self.hidden_layers = len(self.layer_height) - 2
@@ -35,11 +36,11 @@ class BaseEngine:
 
         self.ground_truth = None
 
+        section_size = 3
+        num_classes = 2
+
         if set_verify_config:
             print("Running with verification data set.")
-
-            section_size = 3
-            num_classes = 2
 
             self.LAYER_FILENAME = "verify_{0}x{0}_{{0}}.p".format(section_size)
             self.testbatch_size = 16
@@ -138,6 +139,7 @@ class BaseEngine:
     def get_trainops(self):
         # Bias additions and broadcast plus matrix mult.
         ops = 0
+        # Forward
         for layer in range(0, self.layers):
             rows_in = self.layer_height[layer]
             rows_out = self.layer_height[layer + 1]
@@ -145,6 +147,30 @@ class BaseEngine:
 
         # Final softmax
         ops += self.layer_height[self.layers] * (4 + 100) + 1
+
+        # First delta
+        ops += self.layer_height[self.layers] * self.minibatch_size * 2 + 1
+
+        # Backward
+        for layer in range(0, self.layers):
+            rows_in = self.layer_height[layer]
+            rows_out = self.layer_height[layer + 1]
+            # Bias
+            ops += rows_out * self.minibatch_size * 2
+
+            # Delta next
+            if layer > 0:
[…]

### 2018-11-27 SimpleNN/test_nn_framework/cpu_engine.py

@@ -106,19 +106,22 @@ class CPUEngine(BaseEngine):
             batches = self.batch_limit
         #batches = 20
         print("Training with {} batches of size {}".format(batches, self.minibatch_size))
-
+        total_time = 0.0
         for epoch in range(0, self.epochs):
             print("Epoch {} of {}...".format(epoch+1, self.epochs))
             #self.shuffle_train_set()
             for batch in range(0, batches):
                 self.set_train_input(batch)
-
+                start_time = time.time()
                 self.fw_function()
                 #print("after fw act2 nz", np.count_nonzero(self.act[2]))
                 self.bw_function()
+                total_time += time.time() - start_time
                 sys.stdout.write("Batch {} of {} complete.\r".format(batch+1, batches))
             print("Epoch {} of {} is complete.".format(epoch + 1, self.epochs))
             self.test()
+
+        return total_time
 
     def test(self):
         batches = int(self.x_test.shape[0] / self.testbatch_size)

### 2018-11-27 SimpleNN/test_nn_framework/fpga_engine.py

@@ -139,20 +139,25 @@ class FPGAEngine(BaseEngine):
             batches = self.batch_limit
         # batches = 20
         print("Training with {} batches of size {}".format(batches, self.minibatch_size))
+        fpga_time = 0.0
 
         for epoch in range(0, self.epochs):
             print("Epoch {} of {}...".format(epoch + 1, self.epochs))
             #self.shuffle_train_set()
             for batch in range(0, batches):
                 self.set_train_input(batch)
-                
+
+                start_time = time.time()
                 self.fw_function()
 
                 self.bw_function()
+                fpga_time += time.time() - start_time
 
                 sys.stdout.write("Batch {} of {} complete.\r".format(batch + 1, batches))
             print("Epoch {} of {} is complete.".format(epoch + 1, self.epochs))
             self.test()
+
+        return fpga_time
 
     def test(self):
         batches = int(self.x_test.shape[0] / self.testbatch_size)

### 2018-11-27 SimpleNN/trainCIFAR.py

@@ -14,7 +14,8 @@ plaidml.keras.install_backend()
 import keras
 from keras.datasets import cifar10
 from keras.models import Sequential
-from keras.layers import Dense, Activation, Dropout
+from keras.layers import Dense
+from keras.optimizers import SGD
 
 import pickle
 import numpy
@@ -40,29 +41,25 @@ y_train = keras.utils.to_categorical(y_train, num_classes)
 y_test = keras.utils.to_categorical(y_test, num_classes)
 
 model = Sequential()
-model.add(Dense(1024, input_shape=(32 * 32 * 3,)))
-model.add(Activation('relu'))
+model.add(Dense(1024, activation='relu', input_shape=(32 * 32 * 3,)))
 
-model.add(Dense(512))
-model.add(Activation('relu'))
+model.add(Dense(512, activation='relu'))
 
-model.add(Dense(512))
-model.add(Activation('relu'))
+model.add(Dense(512, activation='relu'))
 
-model.add(Dense(num_classes))
-model.add(Activation('softmax'))
+model.add(Dense(num_classes, activation='softmax', input_shape=(32 * 32 * 3,)))
 
 model.compile(loss='categorical_crossentropy',
-              optimizer='adam',
+              optimizer=SGD(lr=0.001),
               metrics=['accuracy'])
 
 model.summary()
 
-history = model.fit(x_train, y_train,
-                    batch_size=batch_size,
-                    epochs=epochs,
-                    verbose=1,
-                    validation_data=(x_test, y_test))
+# history = model.fit(x_train, y_train,
+#                     batch_size=batch_size,
+#                     epochs=epochs,
+#                     verbose=1,
+#                     validation_data=(x_test, y_test))
 score = model.evaluate(x_test, y_test, verbose=0)
 print('Test loss:', score[0])
 print('Test accuracy:', score[1])

### 2018-12-02 Final Extra Project Paper/paper.tex
Final amendments to final paper.

@@
 
-\usepackage[varg]{txfonts}%%!!
-\makeatletter%
-\input{ot1txtt.fd}
-\makeatother%
+%\usepackage[varg]{txfonts}%%!!
+%\makeatletter%
+%\input{ot1txtt.fd}
+%\makeatother%
 
@@
 
-\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)} \\ \large{This version is amended from it's original version submitted to SWoPP 2018}}
+\title{Towards Accelerating Deep Neural Network Training on FPGAs: Facilitating the Use of Variable Precision\\ \Large{(Unrefereed Workshop Manuscript)} \\ \large{This version is amended from its original version submitted to SWoPP 2018}}
 \affiliate{TiTech}{Tokyo Institute of Technology, 
@@
 One alternative is to simulate alternative floating-point representations in software, for example using soft-float or MPFR libraries~\cite{softfloat}, but the resulting performance is often several magnitudes lower than hardware implementations, limiting the size of the study conducted.
-Furthermore, simulating alternative numerical formats in software are incapable of using any compiler optimizations, nor can they leverage the vector instruction often crucial to reach application performance in modern processors.
+Furthermore, simulating alternative numerical formats in software are incapable of using any compiler optimizations, nor can they leverage the vector instructions often crucial to reach application performance in modern processors.
 Porting the full software infrastructure stack is possible (and inevitable), but is a non-trivial effort that requires changes to the compiler, standard libraries and (possibly) the Application-Binary-Interface (e.g.\ calling convention).
@@
 \item Proposed design for a generalized FPGA training architecture targeting variable numerical formats, and
-\item Preliminary evaluation and analysis of core computation patterns for inference with respect to performance and resource utilization
+\item Preliminary evaluation and analysis of core computation patterns for inference and training with respect to performance and resource utilization
 \end{itemize}
@@
 FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementing a hardware design before taping out full chip.
-They are devices that can belong to the class of fine-grained reconfigurable devices.\\
+They are devices that belong to the class of fine-grained reconfigurable devices.\\
 FPGAs are made up of a reconfigurable fabric.
@@
 This effort is called \textit{forward propagation}. Training the network is done in a similar but reverse fashion -- errors are calculated at the output and propagated backwards.
-At this point in time, our framework focuses on forward propagation.
 
@@
 It is through Python that a user creates networks, selects inputs, and decides what data formats to use.
-Once a particular configuration is selected, our framework generates data-type oblivious training and inference code that targets Intel's OpenCL SDK for FPGAs.
+Once a particular configuration is selected, our framework can generate data-type oblivious training and inference code that targets Intel's OpenCL SDK for FPGAs.
 By data-type oblivious we mean that all operations associated with any particular data-type representation remain unresolved at the point of creation, as they will not depend on any of the native data-types or functionality of the OpenCL language.
-Instead, our Python framework invokes a data-type selector, which automatically generates a low-level hardware description language (HDL) library that contains commonly used operators for the selected data-type.
+Instead, our Python framework invokes a data-type selector, which automatically selects a low-level hardware description language (HDL) library that contains commonly used operators for the selected data-type.
 Once the Register-Transfer Level (RTL) library has been generated, it is merged with the data-type oblivious OpenCL template to yield the final description, which now can be synthesized using EDA tools and used.
 Invisible to the user, our host runtime system handles all communication, invocation and control over the FPGA from the host side.
+The host runtime can take weights from Keras and write weights for use with Keras.
+Currently it does not support Keras models for network design, since we only support Dense, Relu and Softmax layers.
 
@@
 Finally it does a final softmax kernel call to get the final prediction.
-After which it runs the first delta kernel and continues on to run the backward kernel for all layers.
-For performance this could obviously be done on the host, given the limited size of most final layers, but performance is not the main goal of this effort.
+After which it runs the first delta kernel and continues on to run the backward kernel for all layers in reverse order.
+For performance the last couple of layers could obviously be done on the host, given the limited size of most of those layers, but performance is not the main goal of this effort.
 The main goal is to simplify changing the numerical format, and thus all the calculations need to be done in that format, and an FPGA is better at accommodating this without a huge performance impact.
@@
 \subsubsection{Design details}
-All weight matrices are transposed in memory, this to optimize the memory access pattern of the matrix-matrix multiplication.
-The main inference is performed using an blocking implementation of the matrix multiplication.
+All weight matrices are transposed in memory, this to optimize the memory access pattern of the main inference matrix-matrix multiplication.
+The inference is performed using an blocking implementation of the matrix multiplication.
 First a block is fetched from the matrices containing the activations and weights and is placed in the block RAM on the FPGA.
@@
 
-The training logic itself, requires two matrix-matrix multiplications and three more simple multiply substract block.
-Due to the size requirements and the fact that the compiler will not successfully optimize the larger designs, the blocksize of the whole design is now limited to 24 and implementing a similar acceleration as above is impossible without using vendor IP.
+The training logic itself, requires two matrix-matrix multiplications and three more simple multiply and substract blocks.
+Due to the size requirements and the fact that the compiler will not successfully optimize the larger designs, the blocksize of the whole design is now limited to 24 and implementing a similar acceleration as done for inference is impossible without using vendor IP.
 
 \subsubsection{Design decisions}
-One of the main choices with the largest impact on implementation is whenever to keep all weight matrices in memory transposed.
+One of the main choices with the largest impact on implementation is whenever to keep all weight matrices in memory transposed (Colunm Major).
 During inference this is very beneficial, as it makes most reads sequential.
@@
 But since the arithmetic density of the training process is higher, the effect might be slightly less pronounced.
-Although it also increases the used area slightly because now the matrix multiplication block is distinct from the other ones.
+Although it also increases the used area slightly because now the matrix multiplication block used for training is distinct from the other ones.
 The transposing or indexing logic is different for each.
@@
 This saves space on the FPGA and simplifies the hardware design.
+%The final deci rant about other formats and no blocking for training.
 
@@
 All kernels were compiled with the flags ``\texttt{-O3 -fp-relaxed}''.
-``-O3'' is an optimization flag, configuring the compiler to enable resource-driven optimizations. % TODO verify
+``\texttt{-O3}'' is an optimization flag, configuring the compiler to enable resource-driven optimizations. % TODO verify
 The ``\texttt{-fp-relaxed}'' flag gives the compiler some more freedom with the order of operations using a balanced tree hardware implementation, this gives about a \SIrange{10}{15}{\percent} performance benefit.% without changing the numerical output.
@@
 Transposing the weight matrix sped up the kernel to around \num{7.5} GFLOPS.\@
-The results for the different final FPGA block sizes are shown in \cref{tab:inference-kernel-performance} for the inference kernels.
+The results for the different final FPGA block sizes are shown in \cref{tab:inference-kernel-performance} for the inference kernels.\\
 \Cref{tab:kernel-performance} shows the performance of the training kernels (they include an inference kernel), here it is clear that the training kernels are limiting the overall throughput.
 The backwards kernels have a lot of potential to be optimized if required, but much is dependant on the other data types and their implementation (size), so this is better done when actually implementing this flow for that data type.
+Or at least at a point when support for a certain type is added to this framework.
+The used FPGA device for testing has hardware support for IEEE-754 floating point numbers, so an alternative format will greatly increase the required area for the complete design.
 
@@
 Especially the backwards kernels seem to have a hard limit at around \numrange{6}{7} GFLOPS in their current form.
-Furthermore, given our experience with alternative numerical formats (most notably posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format.
+Furthermore, given our experience with alternative numerical formats (most notably posits~\cite{podobasposit}), we do not expect performance to be degraded when changing numerical format given enough resources (area).
 
@@
 The kernel resource utilization is shown in \cref{tab:fpga-inference-util} for the inference kernels only and \cref{tab:fpga-util} shows the utilization for the full implementation.
-The main limiting factor is the available block RAM and the ability for the compiler to runs its optimization phase without crashing.
+The main limiting factor is the available block RAM and the ability for the compiler to run its optimization phase without crashing.
 To stop the calculation of extra padding lines in the matrices, the block size should be a multiple of most of the layer sizes.
@@
 With the training kernels the theoretical need for block RAMs would triple if all matrix operations were implemented in the same way.
-Right now on a single device, make the limit to the block size rather small, in light of that, it was decided to postpone the further optimizations after different formats were added.
-Those will also take a much larger area themselves, making the problem worse.
+Right now on a single device, this makes the limit to the block size rather small, in light of that, it was decided to postpone the further optimizations after different formats were added.
+Those will also take a much larger area themselves as stated before, making the problem worse.
 
@@
 And the CIFAR-10 accuracy after training is \SI{47.9}{\percent}.
-The FPGA gets slightly different floating point results due to rounding differences and reaches \SI{95.4}{\percent} and \SI{45.2}{\percent} respectively after the same number of epochs.
+The FPGA gets slightly different floating point results due to rounding and implementation differences -- mainly in parallelism -- and reaches \SI{96.1}{\percent} and \SI{46.2}{\percent} respectively after the same number of epochs.
 
@@
 We evaluated the performance and resource consumption of our design on the FPGAs, and made sure that the inferred accuracy is correct.
-And that the training performance sufficient for further testing.
+And that the training performance is sufficient for further testing.
 We are currently working on the choice of numerical format to be used in both the inference and training part of our framework.
